### 2020-08-09 paperone_adult_health.Rmd
Putting together baseline tables and map.

---
title: 'Manuscript 1: Adult Health Effects'
author: "Elizabeth Chase"
date: "8/8/2020"
output: pdf_document
---

```{r setup, include=FALSE, echo=TRUE}
library(knitr)
opts_chunk$set(collapse=TRUE, fig.align='center', out.extra = '', fig.pos= "h", tidy=TRUE, tidy.opts=list(blank=TRUE, width.cutoff=40), warning=FALSE,message=FALSE)
options(scipen=999)

rm(list=ls())

library(tidyverse)
library(gridExtra)
library(RColorBrewer)
library(tableone)
library(latex2exp)
library(labelled)
library(kableExtra)
library(tigris)
library(sf)
library(spdep)

mydata <- readRDS("~/Desktop/Research/Jerel Flint/Analyses/adult_data_clean.rds")
```

We start by selecting our sample and assembling some baseline tables and figures:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
mydata_complete <- filter(mydata, !is.na(age), !is.na(reth), !is.na(marital_status), !is.na(educ_level), !is.na(public_benefits), !is.na(gender), !is.na(confidants2), !is.na(years_cityflint), !is.na(noticed_water_issue), !is.na(current_zip), !is.na(blood_test_after_april_2014), !is.na(blood_test_before_april_2014), !is.na(elevated_lead_before_april_2014), !is.na(elevated_lead_after_april_2014), !is.na(rashes_before_april_2014), !is.na(rashes_after_april_2014), !is.na(hairloss_before_april_2014), !is.na(hairloss_after_april_2014), !is.na(nausea_before_april_2014), !is.na(nausea_after_april_2014), !is.na(irritable_before_april_2014), !is.na(irritable_after_april_2014), !is.na(ptsdscore), !is.na(phq), gender != "Transgender Woman")

zcta1 <- zctas(cb = TRUE, starts_with = c("4850", "48532"), class = "sf") %>% filter(ZCTA5CE10 != "48509")
flintdat <- data.frame("zip" = zcta1$ZCTA5CE10, "geometry" = zcta1$geometry)

fils <- unzip("~/Desktop/Research/Jerel Flint/Analyses/tl_2019_26_place.zip")
flint_boundary <- st_read(fils[4]) %>% filter(NAME=="Flint")

totalpop <- data.frame(table(mydata_complete$current_zip))
colnames(totalpop) <- c("current_zip", "pop")

flintdat2 <- full_join(flintdat, totalpop, by=c("zip" = "current_zip")) 
flintdat2$pop <- factor(flintdat2$pop)

popmap <- ggplot(data=flintdat2) + geom_sf(data=flintdat2, aes(geometry = geometry, fill = pop), size=0, alpha = 0.6) + geom_sf(data=flint_boundary, aes(geometry=geometry), fill=NA) + geom_sf_label(aes(geometry = geometry, label = paste0(pop)), label.size = 0.02) + xlab(" ") + ylab(" ") + theme(rect = element_blank(), axis.ticks = element_blank(), axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(), legend.position = "none") + ggtitle("Number of Respondents Per Zipcode")

popmap

mydata_complete$collapsemarital <- case_when(
  mydata_complete$marital_status=="Single (never married)" ~ "Single (never married)",
  mydata_complete$marital_status=="Married" ~ "Married", 
  mydata_complete$marital_status=="Separated" | mydata_complete$marital_status=="Divorced" | mydata_complete$marital_status=="Widowed" ~ "Separated"
)

var_label(mydata_complete$collapseeduc) <- "Education level"
var_label(mydata_complete$public_benefits) <- "Receives public benefits"
var_label(mydata_complete$collapsemarital) <- "Marital status"
var_label(mydata_complete$noticed_water_issue2) <- "How long after water switch to notice water issue?"
var_label(mydata_complete$blood_test_after_april_2014) <- "Received blood lead test"
var_label(mydata_complete$elevated_lead_after_april_2014) <- "Had elevated lead"
var_label(mydata_complete$rashes_after_april_2014) <- "Had rashes"
var_label(mydata_complete$hairloss_after_april_2014) <- "Had hair loss"
var_label(mydata_complete$nausea_after_april_2014) <- "Had nausea"
var_label(mydata_complete$irritable_after_april_2014) <- "Was irritable"
var_label(mydata_complete$ptsdscore) <- "PC-PTSD-5 score"
var_label(mydata_complete$phq) <- "PHQ-4 score"

table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

table_outcomes <- CreateTableOne(vars=c("noticed_water_issue2", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "ptsdscore", "phq"), strata = "collapserace", data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

kable(print(table_predictors, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(5:9, 11:13, 15:17)) %>% kable_styling(position="center")

kable(print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:11, 13:15, 17:19, 21:23, 25:27, 29:31, 33:35)) %>% kable_styling(position="center")
```

Now, we conduct tests to reassure ourselves that we can just adjust for zipcode and not do a full-on spatial analysis:

We fit our models:

We make the Bonferroni correction:

### 2020-09-03 paperone_adult_health.Rmd
More changes for analysis and during paper drafting.

@@
 library(spdep)
+library(logistf)
 
@@
 
-We start by selecting our sample and assembling some baseline tables and figures:
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-mydata_complete <- filter(mydata, !is.na(age), !is.na(reth), !is.na(marital_status), !is.na(educ_level), !is.na(public_benefits), !is.na(gender), !is.na(confidants2), !is.na(years_cityflint), !is.na(noticed_water_issue), !is.na(current_zip), !is.na(blood_test_after_april_2014), !is.na(blood_test_before_april_2014), !is.na(elevated_lead_before_april_2014), !is.na(elevated_lead_after_april_2014), !is.na(rashes_before_april_2014), !is.na(rashes_after_april_2014), !is.na(hairloss_before_april_2014), !is.na(hairloss_after_april_2014), !is.na(nausea_before_april_2014), !is.na(nausea_after_april_2014), !is.na(irritable_before_april_2014), !is.na(irritable_after_april_2014), !is.na(ptsdscore), !is.na(phq), gender != "Transgender Woman")
+We start by selecting our sample:
+```{r, echo=TRUE, message=FALSE, warning=FALSE}
+mydata$num_time_notice <- case_when(
+  mydata$noticed_water_issue=="1 year *AFTER* it was switched" ~ 12,
+  mydata$noticed_water_issue=="2 months *AFTER* it was switched" ~ 2,
+  mydata$noticed_water_issue=="Unsure/Don't know" ~ NA_real_,
+  mydata$noticed_water_issue=="2 years *AFTER* it was switched" ~ 24,
+  mydata$noticed_water_issue=="Less than 1 month *AFTER* the water source was switched" ~ 0.5,
+  mydata$noticed_water_issue=="1 month *AFTER* it was switched" ~ 1,
+  mydata$noticed_water_issue=="3 months *AFTER* it was switched" ~ 3,
+  mydata$noticed_water_issue=="1 year and 2 months *AFTER* it was switched" ~ 14,
+  mydata$noticed_water_issue=="6 months *AFTER* it was switched" ~ 6,
+  mydata$noticed_water_issue=="9 months *AFTER* it was switched" ~ 9,
+  mydata$noticed_water_issue=="1 year and 6 months *AFTER* it was switched" ~ 18,
+  mydata$noticed_water_issue=="7 months *AFTER* it was switched" ~ 7,
+  mydata$noticed_water_issue=="4 years or more *AFTER* it was switched" ~ 4,
+  mydata$noticed_water_issue=="10 months *AFTER* it was switched" ~ 10,
+  mydata$noticed_water_issue=="5 months *AFTER* it was switched" ~ 5,
+  mydata$noticed_water_issue=="11 months *AFTER* it was switched" ~ 11,
+  mydata$noticed_water_issue=="4 months *AFTER* it was switched" ~ 4,
+  mydata$noticed_water_issue=="1 year and 5 months *AFTER* it was switched" ~ 17,
+  mydata$noticed_water_issue=="8 months *AFTER* it was switched" ~ 8,
+  mydata$noticed_water_issue=="3 years *AFTER* it was switched" ~ 36,
+  mydata$noticed_water_issue=="2 year and 1 month *AFTER* it was switched" ~ 25,
+  mydata$noticed_water_issue=="2 year and 6 months *AFTER* it was switched" ~ 30,
+  mydata$noticed_water_issue=="1 year and 3 months *AFTER* it was switched" ~ 15,
+  mydata$noticed_water_issue=="1 year and 1 month *AFTER* it was switched" ~ 13
+)
 
+mydata_complete <- filter(mydata, !is.na(age), !is.na(reth), !is.na(marital_status), !is.na(educ_level), !is.na(public_benefits), !is.na(gender), !is.na(confidants2), !is.na(years_cityflint), !is.na(current_zip), !is.na(blood_test_after_april_2014), !is.na(blood_test_before_april_2014), !is.na(elevated_lead_before_april_2014), !is.na(elevated_lead_after_april_2014), !is.na(rashes_before_april_2014), !is.na(rashes_after_april_2014), !is.na(hairloss_before_april_2014), !is.na(hairloss_after_april_2014), !is.na(nausea_before_april_2014), !is.na(nausea_after_april_2014), !is.na(irritable_before_april_2014), !is.na(irritable_after_april_2014), !is.na(ptsdscore), !is.na(phq), gender != "Transgender Woman", !is.na(num_time_notice))
+
+mydata_complete$collapsemarital <- case_when(
+  mydata_complete$marital_status=="Single (never married)" ~ "Single (never married)",
+  mydata_complete$marital_status=="Married" ~ "Married", 
+  mydata_complete$marital_status=="Separated" | mydata_complete$marital_status=="Divorced" | mydata_complete$marital_status=="Widowed" ~ "Separated"
+)
+
+mydata_complete$overall_collapse <- rowSums(select(mydata_complete, rash_collapse, hair_collapse, irritable_collapse, nausea_collapse))
+
+mydata_complete$bloodtest_collapse <- ifelse(mydata_complete$blood_test_after_april_2014=="Yes", 1, 0)
+
+mydata_complete$ptsd_bin <- as.numeric(mydata_complete$ptsdscore >= 3)
+mydata_complete$phq_bin <- as.numeric(mydata_complete$phq >= 6)
+
+mydata_complete$ptsd_bin <- factor(mydata_complete$ptsd_bin, level=c(0,1), labels=c("No", "Yes"))
+mydata_complete$phq_bin <- factor(mydata_complete$phq_bin, level=c(0,1), labels=c("No", "Yes"))
+```
+
+We assemble some descriptives and maps on the complete data:
+```{r, echo=TRUE, message=FALSE, warning=FALSE}
 zcta1 <- zctas(cb = TRUE, starts_with = c("4850", "48532"), class = "sf") %>% filter(ZCTA5CE10 != "48509")
@@
 flintdat2 <- full_join(flintdat, totalpop, by=c("zip" = "current_zip"))
-flintdat2$pop <- factor(flintdat2$pop)
 
-popmap <- ggplot(data=flintdat2) + geom_sf(data=flintdat2, aes(geometry = geometry, fill = pop), size=0, alpha = 0.6) + geom_sf(data=flint_boundary, aes(geometry=geometry), fill=NA) + geom_sf_label(aes(geometry = geometry, label = paste0(pop)), label.size = 0.02) + xlab(" ") + ylab(" ") + theme(rect = element_blank(), axis.ticks = element_blank(), axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(), legend.position = "none") + ggtitle("Number of Respondents Per Zipcode")
+popmap <- ggplot(data=flintdat2) + geom_sf(data=flintdat2, aes(geometry = geometry, fill = factor(pop)), size=0, alpha = 0.6) + geom_sf(data=flint_boundary, aes(geometry=geometry), fill=NA, color = "black") + geom_sf_label(aes(geometry = geometry, label = paste0(zip, " (", pop, ")"))) + xlab(" ") + ylab(" ") + theme(rect = element_blank(), axis.ticks = element_blank(), axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(), legend.position = "none") + scale_fill_grey()
 
@@
 
-mydata_complete$collapsemarital <- case_when(
-  mydata_complete$marital_status=="Single (never married)" ~ "Single (never married)",
-  mydata_complete$marital_status=="Married" ~ "Married", 
-  mydata_complete$marital_status=="Separated" | mydata_complete$marital_status=="Divorced" | mydata_complete$marital_status=="Widowed" ~ "Separated"
-)
+ggsave(filename = "mymap.pdf", plot = popmap, width = 8, height = 8)
 
@@
 var_label(mydata_complete$collapsemarital) <- "Marital status"
-var_label(mydata_complete$noticed_water_issue2) <- "How long after water switch to notice water issue?"
+var_label(mydata_complete$num_time_notice) <- "How long after water switch to notice water issue? (months)"
 var_label(mydata_complete$blood_test_after_april_2014) <- "Received blood lead test"
@@
 var_label(mydata_complete$irritable_after_april_2014) <- "Was irritable"
-var_label(mydata_complete$ptsdscore) <- "PC-PTSD-5 score"
-var_label(mydata_complete$phq) <- "PHQ-4 score"
+var_label(mydata_complete$ptsd_bin) <- "PTSD"
+var_label(mydata_complete$phq_bin) <- "Depression/Anxiety"
 
-table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
 
-table_outcomes <- CreateTableOne(vars=c("noticed_water_issue2", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "ptsdscore", "phq"), strata = "collapserace", data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+table_outcomes <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "collapserace", data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
 
@@
 
-kable(print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:11, 13:15, 17:19, 21:23, 25:27, 29:31, 33:35)) %>% kable_styling(position="center")
+kable(print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:10, 12:14, 16:18, 20:22, 24:26)) %>% kable_styling(position="center")
+
+table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+
+table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+
+kable(print(table_predictors_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(5:9, 11:13, 15:17)) %>% kable_styling(position="center")
+
+kable(print(table_outcomes_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:10, 12:14, 16:18, 20:22, 24:26)) %>% kable_styling(position="center")
 ```
 
-Now, we conduct tests to reassure ourselves that we can just adjust for zipcode and not do a full-on spatial analysis:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+knitr::include_graphics("~/Desktop/Research/Jerel Flint/Analyses/sample_inclusion.png")
+```
 
-We fit our models:
+Now, we conduct Moran's I tests grouped by zipcode to reassure ourselves that we can just adjust for zipcode and not do a full-on spatial analysis:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+zip_symp <- mydata_complete %>% dplyr::group_by(current_zip) %>% dplyr::summarize(elev_blood = sum(elevated_collapse, na.rm=TRUE), rash = sum(rash_collapse, na.rm=TRUE), nausea = sum(nausea_collapse, na.rm=TRUE), hairloss = sum(hair_collapse, na.rm=TRUE), irritable = sum(irritable_collapse, na.rm=TRUE), overall = sum(overall_collapse, na.rm=TRUE), ptsd = sum(ptsd_bin=="Yes", na.rm=TRUE), phq = sum(phq_bin=="Yes", na.rm=TRUE), get_test = sum(bloodtest_collapse, na.rm=TRUE), notice_issue = mean(num_time_notice, na.rm=TRUE), black = sum(collapserace=="Black", na.rm=TRUE), other = sum(collapserace=="Other", na.rm=TRUE),  l9 = sum(collapseeduc=="Less than high school", na.rm=TRUE), hs = sum(collapseeduc=="High school", na.rm=TRUE), assc = sum(collapseeduc=="Associate's", na.rm=TRUE), somecoll = sum(collapseeduc=="Some college", na.rm=TRUE), female = sum(gender!="Male", na.rm=TRUE), age = mean(age, na.rm=TRUE), pubben = sum(public_benefits=="Yes", na.rm=TRUE), pubbendk = sum(public_benefits=="Don't know/Unsure", na.rm=TRUE), network = mean(confidants2, na.rm=TRUE))
 
-We make the Bonferroni correction:
+flintdat3 <- full_join(flintdat2, zip_symp, by=c("zip" = "current_zip"))
+
+flintdat3$l9 <- flintdat3$l9/flintdat3$pop
+flintdat3$hs <- flintdat3$hs/flintdat3$pop
+flintdat3$assc <- flintdat3$assc/flintdat3$pop
+flintdat3$somecoll <- flintdat3$somecoll/flintdat3$pop
+flintdat3$black <- flintdat3$black/flintdat3$pop
+flintdat3$other <- flintdat3$other/flintdat3$pop
+flintdat3$female <- flintdat3$female/flintdat3$pop
+flintdat3$pubben <- flintdat3$pubben/flintdat3$pop
+flintdat3$pubbendk <- flintdat3$pubbendk/flintdat3$pop
+
+flint.nb <- poly2nb(flintdat3$geometry)
+flint.list.w <- nb2listw(flint.nb)
+
+elevblood <- moran.test(flintdat3$elev_blood/flintdat3$pop, listw=flint.list.w, randomisation=FALSE)
+elevblood
+elevblood_adj <- lm.morantest(lm(flintdat3$elev_blood/flintdat3$pop~ flintdat3$black + flintdat3$other + flintdat3$female + flintdat3$age),listw=flint.list.w)
+elevblood_adj
+
+rash <- moran.test(flintdat3$rash/flintdat3$pop, listw=flint.list.w, randomisation=FALSE)
+rash
+rash_adj <- lm.morantest(lm(flintdat3$rash/flintdat3$pop ~ flintdat3$black + flintdat3$other + flintdat3$female + flintdat3$age),listw=flint.list.w)
+rash_adj
+
+nausea <- moran.test(flintdat3$nausea/flintdat3$pop, listw=flint.list.w, randomisation=FALSE)
+nausea
+nausea_adj <- lm.morantest(lm(flintdat3$nausea/flintdat3$pop ~ flintdat3$black + flintdat3$other + flintdat3$female + flintdat3$age),listw=flint.list.w)
+nausea_adj
+
+hairloss <- moran.test(flintdat3$hairloss/flintdat3$pop, listw=flint.list.w, randomisation=FALSE)
+hairloss
+hairloss_adj <- lm.morantest(lm(flintdat3$hairloss/flintdat3$pop ~ flintdat3$black + flintdat3$other + flintdat3$female + flintdat3$age),listw=flint.list.w)
+hairloss_adj
+
+irritable <- moran.test(flintdat3$irritable/flintdat3$pop, listw=flint.list.w, randomisation=FALSE)
+irritable
+irritable_adj <- lm.morantest(lm(flintdat3$irritable/flintdat3$pop ~ flintdat3$black + flintdat3$other + flintdat3$female + flintdat3$age),listw=flint.list.w)
+irritable_adj
+
+overall <- moran.test(flintdat3$overall/flintdat3$pop, listw=flint.list.w, randomisation=FALSE)
+overall
+overall_adj <- lm.morantest(lm(flintdat3$overall/flintdat3$pop ~ flintdat3$black + flintdat3$other + flintdat3$female + flintdat3$age),listw=flint.list.w)
+overall_adj
+
+ptsd <- moran.test(flintdat3$ptsd/flintdat3$pop, listw=flint.list.w, randomisation=FALSE)
+ptsd
+ptsd_adj <- lm.morantest(lm(flintdat3$ptsd/flintdat3$pop ~ flintdat3$black + flintdat3$other + flintdat3$female + flintdat3$age),listw=flint.list.w)
+ptsd_adj
+
+phq <- moran.test(flintdat3$phq/flintdat3$pop, listw=flint.list.w, randomisation=FALSE)
+phq
+phq_adj <- lm.morantest(lm(flintdat3$phq/flintdat3$pop ~ flintdat3$black + flintdat3$other + flintdat3$female + flintdat3$age),listw=flint.list.w)
+phq_adj
+
+get_tested <- moran.test(flintdat3$get_test/flintdat3$pop, listw=flint.list.w, randomisation=FALSE)
+get_tested
+get_tested_adj <- lm.morantest(lm(flintdat3$get_test/flintdat3$pop ~ flintdat3$black + flintdat3$other + flintdat3$female + flintdat3$age),listw=flint.list.w)
+get_tested_adj
+
+notice <- moran.test(flintdat3$notice_issue, listw=flint.list.w, randomisation=FALSE)
+notice
+notice_adj <- lm.morantest(lm(flintdat3$notice_issue ~ flintdat3$black + flintdat3$other + flintdat3$female + flintdat3$age),listw=flint.list.w)
+notice_adj
+```
+
+There is some evidence of spatial correlation for nausea and hairloss, but once we adjust for baseline covariates it mostly goes away.
+Given the constraints of this analysis, we're going to just adjust for zipcode in our models and call it a day.
+
+We fit our models according to the causal diagram given here:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+knitr::include_graphics("~/Desktop/Research/Jerel Flint/Analyses/mediation.png")
+```
+
+As we know, when trying to understand the effect of a mediated effect on some outcome, we DO NOT adjust for the mediator.
+However, when trying to understand the effect of the mediator on the outcome, we DO adjust for the mediated effect.
+Therefore, we have to fit several models for our different outcomes, adjusting for different things depending on what the predictor of interest is.
+All told, we consider 10 different outcomes (PTSD, PHQ, rashes, hair loss, nausea, irritability, overall number of symptoms, elevated blood lead, getting tested, time to noticing issues) and consider the classes of predictors: demographics/baseline, time to noticing issues/getting tested, elevated blood lead, and emergence of symptoms.
+This results in us fitting 17 different models, given here:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+mydata_complete$collapsezip <- ifelse(mydata_complete$current_zip==48502, 2, mydata_complete$current_zip)
+mydata_complete$collapsezip <- factor(mydata_complete$collapsezip, levels=c(2:7), labels=c("48502/48503", "48504", "48505", "48506", "48507", "48532"))
+mydata_complete$collapsepubben <- ifelse(mydata_complete$public_benefits=="Yes", "Yes", "No")
+
+ptsd_dem <- glm(ptsd_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+
+summary(ptsd_dem)
+
+phq_dem <- glm(phq_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+
+summary(phq_dem)
+
+rash_dem <- glm(rash_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+
+summary(rash_dem)
+
+hairloss_dem <- glm(hair_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+
+summary(hairloss_dem)
+
+nausea_dem <- glm(nausea_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+
+summary(nausea_dem)
+
+irritable_dem <- glm(irritable_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+
+summary(irritable_dem)
+
+overall_dem <- glm(overall_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="poisson")
+
+summary(overall_dem)
+
+bloodlead_dem <- logistf(elevated_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data = mydata_complete)
+
+test1 <- summary(bloodlead_dem)
+
+gettest_dem <- glm(bloodtest_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+
+summary(gettest_dem)
+
+time_dem <- lm(log(num_time_notice) ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete)
+
+summary(time_dem)
+
+mydata_complete$rash_collapse_before <- ifelse(mydata_complete$rashes_before_april_2014=="Yes", "Yes", "No")
+mydata_complete$hair_collapse_before <- ifelse(mydata_complete$hairloss_before_april_2014=="Yes", "Yes", "No")
+mydata_complete$nausea_collapse_before <- ifelse(mydata_complete$nausea_before_april_2014=="Yes", "Yes", "No")
+mydata_complete$irritable_collapse_before <- ifelse(mydata_complete$irritable_before_april_2014=="Yes", "Yes", "No")
+mydata_complete$bloodtest_collapse_before <- ifelse(mydata_complete$blood_test_before_april_2014=="Yes", "Yes", "No")
+
+ptsd_symp <- glm(ptsd_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + overall_collapse + elevated_collapse + bloodtest_collapse + num_time_notice, data=mydata_complete, family="binomial")
+
+summary(ptsd_symp)
+
+phq_symp <- glm(phq_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + overall_collapse + elevated_collapse + bloodtest_collapse + num_time_notice, data=mydata_complete, family="binomial")
+
+summary(phq_symp)
+
+rash_symp <- logistf(rash_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + hair_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + rash_collapse_before, data=mydata_complete)
+
+test2 <- summary(rash_symp)
+
+hairloss_symp <- logistf(hair_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + rash_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + hair_collapse_before, data=mydata_complete)
+
+test3 <- summary(hairloss_symp)
+
+nausea_symp <- logistf(nausea_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + rash_collapse + hair_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + nausea_collapse_before, data=mydata_complete)
+
+test4 <- summary(nausea_symp)
+
+irritable_symp <- logistf(irritable_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + rash_collapse + hair_collapse + nausea_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + irritable_collapse_before, data=mydata_complete)
+
+test5 <- summary(irritable_symp)
+
+overall_bloodlead <- glm(overall_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + elevated_collapse + bloodtest_collapse + num_time_notice + rash_collapse_before + hair_collapse_before + nausea_collapse_before + irritable_collapse_before, data=mydata_complete, family="poisson")
+
+summary(overall_bloodlead)
+```
+
+Since we fit quite a few models, we use the FDR to adjust for our multiple testing.
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#Assembling a data frame of desired coefficients, confidence intervals, and p-values:
+myresults <- data.frame("Outcome" = c(rep("PTSD", length(summary(ptsd_dem)$coefficients[-1,1])), rep("PHQ", length(summary(phq_dem)$coefficients[-1,1])), rep("Rashes", length(summary(rash_dem)$coefficients[-1,1])), rep("Hairloss", length(summary(hairloss_dem)$coefficients[-1,1])), rep("Nausea", length(summary(nausea_dem)$coefficients[-1,1])), rep("Irritable", length(summary(irritable_dem)$coefficients[-1,1])), rep("Overall", length(summary(overall_dem)$coefficients[-1,1])), rep("Elevated lead", length(test1$coefficients[-1])), rep("Get tested", length(summary(gettest_dem)$coefficients[-1,1])), rep("Time to notice", length(summary(time_dem)$coefficients[-1,1])), rep("PTSD", length(summary(ptsd_symp)$coefficients[15:18,1])), rep("PHQ", length(summary(phq_symp)$coefficients[15:18,1])), rep("Rashes", length(test2$coefficients[15:20])), rep("Hairloss", length(test3$coefficients[15:20])), rep("Nausea", length(test4$coefficients[15:20])), rep("Irritable", length(test5$coefficients[15:20])), rep("Overall", length(summary(overall_bloodlead)$coefficients[15:17,1]))))
+
+myresults$Predictor <- c(rownames(summary(ptsd_dem)$coefficients[-1,]), rownames(summary(phq_dem)$coefficients[-1,]), rownames(summary(rash_dem)$coefficients[-1,]), rownames(summary(hairloss_dem)$coefficients[-1,]), rownames(summary(nausea_dem)$coefficients[-1,]), rownames(summary(irritable_dem)$coefficients[-1,]), rownames(summary(overall_dem)$coefficients[-1,]), names(test1$coefficients[-1]), rownames(summary(gettest_dem)$coefficients[-1,]), rownames(summary(time_dem)$coefficients[-1,]), rownames(summary(ptsd_symp)$coefficients[15:18,]), rownames(summary(phq_symp)$coefficients[15:18,]), names(test2$coefficients[15:20]), names(test3$coefficients[15:20]), names(test4$coefficients[15:20]), names(test5$coefficients[15:20]), rownames(summary(overall_bloodlead)$coefficients[15:17,]))
+
+myresults$Coefficient <- c(summary(ptsd_dem)$coefficients[-1,1], summary(phq_dem)$coefficients[-1,1], summary(rash_dem)$coefficients[-1,1], summary(hairloss_dem)$coefficients[-1,1], summary(nausea_dem)$coefficients[-1,1], summary(irritable_dem)$coefficients[-1,1], summary(overall_dem)$coefficients[-1,1], test1$coefficients[-1], summary(gettest_dem)$coefficients[-1,1], summary(time_dem)$coefficients[-1,1], summary(ptsd_symp)$coefficients[15:18,1], summary(phq_symp)$coefficients[15:18,1], test2$coefficients[15:20], test3$coefficients[15:20], test4$coefficients[15:20], test5$coefficients[15:20], summary(overall_bloodlead)$coefficients[15:17,1])
+
+myresults$Lower <- c(summary(ptsd_dem)$coefficients[-1,1]-1.96*summary(ptsd_dem)$coefficients[-1,2], summary(phq_dem)$coefficients[-1,1]-1.96*summary(phq_dem)$coefficients[-1,2], summary(rash_dem)$coefficients[-1,1]-1.96*summary(rash_dem)$coefficients[-1,2], summary(hairloss_dem)$coefficients[-1,1]-1.96*summary(hairloss_dem)$coefficients[-1,2], summary(nausea_dem)$coefficients[-1,1]-1.96*summary(nausea_dem)$coefficients[-1,2], summary(irritable_dem)$coefficients[-1,1]-1.96*summary(irritable_dem)$coefficients[-1,2], summary(overall_dem)$coefficients[-1,1]-1.96*summary(overall_dem)$coefficients[-1,2], test1$ci.lower[-1], summary(gettest_dem)$coefficients[-1,1]-1.96*summary(gettest_dem)$coefficients[-1,2], summary(time_dem)$coefficients[-1,1]-1.96*summary(time_dem)$coefficients[-1,2], summary(ptsd_symp)$coefficients[15:18,1]-1.96*summary(ptsd_symp)$coefficients[15:18,2], summary(phq_symp)$coefficients[15:18,1]-1.96*summary(phq_symp)$coefficients[15:18,2], test2$ci.lower[15:20], test3$ci.lower[15:20], test4$ci.lower[15:20], test5$ci.lower[15:20], summary(overall_bloodlead)$coefficients[15:17,1]-1.96*summary(overall_bloodlead)$coefficients[15:17,2])
+
+myresults$Upper <- c(summary(ptsd_dem)$coefficients[-1,1]+1.96*summary(ptsd_dem)$coefficients[-1,2], summary(phq_dem)$coefficients[-1,1]+1.96*summary(phq_dem)$coefficients[-1,2], summary(rash_dem)$coefficients[-1,1]+1.96*summary(rash_dem)$coefficients[-1,2], summary(hairloss_dem)$coefficients[-1,1]+1.96*summary(hairloss_dem)$coefficients[-1,2], summary(nausea_dem)$coefficients[-1,1]+1.96*summary(nausea_dem)$coefficients[-1,2], summary(irritable_dem)$coefficients[-1,1]+1.96*summary(irritable_dem)$coefficients[-1,2], summary(overall_dem)$coefficients[-1,1]+1.96*summary(overall_dem)$coefficients[-1,2], test1$ci.upper[-1], summary(gettest_dem)$coefficients[-1,1]+1.96*summary(gettest_dem)$coefficients[-1,2], summary(time_dem)$coefficients[-1,1]+1.96*summary(time_dem)$coefficients[-1,2], summary(ptsd_symp)$coefficients[15:18,1]+1.96*summary(ptsd_symp)$coefficients[15:18,2], summary(phq_symp)$coefficients[15:18,1]+1.96*summary(phq_symp)$coefficients[15:18,2], test2$ci.upper[15:20], test3$ci.upper[15:20], test4$ci.upper[15:20], test5$ci.upper[15:20], summary(overall_bloodlead)$coefficients[15:17,1]+1.96*summary(overall_bloodlead)$coefficients[15:17,2])
+
+myresults$pvalue <- c(summary(ptsd_dem)$coefficients[-1,4], summary(phq_dem)$coefficients[-1,4], summary(rash_dem)$coefficients[-1,4], summary(hairloss_dem)$coefficients[-1,4], summary(nausea_dem)$coefficients[-1,4], summary(irritable_dem)$coefficients[-1,4], summary(overall_dem)$coefficients[-1,4], test1$prob[-1], summary(gettest_dem)$coefficients[-1,4], summary(time_dem)$coefficients[-1,4], summary(ptsd_symp)$coefficients[15:18,4], summary(phq_symp)$coefficients[15:18,4], test2$prob[15:20], test3$prob[15:20], test4$prob[15:20], test5$prob[15:20], summary(overall_bloodlead)$coefficients[15:17,4])
+
+myresults$BHpvalue <- p.adjust(myresults$pvalue, method="BH")
+myresults$sig <- ifelse(myresults$BHpvalue <=0.05, "LOOK", NA_character_)
+
+myresults$Predictor_clean <- case_when(
+  myresults$Predictor=="age" ~ "Age",
+  myresults$Predictor=="genderMale" ~ "Male",
+  myresults$Predictor=="collapseraceOther" ~ "Other race",
+  myresults$Predictor=="collapseraceWhite" ~ "White race",
+  myresults$Predictor=="collapseeducHigh school" ~ "High school graduate",
+  myresults$Predictor=="collapseeducSome college" ~ "Some college",
+  myresults$Predictor=="collapseeducAssociate's" ~ "Associate's degree",
+  myresults$Predictor=="collapseeducCollege degree or more" ~ "College degree or more",
+  myresults$Predictor=="collapsepubbenYes" ~ "Receives public benefits",
+  myresults$Predictor=="collapsemaritalSeparated" ~ "Separated",
+  myresults$Predictor=="collapsemaritalSingle (never married)" ~ "Single",
+  myresults$Predictor=="years_cityflint" ~ "Years in Flint",
+  myresults$Predictor=="confidants2" ~ "Network size",
+  myresults$Predictor=="collapsezip48504" ~ "Zipcode 48504",
+  myresults$Predictor=="collapsezip48505" ~ "Zipcode 48505",
+  myresults$Predictor=="collapsezip48506" ~ "Zipcode 48506",
+  myresults$Predictor=="collapsezip48507" ~ "Zipcode 48507",
+  myresults$Predictor=="collapsezip48532" ~ "Zipcode 48532",
+  myresults$Predictor=="rash_collapse" ~ "Rashes",
+  myresults$Predictor=="hair_collapse" ~ "Hair loss",
+  myresults$Predictor=="nausea_collapse" ~ "Nausea",
+  myresults$Predictor=="irritable_collapse" ~ "Irritability",
+  myresults$Predictor=="elevated_collapse" ~ "Elevated BLL",
+  myresults$Predictor=="bloodtest_collapse" ~ "Screened for lead",
+  myresults$Predictor=="num_time_notice" ~ "Months to notice problem"
+)
+
+myresults$Predictor_clean <- factor(myresults$Predictor_clean, levels= c("Age", "Male", "Other race", "White race", "High school graduate", "Some college", "Associate's degree", "College degree or more", "Receives public benefits", "Separated", "Single", "Years in Flint", "Network size", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Months to notice problem", "Screened for lead", "Elevated BLL", "Rashes", "Hair loss", "Nausea", "Irritability"), ordered=TRUE)
+
+table3_results <- filter(myresults, Outcome=="Time to notice" | Outcome=="Get tested" | Outcome=="Elevated lead") %>%
+  mutate(Label = paste(round(exp(Coefficient), digits=1), " (", round(exp(Lower), digits=1), ",", round(exp(Upper), digits=1), ")", sep=""), Pvalue = round(BHpvalue, digits=2)) %>% select(Outcome, Predictor_clean, Label, Pvalue)
+
+table4_results <- filter(myresults, Outcome=="Rashes" | Outcome=="Hairloss" | Outcome=="Nausea" | Outcome=="Irritable") %>%
+  mutate(Label = paste(round(exp(Coefficient), digits=1), " (", round(exp(Lower), digits=1), ",", round(exp(Upper), digits=1), ")", sep=""), Pvalue = round(BHpvalue, digits=2)) %>% select(Outcome, Predictor_clean, Label, Pvalue)
+
+table4_resultsb <- filter(myresults, Outcome=="Overall") %>%
+  mutate(Label = paste(round(Coefficient, digits=1), " (", round(Lower, digits=1), ",", round(Upper, digits=1), ")", sep=""), Pvalue = round(BHpvalue, digits=2)) %>% select(Outcome, Predictor_clean, Label, Pvalue)
+
+table5_results <- filter(myresults, Outcome=="PTSD" | Outcome=="PHQ") %>%
+  mutate(Label = paste(round(exp(Coefficient), digits=1), " (", round(exp(Lower), digits=1), ",", round(exp(Upper), digits=1), ")", sep=""), Pvalue = round(BHpvalue, digits=2)) %>% select(Outcome, Predictor_clean, Label, Pvalue)
+
+#ptsd_plot <- ggplot(myresults[myresults$Outcome=="PTSD",], aes(fct_rev(Predictor_clean), Coefficient)) + geom_point() + geom_errorbar(aes(ymin=Lower, ymax=Upper, width=0.1)) + coord_flip(ylim=c(-2.35, 5.5)) + labs(y = "Odds Ratio and 95% CI", x = "", caption=TeX('Protective $\\leftarrow \\rightarrow$ Harmful' )) + geom_hline(yintercept=0, linetype="dashed", color = "black") + theme(panel.background = element_rect(fill="white"), panel.grid.major = element_blank(), panel.grid.minor=element_blank(), legend.position="bottom", text=element_text(size=14), plot.caption = element_text(size=14, hjust = 0.15)) + geom_rect(fill="white", ymin=4.7, ymax=Inf, xmin=-Inf, xmax=Inf) + annotate(geom = 'text', label = myresults$Label[myresults$Outcome=="PTSD"], x = myresults$Predictor_clean[myresults$Outcome=="PTSD"], y = 3.5, hjust = 0, vjust = 0.5) + scale_y_continuous(breaks=log(c(0.1, 0.25, 0.5, 1, 2, 4, 10)), labels=c("0.1","0.25", "0.5", "1.0", "2.0", "4.0", "10.0")) + ggtitle("Outcome: Trauma Symptoms")
+
+#ptsd_plot
+
+#phq_plot <- ggplot(myresults[myresults$Outcome=="PHQ",], aes(fct_rev(Predictor_clean), Coefficient)) + geom_point() + geom_errorbar(aes(ymin=Lower, ymax=Upper, width=0.1)) + coord_flip(ylim=c(-2.35, 5.5)) + labs(y = "Odds Ratio and 95% CI", x = "", caption=TeX('Protective $\\leftarrow \\rightarrow$ Harmful' )) + geom_hline(yintercept=0, linetype="dashed", color = "black") + theme(panel.background = element_rect(fill="white"), panel.grid.major = element_blank(), panel.grid.minor=element_blank(), legend.position="bottom", text=element_text(size=14), plot.caption = element_text(size=14, hjust = 0.15), axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + geom_rect(fill="white", ymin=4.7, ymax=Inf, xmin=-Inf, xmax=Inf) + annotate(geom = 'text', label = myresults$Label[myresults$Outcome=="PHQ"], x = myresults$Predictor_clean[myresults$Outcome=="PHQ"], y = 3.5, hjust = 0, vjust = 0.5) + scale_y_continuous(breaks=log(c(0.1, 0.25, 0.5, 1, 2, 4, 10)), labels=c("0.1","0.25", "0.5", "1.0", "2.0", "4.0", "10.0")) + ggtitle("Outcome: Depression/Anxiety")
+
+#phq_plot
+
+#mental_plots <- grid.arrange(ptsd_plot, phq_plot, nrow=1, widths = c(6, 3))
+
+```

### 2020-09-09 paperone_adult_health.Rmd
Update to provide sensitivity analyses on missing data.

@@
 
-mydata_complete <- filter(mydata, !is.na(age), !is.na(reth), !is.na(marital_status), !is.na(educ_level), !is.na(public_benefits), !is.na(gender), !is.na(confidants2), !is.na(years_cityflint), !is.na(current_zip), !is.na(blood_test_after_april_2014), !is.na(blood_test_before_april_2014), !is.na(elevated_lead_before_april_2014), !is.na(elevated_lead_after_april_2014), !is.na(rashes_before_april_2014), !is.na(rashes_after_april_2014), !is.na(hairloss_before_april_2014), !is.na(hairloss_after_april_2014), !is.na(nausea_before_april_2014), !is.na(nausea_after_april_2014), !is.na(irritable_before_april_2014), !is.na(irritable_after_april_2014), !is.na(ptsdscore), !is.na(phq), gender != "Transgender Woman", !is.na(num_time_notice))
-
-mydata_complete$collapsemarital <- case_when(
-  mydata_complete$marital_status=="Single (never married)" ~ "Single (never married)",
-  mydata_complete$marital_status=="Married" ~ "Married", 
-  mydata_complete$marital_status=="Separated" | mydata_complete$marital_status=="Divorced" | mydata_complete$marital_status=="Widowed" ~ "Separated"
+mydata$collapsemarital <- case_when(
+  mydata$marital_status=="Single (never married)" ~ "Single (never married)",
+  mydata$marital_status=="Married" ~ "Married", 
+  mydata$marital_status=="Separated" | mydata$marital_status=="Divorced" | mydata$marital_status=="Widowed" ~ "Separated"
 )
 
-mydata_complete$overall_collapse <- rowSums(select(mydata_complete, rash_collapse, hair_collapse, irritable_collapse, nausea_collapse))
+mydata$overall_collapse <- rowSums(select(mydata, rash_collapse, hair_collapse, irritable_collapse, nausea_collapse))
 
-mydata_complete$bloodtest_collapse <- ifelse(mydata_complete$blood_test_after_april_2014=="Yes", 1, 0)
+mydata$bloodtest_collapse <- ifelse(mydata$blood_test_after_april_2014=="Yes", 1, 0)
 
-mydata_complete$ptsd_bin <- as.numeric(mydata_complete$ptsdscore >= 3)
-mydata_complete$phq_bin <- as.numeric(mydata_complete$phq >= 6)
+mydata$ptsd_bin <- as.numeric(mydata$ptsdscore >= 3)
+mydata$phq_bin <- as.numeric(mydata$phq >= 6)
 
-mydata_complete$ptsd_bin <- factor(mydata_complete$ptsd_bin, level=c(0,1), labels=c("No", "Yes"))
-mydata_complete$phq_bin <- factor(mydata_complete$phq_bin, level=c(0,1), labels=c("No", "Yes"))
+mydata$ptsd_bin <- factor(mydata$ptsd_bin, level=c(0,1), labels=c("No", "Yes"))
+mydata$phq_bin <- factor(mydata$phq_bin, level=c(0,1), labels=c("No", "Yes"))
+
+mydata$include <- ifelse(!is.na(mydata$age) & !is.na(mydata$reth) & !is.na(mydata$marital_status) & !is.na(mydata$educ_level) & !is.na(mydata$public_benefits) & !is.na(mydata$gender) & !is.na(mydata$confidants2) & !is.na(mydata$years_cityflint) & !is.na(mydata$current_zip) & !is.na(mydata$blood_test_after_april_2014) & !is.na(mydata$blood_test_before_april_2014) & !is.na(mydata$elevated_lead_before_april_2014) & !is.na(mydata$elevated_lead_after_april_2014) & !is.na(mydata$rashes_before_april_2014) & !is.na(mydata$rashes_after_april_2014) & !is.na(mydata$hairloss_before_april_2014) & !is.na(mydata$hairloss_after_april_2014) & !is.na(mydata$nausea_before_april_2014) & !is.na(mydata$nausea_after_april_2014) & !is.na(mydata$irritable_before_april_2014) & !is.na(mydata$irritable_after_april_2014) & !is.na(mydata$ptsdscore) & !is.na(mydata$phq) & mydata$gender != "Transgender Woman" & !is.na(mydata$num_time_notice),  1, 0)
+
+mydata$include <- factor(mydata$include, levels=c(0, 1), labels=c("Excluded", "Included"))
+
+var_label(mydata$collapseeduc) <- "Education level"
+var_label(mydata$public_benefits) <- "Receives public benefits"
+var_label(mydata$collapsemarital) <- "Marital status"
+var_label(mydata$num_time_notice) <- "How long after water switch to notice water issue? (months)"
+var_label(mydata$blood_test_after_april_2014) <- "Received blood lead test"
+var_label(mydata$elevated_lead_after_april_2014) <- "Had elevated lead"
+var_label(mydata$rashes_after_april_2014) <- "Had rashes"
+var_label(mydata$hairloss_after_april_2014) <- "Had hair loss"
+var_label(mydata$nausea_after_april_2014) <- "Had nausea"
+var_label(mydata$irritable_after_april_2014) <- "Was irritable"
+var_label(mydata$ptsd_bin) <- "PTSD"
+var_label(mydata$phq_bin) <- "Depression/Anxiety"
+
+mydata_complete <- filter(mydata, !is.na(age), !is.na(reth), !is.na(marital_status), !is.na(educ_level), !is.na(public_benefits), !is.na(gender), !is.na(confidants2), !is.na(years_cityflint), !is.na(current_zip), !is.na(blood_test_after_april_2014), !is.na(blood_test_before_april_2014), !is.na(elevated_lead_before_april_2014), !is.na(elevated_lead_after_april_2014), !is.na(rashes_before_april_2014), !is.na(rashes_after_april_2014), !is.na(hairloss_before_april_2014), !is.na(hairloss_after_april_2014), !is.na(nausea_before_april_2014), !is.na(nausea_after_april_2014), !is.na(irritable_before_april_2014), !is.na(irritable_after_april_2014), !is.na(ptsdscore), !is.na(phq), gender != "Transgender Woman", !is.na(num_time_notice))
 ```
@@
 
+table_missing <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2", "num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "include", data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+
 table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
@@
 table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+
+kable(print(table_missing, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:16, 18:20, 26:28, 30:32, 34:36, 38:40, 42:44)) %>% kable_styling(position="center")
+
+test <- print(table_missing, contDigits=1, varLabel = T, printToggle=FALSE)
 

### 2020-11-23 paperone_adult_health.Rmd
Updates to analysis for child health paper.

@@
 
-totalpop <- data.frame(table(mydata_complete$current_zip))
+totalpop <- data.frame(table(mydata$current_zip))
 colnames(totalpop) <- c("current_zip", "pop")
@@
 
-table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata, includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
 
-table_outcomes <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "collapserace", data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+table_outcomes <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "collapserace", data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)
 
@@
 
-table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)
 
-table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), data=mydata_complete, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)
 

### 2020-11-23 papertwo_child_health.Rmd
Updates to analysis for child health paper.

---
title: "Manuscript 2: Child Health Outcomes"
author: "Elizabeth Chase"
date: "10/16/2020"
output: pdf_document
---

```{r setup, include=FALSE, echo=TRUE}
library(knitr)
opts_chunk$set(collapse=TRUE, fig.align='center', out.extra = '', fig.pos= "h", tidy=TRUE, tidy.opts=list(blank=TRUE, width.cutoff=40), warning=FALSE,message=FALSE)
options(scipen=999)

rm(list=ls())

library(tidyverse)
library(gridExtra)
library(RColorBrewer)
library(tableone)
library(latex2exp)
library(labelled)
library(kableExtra)
library(tigris)
library(sf)
library(spdep)
library(logistf)
library(ARTool)
library(lme4)

load("~/Desktop/Research/Jerel Flint/Analyses/child_long.RData")
load("~/Desktop/Research/Jerel Flint/Analyses/adult_data_eliz.RData")

subadult <- mutate(adult_clean_eliz, parbloodtestf = blood_test_after_april_2014, parbllf = elevated_lead_after_april_2014, parrashesf = rashes_after_april_2014, parhairf = hairloss_after_april_2014, parnausf = nausea_after_april_2014, parirrf = irritable_after_april_2014, parbloodtestc = getscreened, parbllc = elevated_collapse, parrashesc = rash_collapse, parhairc = hair_collapse, parnausc = nausea_collapse, parirrc = irritable_collapse, paroverall = overall_collapse) %>% select(inclusion, unique_id, age, gender, collapserace, collapseeduc, have_health_insurance, public_benefits, water_exaggerated, children_health_harmed, trust_government_in_future, drink_tap_in_three_years, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, political_affiliation, nightmares, avoided_thinking_crisis, onguard_watchful, numb_detached, felt_guilty, ptsdscore, phq, parbloodtestf, parbllf, parrashesf, parhairf, parnausf, parirrf, parbloodtestc, parbllc, parrashesc, parhairc, parnausc, parirrc, paroverall, confidants2, number_children, employ_status)

child_adult <- left_join(child_final, subadult, by=c("unique_id"))

rm(list=c("adult_clean_eliz", "subadult", "child_final"))

child_adult$gettested <- ifelse(child_adult$blood_test_after_april_2014=="Yes" & child_adult$blood_test_before_april_2014=="No", 1, ifelse(is.na(child_adult$blood_test_after_april_2014) | is.na(child_adult$blood_test_before_april_2014), NA_real_, 0))

child_adult$elevbll <- ifelse(child_adult$elevated_lead_after_april_2014=="Yes" & child_adult$elevated_lead_before_april_2014=="No", 1, ifelse(is.na(child_adult$elevated_lead_after_april_2014) | is.na(child_adult$elevated_lead_before_april_2014), NA_real_, 0))

child_adult$rash <- ifelse(child_adult$rash_after_april_2014=="Yes" & child_adult$rash_before_april_2014=="No", 1, ifelse(is.na(child_adult$rash_after_april_2014) | is.na(child_adult$rash_before_april_2014), NA_real_, 0))

child_adult$hair <- ifelse(child_adult$hairloss_after_april_2014=="Yes" & child_adult$hairloss_before_april_2014=="No", 1, ifelse(is.na(child_adult$hairloss_after_april_2014) | is.na(child_adult$hairloss_before_april_2014), NA_real_, 0))

child_adult$learn <- ifelse(child_adult$learning_after_april_2014=="Yes" & child_adult$learning_before_april_2014=="No", 1, ifelse(is.na(child_adult$learning_after_april_2014) | is.na(child_adult$learning_before_april_2014), NA_real_, 0))

child_adult$hyper <- ifelse(child_adult$hyper_after_april_2014=="Yes" & child_adult$hyper_before_april_2014=="No", 1, ifelse(is.na(child_adult$hyper_after_april_2014) | is.na(child_adult$hyper_before_april_2014), NA_real_, 0))

child_adult$irritable <- ifelse(child_adult$irritable_after_april_2014=="Yes" & child_adult$irritable_before_april_2014=="No", 1, ifelse(is.na(child_adult$irritable_after_april_2014) | is.na(child_adult$irritable_before_april_2014), NA_real_, 0))

symp_sub <- select(child_adult, gettested, elevbll, rash, hair, learn, hyper, irritable)

child_adult$overall_symp <- rowSums(symp_sub, na.rm=TRUE)

child_adult$racecollapse <- case_when(
  child_adult$reth=="Black or African American" ~ "Black",
  child_adult$reth=="Latino or Hispanic" | child_adult$reth=="Middle Eastern" | child_adult$reth=="Mixed Race" ~ "Other",
  child_adult$reth=="White" ~ "White"
)
```

First, let's get some descriptives:
```{r, echo=TRUE, message=FALSE, warning=FALSE}
child_adult$relationship <- factor(child_adult$relationship, levels=c("Your child", "Your brother or stepbrother", "Your sister or stepsister", "Your niece or nephew", "Your friend's or acquaintance's child or relative", "Your grandchild", "Other relationship"), ordered=TRUE)

child_adult$gettested <- factor(child_adult$gettested, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$elevbll <- factor(child_adult$elevbll, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$rash <- factor(child_adult$rash, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$hair <- factor(child_adult$hair, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$learn <- factor(child_adult$learn, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$hyper <- factor(child_adult$hyper, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$irritable <- factor(child_adult$irritable, levels=c(0, 1), labels=c("No", "Yes"))
child_adult$gendercollapse <- ifelse(child_adult$gender.y=="Transgender Woman" | child_adult$gender.y=="Female", "Female", ifelse(is.na(child_adult$gender.y), NA_character_, "Male"))

var_label(child_adult$relationship) <- "Child's relationship to survey respondent"
var_label(child_adult$age.x) <- "Child age"
var_label(child_adult$gender.x) <- "Child gender"
var_label(child_adult$watersource) <- "Child water source"
var_label(child_adult$gettested) <- "Blood lead test after April 2014 and not before"
var_label(child_adult$elevbll) <- "Elevated BLLs after April 2014 and not before"
var_label(child_adult$rash) <- "Rashes after April 2014 and not before"
var_label(child_adult$hair) <- "Hair loss after April 2014 and not before"
var_label(child_adult$learn) <- "Learning delays after April 2014 and not before"
var_label(child_adult$hyper) <- "Hyperactivity after April 2014 and not before"
var_label(child_adult$irritable) <- "Irritability after April 2014 and not before"
var_label(child_adult$overall_symp) <- "Total number of symptoms after April 2014 and not before"
var_label(child_adult$gendercollapse) <- "Guardian's gender"
var_label(child_adult$collapserace) <- "Guardian's race/ethnicity"
var_label(child_adult$collapseeduc) <- "Guardian's education"
var_label(child_adult$public_benefits) <- "Guardian receives public benefits"
var_label(child_adult$confidants2) <- "Guardian's social network size"
var_label(child_adult$age.y) <- "Guardian's age"
var_label(child_adult$employ_status) <- "Guardian's employment status"

child_adult$racecollapse <- factor(child_adult$racecollapse)
child_adult$unique_id <- factor(child_adult$unique_id)

child_adult <- arrange(child_adult, unique_id, racecollapse)

m <- art(relationship ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- data.frame("Outcome" = "Relationship", "Pvalue" = anova(m)$`Pr(>F)`)
m <- art(age.x ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- rbind(pvalues, data.frame("Outcome" = "Child age", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(gender.x, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- rbind(pvalues, data.frame("Outcome" = "Gender", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(watersource, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$watersource),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Watersource", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(gettested, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$gettested),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "BloodTest", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(elevbll, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$elevbll),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "BLLs", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(rash, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$rash),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Rash", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(hair, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$hair),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Hairloss", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(learn, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$learn),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Learning", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(hyper, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$hyper),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Hyper", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(irritable, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$irritable),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Irritable", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(overall_symp ~ racecollapse + (1 | unique_id), data=child_adult)
pvalues <- rbind(pvalues, data.frame("Outcome" = "Overall", "Pvalue" = anova(m)$`Pr(>F)`))
child_adult$age_grp <- case_when(
  child_adult$age.y < 30 ~ "20-29",
  child_adult$age.y >= 30 & child_adult$age.y < 40 ~ "30-39",
  child_adult$age.y >= 40 & child_adult$age.y < 40 ~ "40-49",
  child_adult$age.y >= 50 ~ "50-73"
)
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(age_grp, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$age_grp),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian age", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(gendercollapse, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$gender.y),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's Gender", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(collapserace, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$collapserace),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's Race", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(collapseeduc, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$collapseeduc),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's Education", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(public_benefits, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$public_benefits),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian receives public benefits", "Pvalue" = anova(m)$`Pr(>F)`))
m <- art(factor(racecollapse, ordered=TRUE) ~ factor(employ_status, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$employ_status),])
pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's employment status", "Pvalue" = anova(m)$`Pr(>F)`))

child_adult$agegrp2 <- case_when(
  child_adult$age.x <= 0.5 ~ "Infant",
  child_adult$age.x > 0.5 ~ "Child"
)

table_pred <- CreateTableOne(vars=c("relationship", "age.x", "gender.x", "watersource", "age.y", "gendercollapse", "collapserace", "collapseeduc", "public_benefits", "employ_status"), strata = "racecollapse", data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

table_pred_nostrat <- CreateTableOne(vars=c("relationship", "age.x", "gender.x", "watersource", "age.y", "gendercollapse", "collapserace", "collapseeduc", "public_benefits", "employ_status"), data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

table_outcome <- CreateTableOne(vars=c("gettested", "elevbll", "rash", "hair", "learn", "hyper","irritable", "overall_symp"), strata = "racecollapse", data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

table_outcome_nostrat <- CreateTableOne(vars=c("gettested", "elevbll", "rash", "hair", "learn", "hyper","irritable", "overall_symp"), data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

kable(print(table_pred, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:9, 13:18, 22:24, 26:30, 32:34, 36:39)) %>% kable_styling(position="center")

kable(print(table_pred_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:9, 13:18, 22:24, 26:30, 32:34, 36:39)) %>% kable_styling(position="center")

kable(print(table_outcome, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:5, 7:9, 11:13, 15:17, 19:21, 23:25, 27:29)) %>% kable_styling(position="center")

kable(print(table_outcome_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:5, 7:9, 11:13, 15:17, 19:21, 23:25, 27:29)) %>% kable_styling(position="center")
```

Now, onto modeling for children health outcomes:
```{r, echo=TRUE, message=FALSE, warning=FALSE}
#For water source:
child_adult$pubben <- ifelse(child_adult$public_benefits=="Yes", 1, ifelse(is.na(child_adult$public_benefits), NA_real_, 0))
child_adult$bottledwater <- ifelse(child_adult$watersource=="Bottled water", 1, ifelse(is.na(child_adult$watersource), NA_real_, 0))
child_adult$employcollapse <- ifelse(child_adult$employ_status=="Employed", "Employed", ifelse(child_adult$employ_status=="Unemployed", "Unemployed", ifelse(is.na(child_adult$employ_status), NA_character_, "Other")))

watersource_model <- glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ##issues with convergence; did not include

#For getting tested:
#child_adult$gettested <- ifelse(child_adult$blood_test_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$blood_test_after_april_2014), NA_real_, 0))

tested_model_noadult <- glmer(gettested ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")

effects_mat <- data.frame("Outcome" = rep("Get tested", 5), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits"), "Estimate" = summary(tested_model_noadult)$coefficients[-1,1], "StErr" = summary(tested_model_noadult)$coefficients[-1,2], "Pvalue" = summary(tested_model_noadult)$coefficients[-1,4])

#For having elevated BLLs:
#child_adult$elevbll <- ifelse(child_adult$elevated_lead_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$elevated_lead_after_april_2014), NA_real_, 0))

bll_model_noadult <- glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
bll_model_adult <- glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial") # + parbllc

subdat <- data.frame("Outcome" = rep("Elevated BLLs", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(bll_model_noadult)$coefficients[-1,1], summary(bll_model_adult)$coefficients[7,1]), "StErr" = c(summary(bll_model_noadult)$coefficients[-1,2], summary(bll_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(bll_model_noadult)$coefficients[-1,4], summary(bll_model_adult)$coefficients[7,4]))

effects_mat <- rbind(effects_mat, subdat)

#For having rashes:
#child_adult$rash <- ifelse(child_adult$rash_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$rash_after_april_2014), NA_real_, 0))

rash_model_noadult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
rash_model_adult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial")

subdat <- data.frame("Outcome" = rep("Rashes", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(rash_model_noadult)$coefficients[-1,1], summary(rash_model_adult)$coefficients[7,1]), "StErr" = c(summary(rash_model_noadult)$coefficients[-1,2], summary(rash_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(rash_model_noadult)$coefficients[-1,4], summary(rash_model_adult)$coefficients[7,4]))

effects_mat <- rbind(effects_mat, subdat)

#For having hair loss:
#child_adult$hair <- ifelse(child_adult$hairloss_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$hairloss_after_april_2014), NA_real_, 0))

hair_model_noadult <- glmer(hair ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include
hair_model_adult <- glmer(hair ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include

#For having learning delays:
#child_adult$learn <- ifelse(child_adult$learning_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$learning_after_april_2014), NA_real_, 0))

learn_model_noadult <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
learn_model_layer2 <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial")

subdat <- data.frame("Outcome" = rep("Learning Delays", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(learn_model_noadult)$coefficients[-1,1], summary(learn_model_layer2)$coefficients[7,1]), "StErr" = c(summary(learn_model_noadult)$coefficients[-1,2], summary(learn_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(learn_model_noadult)$coefficients[-1,4], summary(learn_model_layer2)$coefficients[7,4]))

effects_mat <- rbind(effects_mat, subdat)

#For having hyperactivity:
#child_adult$hyper <- ifelse(child_adult$hyper_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$hyper_after_april_2014), NA_real_, 0))

hyper_model_noadult <- glmer(hyper ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
hyper_model_layer2 <- glmer(hyper ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial")

subdat <- data.frame("Outcome" = rep("Hyperactivity", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(hyper_model_noadult)$coefficients[-1,1], summary(hyper_model_layer2)$coefficients[7,1]), "StErr" = c(summary(hyper_model_noadult)$coefficients[-1,2], summary(hyper_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(hyper_model_noadult)$coefficients[-1,4], summary(hyper_model_layer2)$coefficients[7,4]))

effects_mat <- rbind(effects_mat, subdat)

#For having irritability:
#child_adult$irritable <- ifelse(child_adult$irritable_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$irritable_after_april_2014), NA_real_, 0))

irr_model_noadult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
irr_model_adult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial")

subdat <- data.frame("Outcome" = rep("Irritability", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(irr_model_noadult)$coefficients[-1,1], summary(irr_model_adult)$coefficients[7,1]), "StErr" = c(summary(irr_model_noadult)$coefficients[-1,2], summary(irr_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(irr_model_noadult)$coefficients[-1,4], summary(irr_model_adult)$coefficients[7,4]))

effects_mat <- rbind(effects_mat, subdat)

#For overall symptoms:
overall_model_noadult <- glmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult)
overall_model_adult <- glmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult)

subdat <- data.frame("Outcome" = rep("Overall Symptoms", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(overall_model_noadult)$coefficients[-1,1], summary(overall_model_adult)$coefficients[7,1]), "StErr" = c(summary(overall_model_noadult)$coefficients[-1,2], summary(overall_model_adult)$coefficients[7,2]), "Pvalue" = pnorm(c(summary(overall_model_noadult)$coefficients[-1,3], summary(overall_model_adult)$coefficients[7,3]), lower.tail = FALSE))

effects_mat <- rbind(effects_mat, subdat)
```

And now modeling for adult experiences:
```{r, echo=TRUE, message=FALSE, warning=FALSE}
##Assembling child health indicators:
child_sum <- group_by(child_adult, unique_id) %>% summarise(child_screen = as.numeric(sum(as.numeric(gettested)-1, na.rm=TRUE) > 0), child_symps = sum(overall_symp), child_bll = as.numeric(sum(as.numeric(elevbll)-1, na.rm=TRUE) > 0), child_rash = as.numeric(sum(as.numeric(rash)-1, na.rm=TRUE) > 0), child_hair = as.numeric(sum(as.numeric(hair)-1, na.rm=TRUE) > 0), child_learning = as.numeric(sum(as.numeric(learn)-1, na.rm=TRUE) > 0), child_hyper = as.numeric(sum(as.numeric(hyper)-1, na.rm=TRUE) > 0), child_irritable = as.numeric(sum(as.numeric(irritable)-1, na.rm=TRUE) > 0))

child_adult_sub <- unique(select(child_adult, unique_id, age.y, gendercollapse, collapserace, collapseeduc, pubben, water_exaggerated, children_health_harmed, trust_government_in_future, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, ptsdscore, phq, parbloodtestc, parbllc, parrashesc, parhairc, parnausc, parirrc, paroverall, confidants2, number_children))

child_adult_sum <- left_join(child_adult_sub, child_sum, by=c("unique_id"))

##Outcome: believing water crisis exaggerated
exaggerated_layer1 <- glm(as.numeric(water_exaggerated=="Agree" | water_exaggerated=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 + number_children, data = child_adult_sum, family = "binomial")
exaggerated_layer2 <- logistf(as.numeric(water_exaggerated=="Agree" | water_exaggerated=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 +  number_children + paroverall + child_symps + child_screen + child_bll + child_rash + child_learning + child_hyper + child_irritable, data = child_adult_sum)
test <- summary(exaggerated_layer2)

subdat <- data.frame("Outcome" = rep("Crisis Exaggerated", 15), "Variable" = c("Guardian Age", "Guardian Male", "Guardian Race-Other", "Guardian Race-White", "Public Benefits", "Number of confidants", "Number of children", "Number of adult symptoms", "Number of child symptoms", "Child screened", "Child with BLL", "Child with Rash", "Child with Learning", "Child with Hyper", "Child with Irritability"), "Estimate" = c(summary(exaggerated_layer1)$coefficients[-1,1], test$coefficients[9:16]), "StErr" = c(summary(exaggerated_layer1)$coefficients[-1,2], sqrt(diag(test$var)[9:16])), "Pvalue" = c(summary(exaggerated_layer1)$coefficients[-1,4], test$prob[9:16]))

effects_mat <- rbind(effects_mat, subdat)

##Outcome: believing children's health was harmed
health_layer1 <- glm(as.numeric(children_health_harmed=="Agree" | children_health_harmed=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 + number_children, data = child_adult_sum, family = "binomial")
health_layer2 <- glm(as.numeric(children_health_harmed=="Agree" | children_health_harmed=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 +  number_children + paroverall + child_symps + child_screen + child_bll + child_rash + child_learning + child_hyper + child_irritable, data = child_adult_sum, family = "binomial")

subdat <- data.frame("Outcome" = rep("Children's Health Harmed", 15), "Variable" = c("Guardian Age", "Guardian Male", "Guardian Race-Other", "Guardian Race-White", "Public Benefits", "Number of confidants", "Number of children", "Number of adult symptoms", "Number of child symptoms", "Child screened", "Child with BLL", "Child with Rash", "Child with Learning", "Child with Hyper", "Child with Irritability"), "Estimate" = c(summary(health_layer1)$coefficients[-1,1], summary(health_layer2)$coefficients[9:16,1]), "StErr" = c(summary(health_layer1)$coefficients[-1,2], summary(health_layer2)$coefficients[9:16,2]), "Pvalue" = c(summary(health_layer1)$coefficients[-1,4], summary(health_layer2)$coefficients[9:16,4]))

effects_mat <- rbind(effects_mat, subdat)

##Outcome: having trust in government
trust_layer1 <- glm(as.numeric(trust_government_in_future=="Agree" | trust_government_in_future=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 + number_children, data = child_adult_sum, family = "binomial")
trust_layer2 <- glm(as.numeric(trust_government_in_future=="Agree" | trust_government_in_future=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 +  number_children + paroverall + child_symps + child_screen + child_bll + child_rash + child_learning + child_hyper + child_irritable, data = child_adult_sum, family = "binomial")

subdat <- data.frame("Outcome" = rep("Trust government", 15), "Variable" = c("Guardian Age", "Guardian Male", "Guardian Race-Other", "Guardian Race-White", "Public Benefits", "Number of confidants", "Number of children", "Number of adult symptoms", "Number of child symptoms", "Child screened", "Child with BLL", "Child with Rash", "Child with Learning", "Child with Hyper", "Child with Irritability"), "Estimate" = c(summary(trust_layer1)$coefficients[-1,1], summary(trust_layer2)$coefficients[9:16,1]), "StErr" = c(summary(trust_layer1)$coefficients[-1,2], summary(trust_layer2)$coefficients[9:16,2]), "Pvalue" = c(summary(trust_layer1)$coefficients[-1,4], summary(trust_layer2)$coefficients[9:16,4]))

effects_mat <- rbind(effects_mat, subdat)

##Outcome: PTSD
ptsd_layer1 <- glm(as.numeric(ptsdscore >= 3) ~ age.y + gendercollapse + collapserace + pubben + confidants2 + number_children, data = child_adult_sum, family = "binomial")
ptsd_layer2 <- glm(as.numeric(ptsdscore >= 3) ~ age.y + gendercollapse + collapserace + pubben + confidants2 +  number_children + paroverall + child_symps + child_screen + child_bll + child_rash + child_learning + child_hyper + child_irritable, data = child_adult_sum, family = "binomial")

subdat <- data.frame("Outcome" = rep("PTSD", 15), "Variable" = c("Guardian Age", "Guardian Male", "Guardian Race-Other", "Guardian Race-White", "Public Benefits", "Number of confidants", "Number of children", "Number of adult symptoms", "Number of child symptoms", "Child screened", "Child with BLL", "Child with Rash", "Child with Learning", "Child with Hyper", "Child with Irritability"), "Estimate" = c(summary(ptsd_layer1)$coefficients[-1,1], summary(ptsd_layer2)$coefficients[9:16,1]), "StErr" = c(summary(ptsd_layer1)$coefficients[-1,2], summary(ptsd_layer2)$coefficients[9:16,2]), "Pvalue" = c(summary(ptsd_layer1)$coefficients[-1,4], summary(ptsd_layer2)$coefficients[9:16,4]))

effects_mat <- rbind(effects_mat, subdat)

##Outcome: PHQ
phq_layer1 <- glm(as.numeric(phq >= 6) ~ age.y + gendercollapse + collapserace + pubben + confidants2 + number_children, data = child_adult_sum, family = "binomial")
phq_layer2 <- glm(as.numeric(phq >= 6) ~ age.y + gendercollapse + collapserace + pubben + confidants2 +  number_children + paroverall + child_symps + child_screen + child_bll + child_rash + child_learning + child_hyper + child_irritable, data = child_adult_sum, family = "binomial")

subdat <- data.frame("Outcome" = rep("Depression", 15), "Variable" = c("Guardian Age", "Guardian Male", "Guardian Race-Other", "Guardian Race-White", "Public Benefits", "Number of confidants", "Number of children", "Number of adult symptoms", "Number of child symptoms", "Child screened", "Child with BLL", "Child with Rash", "Child with Learning", "Child with Hyper", "Child with Irritability"), "Estimate" = c(summary(phq_layer1)$coefficients[-1,1], summary(phq_layer2)$coefficients[9:16,1]), "StErr" = c(summary(phq_layer1)$coefficients[-1,2], summary(phq_layer2)$coefficients[9:16,2]), "Pvalue" = c(summary(phq_layer1)$coefficients[-1,4], summary(phq_layer2)$coefficients[9:16,4]))

effects_mat <- rbind(effects_mat, subdat)
```

Now we tidy up our effects matrix and apply a multiple testing correction:
```{r, echo=TRUE, message=FALSE, warning=FALSE}
effects_mat$BHpvalue <- p.adjust(effects_mat$Pvalue, method="BH")

effects_mat$lower <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate - 1.96*effects_mat$StErr,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate - 1.96*effects_mat$StErr)
)

effects_mat$upper <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate + 1.96*effects_mat$StErr,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate + 1.96*effects_mat$StErr)
)

effects_mat$effect <- case_when(
  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate,
  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate)
)

effects_mat$label <- paste0(round(effects_mat$effect, digits=1), " (", round(effects_mat$lower, digits = 1), ", ", round(effects_mat$upper, digits = 1), ")")

pretty_effects <- select(effects_mat, Outcome, Variable, label, BHpvalue)
```

### 2020-11-23 papertwo_child_health.Rmd
Updating decision to drop adult mental health outcomes from child paper.

@@
 
-And now modeling for adult experiences:
+Now we tidy up our effects matrix and apply a multiple testing correction:
+```{r, echo=TRUE, message=FALSE, warning=FALSE}
+effects_mat$BHpvalue <- p.adjust(effects_mat$Pvalue, method="BH")
+
+effects_mat$lower <- case_when(
+  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate - 1.96*effects_mat$StErr,
+  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate - 1.96*effects_mat$StErr)
+)
+
+effects_mat$upper <- case_when(
+  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate + 1.96*effects_mat$StErr,
+  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate + 1.96*effects_mat$StErr)
+)
+
+effects_mat$effect <- case_when(
+  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate,
+  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate)
+)
+
+effects_mat$label <- paste0(round(effects_mat$effect, digits=1), " (", round(effects_mat$lower, digits = 1), ", ", round(effects_mat$upper, digits = 1), ")")
+
+pretty_effects <- select(effects_mat, Outcome, Variable, label, BHpvalue)
+```
+
+And now modeling for adult experiences (dropped from paper 2; will be used elsewhere:
 ```{r, echo=TRUE, message=FALSE, warning=FALSE}
@@
 ```
-
-Now we tidy up our effects matrix and apply a multiple testing correction:
-```{r, echo=TRUE, message=FALSE, warning=FALSE}
-effects_mat$BHpvalue <- p.adjust(effects_mat$Pvalue, method="BH")
-
-effects_mat$lower <- case_when(
-  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate - 1.96*effects_mat$StErr,
-  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate - 1.96*effects_mat$StErr)
-)
-
-effects_mat$upper <- case_when(
-  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate + 1.96*effects_mat$StErr,
-  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate + 1.96*effects_mat$StErr)
-)
-
-effects_mat$effect <- case_when(
-  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate,
-  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate)
-)
-
-effects_mat$label <- paste0(round(effects_mat$effect, digits=1), " (", round(effects_mat$lower, digits = 1), ", ", round(effects_mat$upper, digits = 1), ")")
-
-pretty_effects <- select(effects_mat, Outcome, Variable, label, BHpvalue)
-```

### 2020-12-23 paperthree_politics.Rmd
Updates to include our third paper on politics.

---
title: "Manuscript 3: Political Beliefs and Attitudes"
author: "Elizabeth Chase"
date: "12/10/2020"
output: pdf_document
---

```{r setup, include=FALSE, echo=TRUE}
library(knitr)
opts_chunk$set(collapse=TRUE, fig.align='center', out.extra = '', fig.pos= "h", tidy=TRUE, tidy.opts=list(blank=TRUE, width.cutoff=40), warning=FALSE,message=FALSE)
options(scipen=999)

rm(list=ls())

library(gridExtra)
library(RColorBrewer)
library(tableone)
library(latex2exp)
library(labelled)
library(kableExtra)
library(logistf)
library(MASS)
library(tidyverse)

load("~/Desktop/Research/Jerel Flint/Analyses/child_long.RData")
load("~/Desktop/Research/Jerel Flint/Analyses/adult_data_eliz_fixed.RData")

child_final$gettested <- ifelse(child_final$blood_test_after_april_2014=="Yes" & child_final$blood_test_before_april_2014=="No", 1, ifelse(is.na(child_final$blood_test_after_april_2014) | is.na(child_final$blood_test_before_april_2014), NA_real_, 0))

child_final$elevbll <- ifelse(child_final$elevated_lead_after_april_2014=="Yes" & child_final$elevated_lead_before_april_2014=="No", 1, ifelse(is.na(child_final$elevated_lead_after_april_2014) | is.na(child_final$elevated_lead_before_april_2014), NA_real_, 0))

child_final$rash <- ifelse(child_final$rash_after_april_2014=="Yes" & child_final$rash_before_april_2014=="No", 1, ifelse(is.na(child_final$rash_after_april_2014) | is.na(child_final$rash_before_april_2014), NA_real_, 0))

child_final$hair <- ifelse(child_final$hairloss_after_april_2014=="Yes" & child_final$hairloss_before_april_2014=="No", 1, ifelse(is.na(child_final$hairloss_after_april_2014) | is.na(child_final$hairloss_before_april_2014), NA_real_, 0))

child_final$learn <- ifelse(child_final$learning_after_april_2014=="Yes" & child_final$learning_before_april_2014=="No", 1, ifelse(is.na(child_final$learning_after_april_2014) | is.na(child_final$learning_before_april_2014), NA_real_, 0))

child_final$hyper <- ifelse(child_final$hyper_after_april_2014=="Yes" & child_final$hyper_before_april_2014=="No", 1, ifelse(is.na(child_final$hyper_after_april_2014) | is.na(child_final$hyper_before_april_2014), NA_real_, 0))

child_final$irritable <- ifelse(child_final$irritable_after_april_2014=="Yes" & child_final$irritable_before_april_2014=="No", 1, ifelse(is.na(child_final$irritable_after_april_2014) | is.na(child_final$irritable_before_april_2014), NA_real_, 0))

symp_sub <- select(child_final, gettested, elevbll, rash, hair, learn, hyper, irritable)

symp_sub$overall_symp <- rowSums(symp_sub, na.rm=TRUE)
symp_sub$unique_id <- child_final$unique_id

symp_collapse <- group_by(symp_sub, unique_id) %>% summarise(child_test = sum(gettested, na.rm=TRUE), child_bll = sum(elevbll, na.rm=TRUE), child_rash = sum(rash, na.rm=TRUE), child_hair = sum(hair, na.rm=TRUE), child_learn = sum(learn, na.rm=TRUE), child_hyper = sum(hyper, na.rm=TRUE), child_irritable = sum(irritable, na.rm=TRUE), child_overall = sum(overall_symp, na.rm=TRUE))

symp_collapse$any_child_test <- ifelse(symp_collapse$child_test > 0, 1, 0)
symp_collapse$any_child_bll <- ifelse(symp_collapse$child_bll > 0, 1, 0)
symp_collapse$any_child_rash <- ifelse(symp_collapse$child_rash > 0, 1, 0)
symp_collapse$any_child_hair <- ifelse(symp_collapse$child_hair > 0, 1, 0)
symp_collapse$any_child_learn <- ifelse(symp_collapse$child_learn > 0, 1, 0)
symp_collapse$any_child_hyper <- ifelse(symp_collapse$child_hyper > 0, 1, 0)
symp_collapse$any_child_irritable <- ifelse(symp_collapse$child_irritable > 0, 1, 0)
symp_collapse$any_child_overall <- ifelse(symp_collapse$child_overall > 0, 1, 0)

adult_clean_eliz$bloodtest <- ifelse(adult_clean_eliz$blood_test_after_april_2014=="Yes" & adult_clean_eliz$blood_test_before_april_2014=="No", 1, ifelse(is.na(adult_clean_eliz$blood_test_after_april_2014) | is.na(adult_clean_eliz$blood_test_before_april_2014), NA_real_, 0))
adult_clean_eliz$elev_bll <- ifelse(adult_clean_eliz$elevated_lead_after_april_2014=="Yes" & adult_clean_eliz$elevated_lead_before_april_2014=="No", 1, ifelse(is.na(adult_clean_eliz$elevated_lead_after_april_2014) | is.na(adult_clean_eliz$elevated_lead_before_april_2014), NA_real_, 0))
adult_clean_eliz$rashes <- ifelse(adult_clean_eliz$rashes_after_april_2014=="Yes" & adult_clean_eliz$rashes_before_april_2014=="No", 1, ifelse(is.na(adult_clean_eliz$rashes_after_april_2014) | is.na(adult_clean_eliz$rashes_before_april_2014), NA_real_, 0))
adult_clean_eliz$hairloss <- ifelse(adult_clean_eliz$hairloss_after_april_2014=="Yes" & adult_clean_eliz$hairloss_before_april_2014=="No", 1, ifelse(is.na(adult_clean_eliz$hairloss_after_april_2014) | is.na(adult_clean_eliz$hairloss_before_april_2014), NA_real_, 0))
adult_clean_eliz$nausea <- ifelse(adult_clean_eliz$nausea_after_april_2014=="Yes" & adult_clean_eliz$nausea_before_april_2014=="No", 1, ifelse(is.na(adult_clean_eliz$nausea_after_april_2014) | is.na(adult_clean_eliz$nausea_before_april_2014), NA_real_, 0))
adult_clean_eliz$irritable <- ifelse(adult_clean_eliz$irritable_after_april_2014=="Yes" & adult_clean_eliz$irritable_before_april_2014=="No", 1, ifelse(is.na(adult_clean_eliz$irritable_after_april_2014) | is.na(adult_clean_eliz$irritable_before_april_2014), NA_real_, 0))

symp_sub2 <- select(adult_clean_eliz, bloodtest, elev_bll, rashes, hairloss, nausea, irritable)
adult_clean_eliz$overall_symps <- rowSums(symp_sub2, na.rm=TRUE)
adult_clean_eliz$any_symps <- ifelse(adult_clean_eliz$overall_symps > 0, 1, 0)

subadult <- select(adult_clean_eliz, inclusion, unique_id, age, gender, collapserace, collapseeduc, have_health_insurance, public_benefits, years_cityflint, current_zip, intent_harm, water_exaggerated, children_health_harmed, discriminatory_poor, racially_motivated, trust_government_in_future, drink_tap_in_three_years, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, political_affiliation, nightmares, avoided_thinking_crisis, onguard_watchful, numb_detached, felt_guilty, days_nervous_2weeks, days_worrying_2weeks, days_nopleasure_2weeks, days_depressed_2weeks, ptsdscore, phq, confidants2, number_children, employ_status, bloodtest, elev_bll, rashes, hairloss, nausea, irritable, overall_symps, any_symps)

adult_child <- left_join(subadult, symp_collapse, by=c("unique_id"))

adult_child$any_child_test <- ifelse(adult_child$number_children==0, 0, adult_child$any_child_test)
adult_child$child_test <- ifelse(adult_child$number_children==0, 0, adult_child$child_test)
adult_child$any_child_bll <- ifelse(adult_child$number_children==0, 0, adult_child$any_child_bll)
adult_child$child_bll <- ifelse(adult_child$number_children==0, 0, adult_child$child_bll)
adult_child$any_child_rash <- ifelse(adult_child$number_children==0, 0, adult_child$any_child_rash)
adult_child$child_rash <- ifelse(adult_child$number_children==0, 0, adult_child$child_rash)
adult_child$any_child_hair <- ifelse(adult_child$number_children==0, 0, adult_child$any_child_hair)
adult_child$child_hair <- ifelse(adult_child$number_children==0, 0, adult_child$child_hair)
adult_child$any_child_learn <- ifelse(adult_child$number_children==0, 0, adult_child$any_child_learn)
adult_child$child_learn <- ifelse(adult_child$number_children==0, 0, adult_child$child_learn)
adult_child$any_child_hyper <- ifelse(adult_child$number_children==0, 0, adult_child$any_child_hyper)
adult_child$child_hyper <- ifelse(adult_child$number_children==0, 0, adult_child$child_hyper)
adult_child$any_child_irritable <- ifelse(adult_child$number_children==0, 0, adult_child$any_child_irritable)
adult_child$child_irritable <- ifelse(adult_child$number_children==0, 0, adult_child$child_irritable)
adult_child$any_child_overall <- ifelse(adult_child$number_children==0, 0, adult_child$any_child_overall)
adult_child$child_overall <- ifelse(adult_child$number_children==0, 0, adult_child$child_overall)

adult_child$intent_harm_tri <- case_when(
  adult_child$intent_harm=="Strongly Disagree" | adult_child$intent_harm=="Disagree" ~ "Disagree",
  adult_child$intent_harm=="Neutral" ~ "Neutral",
  adult_child$intent_harm=="Agree" | adult_child$intent_harm=="Strongly Agree" ~ "Agree",
  is.na(adult_child$intent_harm) ~ NA_character_
)

adult_child$water_exaggerated_tri <- case_when(
  adult_child$water_exaggerated=="Strongly Disagree" | adult_child$water_exaggerated=="Disagree" ~ "Disagree",
  adult_child$water_exaggerated=="Neutral" ~ "Neutral",
  adult_child$water_exaggerated=="Agree" | adult_child$water_exaggerated=="Strongly Agree" ~ "Agree",
  is.na(adult_child$water_exaggerated) ~ NA_character_
)

adult_child$children_health_harmed_tri <- case_when(
  adult_child$children_health_harmed=="Strongly Disagree" | adult_child$children_health_harmed=="Disagree" ~ "Disagree",
  adult_child$children_health_harmed=="Neutral" ~ "Neutral",
  adult_child$children_health_harmed=="Agree" | adult_child$children_health_harmed=="Strongly Agree" ~ "Agree",
  is.na(adult_child$children_health_harmed) ~ NA_character_
)

adult_child$discriminatory_poor_tri <- case_when(
  adult_child$discriminatory_poor=="Strongly Disagree" | adult_child$discriminatory_poor=="Disagree" ~ "Disagree",
  adult_child$discriminatory_poor=="Neutral" ~ "Neutral",
  adult_child$discriminatory_poor=="Agree" | adult_child$discriminatory_poor=="Strongly Agree" ~ "Agree",
  is.na(adult_child$discriminatory_poor) ~ NA_character_
)

adult_child$racially_motivated_tri <- case_when(
  adult_child$racially_motivated=="Strongly Disagree" | adult_child$racially_motivated=="Disagree" ~ "Disagree",
  adult_child$racially_motivated=="Neutral" ~ "Neutral",
  adult_child$racially_motivated=="Agree" | adult_child$racially_motivated=="Strongly Agree" ~ "Agree",
  is.na(adult_child$racially_motivated) ~ NA_character_
)

adult_child$trust_government_in_future_tri <- case_when(
  adult_child$trust_government_in_future=="Strongly Disagree" | adult_child$trust_government_in_future=="Disagree" ~ "Disagree",
  adult_child$trust_government_in_future=="Neutral" ~ "Neutral",
  adult_child$trust_government_in_future=="Agree" | adult_child$trust_government_in_future=="Strongly Agree" ~ "Agree",
  is.na(adult_child$trust_government_in_future) ~ NA_character_
)

adult_child$drink_tap_in_three_years_tri <- case_when(
  adult_child$drink_tap_in_three_years=="Strongly Disagree" | adult_child$drink_tap_in_three_years=="Disagree" ~ "Disagree",
  adult_child$drink_tap_in_three_years=="Neutral" ~ "Neutral",
  adult_child$drink_tap_in_three_years=="Agree" | adult_child$drink_tap_in_three_years=="Strongly Agree" ~ "Agree",
  is.na(adult_child$drink_tap_in_three_years) ~ NA_character_
)

adult_child$satisfied_flint_government_tri <- case_when(
  adult_child$satisfied_flint_government=="Strongly Disagree" | adult_child$satisfied_flint_government=="Disagree" ~ "Disagree",
  adult_child$satisfied_flint_government=="Neutral" ~ "Neutral",
  adult_child$satisfied_flint_government=="Agree" | adult_child$satisfied_flint_government=="Strongly Agree" ~ "Agree",
  is.na(adult_child$satisfied_flint_government) ~ NA_character_
)

adult_child$satisfied_state_government_tri <- case_when(
  adult_child$satisfied_state_government=="Strongly Disagree" | adult_child$satisfied_state_government=="Disagree" ~ "Disagree",
  adult_child$satisfied_state_government=="Neutral" ~ "Neutral",
  adult_child$satisfied_state_government=="Agree" | adult_child$satisfied_state_government=="Strongly Agree" ~ "Agree",
  is.na(adult_child$satisfied_state_government) ~ NA_character_
)

adult_child$satisfied_federal_government_tri <- case_when(
  adult_child$satisfied_federal_government=="Strongly Disagree" | adult_child$satisfied_federal_government=="Disagree" ~ "Disagree",
  adult_child$satisfied_federal_government=="Neutral" ~ "Neutral",
  adult_child$satisfied_federal_government=="Agree" | adult_child$satisfied_federal_government=="Strongly Agree" ~ "Agree",
  is.na(adult_child$satisfied_federal_government) ~ NA_character_
)

adult_child$gendercollapse <- ifelse(adult_child$gender=="Transgender Woman" | adult_child$gender=="Female", "Female", ifelse(is.na(adult_child$gender), NA_character_, "Male"))

rm(list=c("adult_clean_eliz", "subadult", "child_final", "symp_collapse", "symp_sub", "symp_sub2"))
```

First, we get the baseline tables and descriptives:
```{r, include=FALSE, echo=TRUE}
var_label(adult_child$age) <- "Age"
var_label(adult_child$gendercollapse) <- "Gender"
var_label(adult_child$collapserace) <- "Race"
var_label(adult_child$collapseeduc) <- "Education"
var_label(adult_child$have_health_insurance) <- "Health insurance"
var_label(adult_child$public_benefits) <- "Public benefits status"
var_label(adult_child$current_zip) <- "Zip code"
var_label(adult_child$years_cityflint) <- "Years lived in Flint"
var_label(adult_child$intent_harm_tri) <- "The water source switch was intended to harm Flint residents."
var_label(adult_child$water_exaggerated_tri) <- "People have made the water issues a bigger deal than reality."
var_label(adult_child$children_health_harmed_tri) <- "Children in Flint are going to have health problems in future due to the water crisis."
var_label(adult_child$discriminatory_poor_tri) <- "The water source switch was discriminatory against lower income Flint residents."
var_label(adult_child$racially_motivated_tri) <- "The water source switch was racially motivated."
var_label(adult_child$trust_government_in_future_tri) <- "I am likely to trust the government on water/environmental issues in future."
var_label(adult_child$drink_tap_in_three_years_tri) <- "Three years from now, I am likely to drink primarily tap water at home."
var_label(adult_child$satisfied_federal_government_tri) <- "I am satisfied with the federal government's role in addressing the Flint water issues."
var_label(adult_child$satisfied_flint_government_tri) <- "I am satisfied with the Flint government's role in addressing the Flint water issues."
var_label(adult_child$satisfied_state_government_tri) <- "I am satisfied with the Michigan government's role in addressing the Flint water issues."
var_label(adult_child$political_affiliation) <- "Political affiliation"
var_label(adult_child$nightmares) <- "In the last month, I have had nightmares about the water crisis."
var_label(adult_child$avoided_thinking_crisis) <- "In the last month, I have avoided thinking about the water crisis."
var_label(adult_child$onguard_watchful) <- "In the last month, I have been constantly on guard."
var_label(adult_child$numb_detached) <- "In the last month, I have felt numb/detached from my surroundings."
var_label(adult_child$felt_guilty) <- "In the last month, I have felt guilty about the water crisis."
var_label(adult_child$days_nervous_2weeks) <- "In the last two weeks, how many days have you felt nervous?"
var_label(adult_child$days_worrying_2weeks) <- "In the last two weeks, how many days have you worried uncontrollably?"
var_label(adult_child$days_nopleasure_2weeks) <- "In the last two weeks, how many days have you felt little interest/pleasure in doing things?"
var_label(adult_child$days_depressed_2weeks) <- "In the last two weeks, how many days have you felt depressed?"
var_label(adult_child$ptsdscore) <- "PTSD-5 Score"
var_label(adult_child$phq) <- "PHQ-4 Score"
var_label(adult_child$confidants2) <- "Number of confidants"
var_label(adult_child$number_children) <- "Number of children in care"
var_label(adult_child$employ_status) <- "Employment status"
var_label(adult_child$overall_symps) <- "Number of symptoms experienced"

adult_child$any_symps <- factor(adult_child$any_symps, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$any_child_test <- factor(adult_child$any_child_test, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$any_child_bll <- factor(adult_child$any_child_bll, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$any_child_rash <- factor(adult_child$any_child_rash, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$any_child_hair <- factor(adult_child$any_child_hair, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$any_child_learn <- factor(adult_child$any_child_learn, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$any_child_hyper <- factor(adult_child$any_child_hyper, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$any_child_irritable <- factor(adult_child$any_child_irritable, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$any_child_overall <- factor(adult_child$any_child_overall, levels=c(0, 1), labels=c("No", "Yes"))
var_label(adult_child$any_symps) <- "Experienced any symptoms?"
var_label(adult_child$any_child_test) <- "Have at least one child tested for BLLs?"
var_label(adult_child$any_child_bll) <- "Have at least one child with elevated BLLs?"
var_label(adult_child$any_child_rash) <- "Have at least one child with rash?"
var_label(adult_child$any_child_hair) <- "Have at least one child with hair loss?"
var_label(adult_child$any_child_learn) <- "Have at least one child with learning delays?"
var_label(adult_child$any_child_hyper) <- "Have at least one child with hyperactivity?"
var_label(adult_child$any_child_irritable) <- "Have at least one child with irritability?"
var_label(adult_child$any_child_overall) <- "Have at least one child experience any symptom?"

adult_child$bloodtest <- factor(adult_child$bloodtest, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$elev_bll <- factor(adult_child$elev_bll, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$rashes <- factor(adult_child$rashes, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$hairloss <- factor(adult_child$hairloss, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$nausea <- factor(adult_child$nausea, levels=c(0, 1), labels=c("No", "Yes"))
adult_child$irritable <- factor(adult_child$irritable, levels=c(0, 1), labels=c("No", "Yes"))
var_label(adult_child$bloodtest) <- "Tested for BLLs?"
var_label(adult_child$elev_bll) <- "Had elevated BLLs?"
var_label(adult_child$rashes) <- "Had rashes?"
var_label(adult_child$hairloss) <- "Had hair loss?"
var_label(adult_child$nausea) <- "Had nausea?"
var_label(adult_child$irritable) <- "Had irritability?"
var_label(adult_child$overall_symps) <- "Total number of symptoms"

table_predictors <- CreateTableOne(vars=c("age", "gendercollapse", "collapseeduc", "have_health_insurance", "public_benefits", "employ_status", "political_affiliation", "years_cityflint", "current_zip", "number_children", "confidants2", "any_symps", "bloodtest", "elev_bll", "rashes", "hairloss", "nausea", "irritable", "overall_symps", "any_child_overall", "any_child_test", "any_child_bll", "any_child_rash", "any_child_hair", "any_child_learn", "any_child_hyper", "any_child_irritable"), strata = "collapserace", data=adult_child, includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

table_predictors_nostrat <- CreateTableOne(vars=c("age", "gendercollapse", "collapseeduc", "have_health_insurance", "public_benefits", "employ_status", "political_affiliation", "years_cityflint", "current_zip", "number_children", "confidants2", "any_symps", "bloodtest", "elev_bll", "rashes", "hairloss", "nausea", "irritable", "overall_symps", "any_child_overall", "any_child_test", "any_child_bll", "any_child_rash", "any_child_hair", "any_child_learn", "any_child_hyper", "any_child_irritable"), data=adult_child, includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

table_outcomes <- CreateTableOne(vars=c("intent_harm_tri", "water_exaggerated_tri", "children_health_harmed_tri", "discriminatory_poor_tri", "racially_motivated_tri", "trust_government_in_future_tri", "drink_tap_in_three_years_tri", "satisfied_federal_government_tri", "satisfied_state_government_tri", "satisfied_flint_government_tri", "nightmares", "avoided_thinking_crisis", "onguard_watchful", "numb_detached", "felt_guilty", "days_nervous_2weeks", "days_worrying_2weeks", "days_nopleasure_2weeks", "days_depressed_2weeks", "ptsdscore", "phq"), strata = "collapserace", data=adult_child, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

table_outcomes_nostrat <- CreateTableOne(vars=c("intent_harm_tri", "water_exaggerated_tri", "children_health_harmed_tri", "discriminatory_poor_tri", "racially_motivated_tri", "trust_government_in_future_tri", "drink_tap_in_three_years_tri", "satisfied_federal_government_tri", "satisfied_state_government_tri", "satisfied_flint_government_tri", "nightmares", "avoided_thinking_crisis", "onguard_watchful", "numb_detached", "felt_guilty", "days_nervous_2weeks", "days_worrying_2weeks", "days_nopleasure_2weeks", "days_depressed_2weeks", "ptsdscore", "phq"), data=adult_child, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)

kable(print(table_predictors, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(5:9, 11:13, 15:17, 19:23, 25:29, 32:38, 43:45, 47:49, 51:53, 55:57, 59:61, 63:65)) %>% kable_styling(position="center")

kable(print(table_predictors_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(5:9, 11:13, 15:17, 19:23, 25:29, 32:38, 43:45, 47:49, 51:53, 55:57, 59:61, 63:65)) %>% kable_styling(position="center")

kable(print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:5, 7:9, 11:13, 15:17, 19:21, 23:25, 27:30, 32:34, 36:38, 40:42, 49:53, 55:59, 61:65, 67:71)) %>% kable_styling(position="center")

kable(print(table_outcomes_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:5, 7:9, 11:13, 15:17, 19:21, 23:25, 27:30, 32:34, 36:38, 40:42, 49:53, 55:59, 61:65, 67:71)) %>% kable_styling(position="center")
```

Now, we start fitting the trinary proportional odds models that Jerel wanted to see for the mental health/attitudes outcomes:
```{r, include=FALSE, echo=TRUE}
adult_child$zipcollapse <- case_when(
  adult_child$current_zip==48502 ~"48503", 
  adult_child$current_zip!=48502 ~ as.character(adult_child$current_zip)
)

adult_child$partycollapse <- ifelse(adult_child$political_affiliation=="An Independent" | adult_child$political_affiliation=="Other", "Other", adult_child$political_affiliation)

adult_child$pubbencollapse <- case_when(
  adult_child$public_benefits=="Don't know/Unsure" | adult_child$public_benefits=="No" ~ "No/Unsure",
  adult_child$public_benefits=="Yes" ~ "Yes",
  is.na(adult_child$public_benefits) ~ NA_character_)

effects <- data.frame("Outcome" = NA, "Predictor" = NA, "Effect" = NA, "SE" = NA)

intent_model_layer1 <- polr(factor(intent_harm_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(intent_model_layer1)

intent_model_layer2 <- polr(factor(intent_harm_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(intent_model_layer2)

subdat <- data.frame("Outcome" = rep("The water source switch was intended to harm Flint residents.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(intent_model_layer1)$coefficients[1:14, 1], summary(intent_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(intent_model_layer1)$coefficients[1:14, 2], summary(intent_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

exag_model_layer1 <- polr(factor(water_exaggerated_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(exag_model_layer1)

exag_model_layer2 <- polr(factor(water_exaggerated_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(exag_model_layer2)

subdat <- data.frame("Outcome" = rep("People have made the water issues a bigger deal than reality.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(exag_model_layer1)$coefficients[1:14, 1], summary(exag_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(exag_model_layer1)$coefficients[1:14, 2], summary(exag_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

harm_model_layer1 <- polr(factor(children_health_harmed_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(harm_model_layer1)

harm_model_layer2 <- polr(factor(children_health_harmed_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(harm_model_layer2)

subdat <- data.frame("Outcome" = rep("Children in Flint are going to have health problems in future due to the water crisis.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(harm_model_layer1)$coefficients[1:14, 1], summary(harm_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(harm_model_layer1)$coefficients[1:14, 2], summary(harm_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

poor_model_layer1 <- polr(factor(discriminatory_poor_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(poor_model_layer1)

poor_model_layer2 <- polr(factor(discriminatory_poor_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(poor_model_layer2)

subdat <- data.frame("Outcome" = rep("The water source switch was discriminatory against lower income Flint residents.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(poor_model_layer1)$coefficients[1:14, 1], summary(poor_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(poor_model_layer1)$coefficients[1:14, 2], summary(poor_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

race_model_layer1 <- polr(factor(racially_motivated_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(race_model_layer1)

race_model_layer2 <- polr(factor(racially_motivated_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(race_model_layer2)

subdat <- data.frame("Outcome" = rep("The water source switch was racially motivated.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(race_model_layer1)$coefficients[1:14, 1], summary(race_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(race_model_layer1)$coefficients[1:14, 2], summary(race_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

trust_model_layer1 <- polr(factor(trust_government_in_future_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(trust_model_layer1)

trust_model_layer2 <- polr(factor(trust_government_in_future_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(trust_model_layer2)

subdat <- data.frame("Outcome" = rep("I am likely to trust the government on water/environmental issues in future.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(trust_model_layer1)$coefficients[1:14, 1], summary(trust_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(trust_model_layer1)$coefficients[1:14, 2], summary(trust_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

drink_model_layer1 <- polr(factor(drink_tap_in_three_years_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(drink_model_layer1)

drink_model_layer2 <- polr(factor(drink_tap_in_three_years_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(drink_model_layer2)

subdat <- data.frame("Outcome" = rep("Three years from now, I am likely to drink primarily tap water at home.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(drink_model_layer1)$coefficients[1:14, 1], summary(drink_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(drink_model_layer1)$coefficients[1:14, 2], summary(drink_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

fedsatis_model_layer1 <- polr(factor(satisfied_federal_government_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(fedsatis_model_layer1)

fedsatis_model_layer2 <- polr(factor(satisfied_federal_government_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(fedsatis_model_layer2)

subdat <- data.frame("Outcome" = rep("I am satisfied with the federal government's role in addressing the Flint water issues.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(fedsatis_model_layer1)$coefficients[1:14, 1], summary(fedsatis_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(fedsatis_model_layer1)$coefficients[1:14, 2], summary(fedsatis_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

statesatis_model_layer1 <- polr(factor(satisfied_state_government_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(statesatis_model_layer1)

statesatis_model_layer2 <- polr(factor(satisfied_state_government_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(statesatis_model_layer2)

subdat <- data.frame("Outcome" = rep("I am satisfied with the Michigan government's role in addressing the Flint water issues.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(statesatis_model_layer1)$coefficients[1:14, 1], summary(statesatis_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(statesatis_model_layer1)$coefficients[1:14, 2], summary(statesatis_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

flintsatis_model_layer1 <- polr(factor(satisfied_flint_government_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(flintsatis_model_layer1)

flintsatis_model_layer2 <- polr(factor(satisfied_flint_government_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(flintsatis_model_layer2)

subdat <- data.frame("Outcome" = rep("I am satisfied with the Flint government's role in addressing the Flint water issues.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(flintsatis_model_layer1)$coefficients[1:14, 1], summary(flintsatis_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(flintsatis_model_layer1)$coefficients[1:14, 2], summary(flintsatis_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

adult_child$nightmares_fac <- case_when(
  adult_child$nightmares=="Yes" ~ 1,
  adult_child$nightmares=="No" ~ 0,
  is.na(adult_child$nightmares)~ NA_real_
)

nightmares_model_layer1 <- glm(nightmares_fac ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child)

summary(nightmares_model_layer1)

nightmares_model_layer2 <- glm(nightmares_fac ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child)

summary(nightmares_model_layer2)

subdat <- data.frame("Outcome" = rep("In the last month, I have had nightmares about the water crisis.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(nightmares_model_layer1)$coefficients[2:15, 1], summary(nightmares_model_layer2)$coefficients[16:17, 1]), "SE" = c(summary(nightmares_model_layer1)$coefficients[2:15, 2], summary(nightmares_model_layer2)$coefficients[16:17, 2]))

effects <- rbind(effects, subdat)

adult_child$avoided_fac <- case_when(
  adult_child$avoided_thinking_crisis=="Yes" ~ 1,
  adult_child$avoided_thinking_crisis=="No" ~ 0,
  is.na(adult_child$avoided_thinking_crisis)~ NA_real_
)

avoid_model_layer1 <- glm(avoided_fac ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child)

summary(avoid_model_layer1)

avoid_model_layer2 <- glm(avoided_fac ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child)

summary(avoid_model_layer2)

subdat <- data.frame("Outcome" = rep("In the last month, I have avoided thinking about the water crisis.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(avoid_model_layer1)$coefficients[2:15, 1], summary(avoid_model_layer2)$coefficients[16:17, 1]), "SE" = c(summary(avoid_model_layer1)$coefficients[2:15, 2], summary(avoid_model_layer2)$coefficients[16:17, 2]))

effects <- rbind(effects, subdat)

adult_child$onguard_fac <- case_when(
  adult_child$onguard_watchful=="Yes" ~ 1,
  adult_child$onguard_watchful=="No" ~ 0,
  is.na(adult_child$onguard_watchful)~ NA_real_
)

onguard_model_layer1 <- glm(onguard_fac ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child)

summary(onguard_model_layer1)

onguard_model_layer2 <- glm(onguard_fac ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child)

summary(onguard_model_layer2)

subdat <- data.frame("Outcome" = rep("In the last month, I have been constantly on guard.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(onguard_model_layer1)$coefficients[2:15, 1], summary(onguard_model_layer2)$coefficients[16:17, 1]), "SE" = c(summary(onguard_model_layer1)$coefficients[2:15, 2], summary(onguard_model_layer2)$coefficients[16:17, 2]))

effects <- rbind(effects, subdat)

adult_child$numb_fac <- case_when(
  adult_child$numb_detached=="Yes" ~ 1,
  adult_child$numb_detached=="No" ~ 0,
  is.na(adult_child$numb_detached)~ NA_real_
)

numb_model_layer1 <- glm(numb_fac ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child)

summary(numb_model_layer1)

numb_model_layer2 <- glm(numb_fac ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child)

summary(numb_model_layer2)

subdat <- data.frame("Outcome" = rep("In the last month, I have felt numb/detached from my surroundings.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(numb_model_layer1)$coefficients[2:15, 1], summary(numb_model_layer2)$coefficients[16:17, 1]), "SE" = c(summary(numb_model_layer1)$coefficients[2:15, 2], summary(numb_model_layer2)$coefficients[16:17, 2]))

effects <- rbind(effects, subdat)

adult_child$guilt_fac <- case_when(
  adult_child$felt_guilty=="Yes" ~ 1,
  adult_child$felt_guilty=="No" ~ 0,
  is.na(adult_child$felt_guilty)~ NA_real_
)

guilt_model_layer1 <- glm(guilt_fac ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child)

summary(guilt_model_layer1)

guilt_model_layer2 <- glm(guilt_fac ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child)

summary(guilt_model_layer2)

subdat <- data.frame("Outcome" = rep("In the last month, I have felt guilty about the water crisis.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(guilt_model_layer1)$coefficients[2:15, 1], summary(guilt_model_layer2)$coefficients[16:17, 1]), "SE" = c(summary(guilt_model_layer1)$coefficients[2:15, 2], summary(guilt_model_layer2)$coefficients[16:17, 2]))

effects <- rbind(effects, subdat)

nervous_model_layer1 <- polr(factor(days_nervous_2weeks, levels=c("Not at all", "Several days", "More than half the days", "Nearly every day"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(nervous_model_layer1)

nervous_model_layer2 <- polr(factor(days_nervous_2weeks, levels=c("Not at all", "Several days", "More than half the days", "Nearly every day"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(nervous_model_layer2)

subdat <- data.frame("Outcome" = rep("In the last two weeks, how many days have you felt nervous?", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(nervous_model_layer1)$coefficients[1:14, 1], summary(nervous_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(nervous_model_layer1)$coefficients[1:14, 2], summary(nervous_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

worry_model_layer1 <- polr(factor(days_worrying_2weeks, levels=c("Not at all", "Several days", "More than half the days", "Nearly every day"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(worry_model_layer1)

worry_model_layer2 <- polr(factor(days_worrying_2weeks, levels=c("Not at all", "Several days", "More than half the days", "Nearly every day"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(worry_model_layer2)

subdat <- data.frame("Outcome" = rep("In the last two weeks, how many days have you worried uncontrollably?", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(worry_model_layer1)$coefficients[1:14, 1], summary(worry_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(worry_model_layer1)$coefficients[1:14, 2], summary(worry_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

pleasure_model_layer1 <- polr(factor(days_nopleasure_2weeks, levels=c("Not at all", "Several days", "More than half the days", "Nearly every day"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(pleasure_model_layer1)

pleasure_model_layer2 <- polr(factor(days_nopleasure_2weeks, levels=c("Not at all", "Several days", "More than half the days", "Nearly every day"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(pleasure_model_layer2)

subdat <- data.frame("Outcome" = rep("In the last two weeks, how many days have you felt little interest/pleasure in doing things?", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(pleasure_model_layer1)$coefficients[1:14, 1], summary(pleasure_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(pleasure_model_layer1)$coefficients[1:14, 2], summary(pleasure_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

depress_model_layer1 <- polr(factor(days_depressed_2weeks, levels=c("Not at all", "Several days", "More than half the days", "Nearly every day"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child, Hess = TRUE)

summary(depress_model_layer1)

depress_model_layer2 <- polr(factor(days_depressed_2weeks, levels=c("Not at all", "Several days", "More than half the days", "Nearly every day"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child, Hess = TRUE)

summary(depress_model_layer2)

subdat <- data.frame("Outcome" = rep("In the last two weeks, how many days have you felt depressed?", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(depress_model_layer1)$coefficients[1:14, 1], summary(depress_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(depress_model_layer1)$coefficients[1:14, 2], summary(depress_model_layer2)$coefficients[15:16, 2]))

effects <- rbind(effects, subdat)

ptsd_model_layer1 <- lm(ptsdscore ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child)

summary(ptsd_model_layer1)

ptsd_model_layer2 <- lm(ptsdscore ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child)

summary(ptsd_model_layer2)

subdat <- data.frame("Outcome" = rep("PTSD-5 Score", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(ptsd_model_layer1)$coefficients[2:15, 1], summary(ptsd_model_layer2)$coefficients[16:17, 1]), "SE" = c(summary(ptsd_model_layer1)$coefficients[2:15, 2], summary(ptsd_model_layer2)$coefficients[16:17, 2]))

effects <- rbind(effects, subdat)

phq_model_layer1 <- lm(phq ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse, data = adult_child)

summary(phq_model_layer1)

phq_model_layer2 <- lm(phq ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall, data = adult_child)

summary(phq_model_layer2)

subdat <- data.frame("Outcome" = rep("PHQ-4 Score", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(phq_model_layer1)$coefficients[2:15, 1], summary(phq_model_layer2)$coefficients[16:17, 1]), "SE" = c(summary(phq_model_layer1)$coefficients[2:15, 2], summary(phq_model_layer2)$coefficients[16:17, 2]))

effects <- rbind(effects, subdat)
```

Now tidying up all of these effect estimates:
```{r, include=FALSE, echo=TRUE}
effects <- effects[-1,]
effects$Lower_raw <- effects$Effect - 1.96*effects$SE
effects$Upper_raw <- effects$Effect + 1.96*effects$SE
effects$tstat <- effects$Effect/effects$SE
effects$pvalue <- 2*pnorm(abs(effects$tstat), lower.tail = FALSE)

effects$Lower[effects$Outcome=="PHQ-4 Score" | effects$Outcome=="PTSD-5 Score"] <- effects$Lower_raw[effects$Outcome=="PHQ-4 Score" | effects$Outcome=="PTSD-5 Score"]
effects$Upper[effects$Outcome=="PHQ-4 Score" | effects$Outcome=="PTSD-5 Score"] <- effects$Upper_raw[effects$Outcome=="PHQ-4 Score" | effects$Outcome=="PTSD-5 Score"]
effects$Estimate[effects$Outcome=="PHQ-4 Score" | effects$Outcome=="PTSD-5 Score"] <- effects$Effect[effects$Outcome=="PHQ-4 Score" | effects$Outcome=="PTSD-5 Score"]

effects$Lower[effects$Outcome!="PHQ-4 Score" & effects$Outcome!="PTSD-5 Score"] <- exp(effects$Lower_raw[effects$Outcome!="PHQ-4 Score" & effects$Outcome!="PTSD-5 Score"])
effects$Upper[effects$Outcome!="PHQ-4 Score" & effects$Outcome!="PTSD-5 Score"] <- exp(effects$Upper_raw[effects$Outcome!="PHQ-4 Score" & effects$Outcome!="PTSD-5 Score"])
effects$Estimate[effects$Outcome!="PHQ-4 Score" & effects$Outcome!="PTSD-5 Score"] <- exp(effects$Effect[effects$Outcome!="PHQ-4 Score" & effects$Outcome!="PTSD-5 Score"])

effects$BHpvalue <- p.adjust(effects$pvalue, method="BH")

effects$label <- paste0(round(effects$Estimate, digits = 1), ", (", round(effects$Lower, digits = 1), ", ", round(effects$Upper, digits = 1), ")")

prettyeffects <- select(effects, Predictor, Outcome, label, BHpvalue)

sigeffects <- prettyeffects[prettyeffects$BHpvalue < 0.05,]
```

### 2020-12-28 paperthree_politics.Rmd
Deleted extraneous files and added mental health predictors to politics analysis.

@@
 
-subdat <- data.frame("Outcome" = rep("The water source switch was intended to harm Flint residents.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(intent_model_layer1)$coefficients[1:14, 1], summary(intent_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(intent_model_layer1)$coefficients[1:14, 2], summary(intent_model_layer2)$coefficients[15:16, 2]))
+intent_model_layer3 <- polr(factor(intent_harm_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall + ptsdscore + phq, data = adult_child, Hess = TRUE)
+
+summary(intent_model_layer3)
+
+subdat <- data.frame("Outcome" = rep("The water source switch was intended to harm Flint residents.", 18), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom", "PTSD score", "PHQ score"), "Effect" = c(summary(intent_model_layer1)$coefficients[1:14, 1], summary(intent_model_layer2)$coefficients[15:16, 1], summary(intent_model_layer3)$coefficients[17:18,1]), "SE" = c(summary(intent_model_layer1)$coefficients[1:14, 2], summary(intent_model_layer2)$coefficients[15:16, 2], summary(intent_model_layer3)$coefficients[17:18, 2]))
 
@@
 
-subdat <- data.frame("Outcome" = rep("People have made the water issues a bigger deal than reality.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(exag_model_layer1)$coefficients[1:14, 1], summary(exag_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(exag_model_layer1)$coefficients[1:14, 2], summary(exag_model_layer2)$coefficients[15:16, 2]))
+exag_model_layer3 <- polr(factor(water_exaggerated_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall + ptsdscore + phq, data = adult_child, Hess = TRUE)
+
+summary(exag_model_layer3)
+
+subdat <- data.frame("Outcome" = rep("People have made the water issues a bigger deal than reality.", 18), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom", "PTSD score", "PHQ score"), "Effect" = c(summary(exag_model_layer1)$coefficients[1:14, 1], summary(exag_model_layer2)$coefficients[15:16, 1], summary(exag_model_layer3)$coefficients[17:18, 1]), "SE" = c(summary(exag_model_layer1)$coefficients[1:14, 2], summary(exag_model_layer2)$coefficients[15:16, 2], summary(exag_model_layer3)$coefficients[17:18, 2]))
 
@@
 
-subdat <- data.frame("Outcome" = rep("Children in Flint are going to have health problems in future due to the water crisis.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(harm_model_layer1)$coefficients[1:14, 1], summary(harm_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(harm_model_layer1)$coefficients[1:14, 2], summary(harm_model_layer2)$coefficients[15:16, 2]))
+harm_model_layer3 <- polr(factor(children_health_harmed_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall + ptsdscore + phq, data = adult_child, Hess = TRUE)
+
+summary(harm_model_layer3)
+
+subdat <- data.frame("Outcome" = rep("Children in Flint are going to have health problems in future due to the water crisis.", 18), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom", "PTSD score", "PHQ score"), "Effect" = c(summary(harm_model_layer1)$coefficients[1:14, 1], summary(harm_model_layer2)$coefficients[15:16, 1], summary(harm_model_layer3)$coefficients[17:18, 1]), "SE" = c(summary(harm_model_layer1)$coefficients[1:14, 2], summary(harm_model_layer2)$coefficients[15:16, 2], summary(harm_model_layer3)$coefficients[17:18, 2]))
 
@@
 
-subdat <- data.frame("Outcome" = rep("The water source switch was discriminatory against lower income Flint residents.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(poor_model_layer1)$coefficients[1:14, 1], summary(poor_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(poor_model_layer1)$coefficients[1:14, 2], summary(poor_model_layer2)$coefficients[15:16, 2]))
+poor_model_layer3 <- polr(factor(discriminatory_poor_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall + ptsdscore + phq, data = adult_child, Hess = TRUE)
+
+summary(poor_model_layer3)
+
+subdat <- data.frame("Outcome" = rep("The water source switch was discriminatory against lower income Flint residents.", 18), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom", "PTSD score", "PHQ score"), "Effect" = c(summary(poor_model_layer1)$coefficients[1:14, 1], summary(poor_model_layer2)$coefficients[15:16, 1], summary(poor_model_layer3)$coefficients[17:18, 1]), "SE" = c(summary(poor_model_layer1)$coefficients[1:14, 2], summary(poor_model_layer2)$coefficients[15:16, 2], summary(poor_model_layer3)$coefficients[17:18, 2]))
 
@@
 
-subdat <- data.frame("Outcome" = rep("The water source switch was racially motivated.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(race_model_layer1)$coefficients[1:14, 1], summary(race_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(race_model_layer1)$coefficients[1:14, 2], summary(race_model_layer2)$coefficients[15:16, 2]))
+race_model_layer3 <- polr(factor(racially_motivated_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall + ptsdscore + phq, data = adult_child, Hess = TRUE)
+
+summary(race_model_layer3)
+
+subdat <- data.frame("Outcome" = rep("The water source switch was racially motivated.", 18), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom", "PTSD score", "PHQ score"), "Effect" = c(summary(race_model_layer1)$coefficients[1:14, 1], summary(race_model_layer2)$coefficients[15:16, 1], summary(race_model_layer3)$coefficients[17:18, 1]), "SE" = c(summary(race_model_layer1)$coefficients[1:14, 2], summary(race_model_layer2)$coefficients[15:16, 2], summary(race_model_layer3)$coefficients[17:18, 2]))
 
@@
 
-subdat <- data.frame("Outcome" = rep("I am likely to trust the government on water/environmental issues in future.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(trust_model_layer1)$coefficients[1:14, 1], summary(trust_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(trust_model_layer1)$coefficients[1:14, 2], summary(trust_model_layer2)$coefficients[15:16, 2]))
+trust_model_layer3 <- polr(factor(trust_government_in_future_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall + ptsdscore + phq, data = adult_child, Hess = TRUE)
+
+summary(trust_model_layer3)
+
+subdat <- data.frame("Outcome" = rep("I am likely to trust the government on water/environmental issues in future.", 18), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom", "PTSD score", "PHQ score"), "Effect" = c(summary(trust_model_layer1)$coefficients[1:14, 1], summary(trust_model_layer2)$coefficients[15:16, 1], summary(trust_model_layer3)$coefficients[17:18, 1]), "SE" = c(summary(trust_model_layer1)$coefficients[1:14, 2], summary(trust_model_layer2)$coefficients[15:16, 2], summary(trust_model_layer3)$coefficients[17:18, 2]))
 
@@
 
-subdat <- data.frame("Outcome" = rep("Three years from now, I am likely to drink primarily tap water at home.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(drink_model_layer1)$coefficients[1:14, 1], summary(drink_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(drink_model_layer1)$coefficients[1:14, 2], summary(drink_model_layer2)$coefficients[15:16, 2]))
+drink_model_layer3 <- polr(factor(drink_tap_in_three_years_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall + ptsdscore + phq, data = adult_child, Hess = TRUE)
+
+summary(drink_model_layer3)
+
+subdat <- data.frame("Outcome" = rep("Three years from now, I am likely to drink primarily tap water at home.", 18), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom", "PTSD score", "PHQ score"), "Effect" = c(summary(drink_model_layer1)$coefficients[1:14, 1], summary(drink_model_layer2)$coefficients[15:16, 1], summary(drink_model_layer3)$coefficients[17:18, 1]), "SE" = c(summary(drink_model_layer1)$coefficients[1:14, 2], summary(drink_model_layer2)$coefficients[15:16, 2], summary(drink_model_layer3)$coefficients[17:18, 2]))
 
@@
 
-subdat <- data.frame("Outcome" = rep("I am satisfied with the federal government's role in addressing the Flint water issues.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(fedsatis_model_layer1)$coefficients[1:14, 1], summary(fedsatis_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(fedsatis_model_layer1)$coefficients[1:14, 2], summary(fedsatis_model_layer2)$coefficients[15:16, 2]))
+fedsatis_model_layer3 <- polr(factor(satisfied_federal_government_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall + ptsdscore + phq, data = adult_child, Hess = TRUE)
+
+summary(fedsatis_model_layer3)
+
+subdat <- data.frame("Outcome" = rep("I am satisfied with the federal government's role in addressing the Flint water issues.", 18), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom", "PTSD score", "PHQ score"), "Effect" = c(summary(fedsatis_model_layer1)$coefficients[1:14, 1], summary(fedsatis_model_layer2)$coefficients[15:16, 1], summary(fedsatis_model_layer3)$coefficients[17:18, 1]), "SE" = c(summary(fedsatis_model_layer1)$coefficients[1:14, 2], summary(fedsatis_model_layer2)$coefficients[15:16, 2], summary(fedsatis_model_layer3)$coefficients[17:18, 2]))
 
@@
 
-subdat <- data.frame("Outcome" = rep("I am satisfied with the Michigan government's role in addressing the Flint water issues.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(statesatis_model_layer1)$coefficients[1:14, 1], summary(statesatis_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(statesatis_model_layer1)$coefficients[1:14, 2], summary(statesatis_model_layer2)$coefficients[15:16, 2]))
+statesatis_model_layer3 <- polr(factor(satisfied_state_government_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall + ptsdscore + phq, data = adult_child, Hess = TRUE)
+
+summary(statesatis_model_layer3)
+
+subdat <- data.frame("Outcome" = rep("I am satisfied with the Michigan government's role in addressing the Flint water issues.", 18), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom", "PTSD score", "PHQ score"), "Effect" = c(summary(statesatis_model_layer1)$coefficients[1:14, 1], summary(statesatis_model_layer2)$coefficients[15:16, 1], summary(statesatis_model_layer3)$coefficients[17:18, 1]), "SE" = c(summary(statesatis_model_layer1)$coefficients[1:14, 2], summary(statesatis_model_layer2)$coefficients[15:16, 2], summary(statesatis_model_layer3)$coefficients[17:18, 2]))
 
@@
 
-subdat <- data.frame("Outcome" = rep("I am satisfied with the Flint government's role in addressing the Flint water issues.", 16), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom"), "Effect" = c(summary(flintsatis_model_layer1)$coefficients[1:14, 1], summary(flintsatis_model_layer2)$coefficients[15:16, 1]), "SE" = c(summary(flintsatis_model_layer1)$coefficients[1:14, 2], summary(flintsatis_model_layer2)$coefficients[15:16, 2]))
+flintsatis_model_layer3 <- polr(factor(satisfied_flint_government_tri, levels=c("Disagree", "Neutral", "Agree"), ordered = TRUE) ~ age + gendercollapse + collapserace + pubbencollapse + partycollapse + years_cityflint + confidants2 + zipcollapse + overall_symps + any_child_overall + ptsdscore + phq, data = adult_child, Hess = TRUE)
+
+summary(flintsatis_model_layer3)
+
+subdat <- data.frame("Outcome" = rep("I am satisfied with the Flint government's role in addressing the Flint water issues.", 18), "Predictor" = c("Age", "Male", "Other Race", "White Race", "Receives public benefits", "Republican", "Other political party", "Years in Flint", "Number of confidants", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Number of adult symptoms", "Had child report at least one symptom", "PTSD score", "PHQ score"), "Effect" = c(summary(flintsatis_model_layer1)$coefficients[1:14, 1], summary(flintsatis_model_layer2)$coefficients[15:16, 1], summary(flintsatis_model_layer3)$coefficients[17:18, 1]), "SE" = c(summary(flintsatis_model_layer1)$coefficients[1:14, 2], summary(flintsatis_model_layer2)$coefficients[15:16, 2], summary(flintsatis_model_layer3)$coefficients[17:18, 2]))
 
@@
 prettyeffects <- select(effects, Predictor, Outcome, label, BHpvalue)
-
+prettyeffects$BHpvalue <- round(prettyeffects$BHpvalue, digits = 2)
 sigeffects <- prettyeffects[prettyeffects$BHpvalue < 0.05,]

### 2021-02-02 paperone_adult_health.Rmd
Changes to meet reviewer comments for JUH.

@@
 library(logistf)
+library(mice)
 
@@
 
+mydata$phq <- rowSums(select(mydata, nervousscore, depressedscore, nopleasurescore, worryscore), na.rm=TRUE)
+mydata$phq[is.na(mydata$nervousscore)] <- NA_real_
+
 mydata$ptsd_bin <- as.numeric(mydata$ptsdscore >= 3)
@@
 mydata$include <- factor(mydata$include, levels=c(0, 1), labels=c("Excluded", "Included"))
+
+mydata$employ_collapse <- case_when(
+  mydata$employ_status=="Jobs/sporadic" | mydata$employ_status=="Other" ~ "Other",
+  mydata$employ_status=="Retired" ~ "Retired",
+  mydata$employ_status=="Employed" ~ "Employed",
+  mydata$employ_status=="Unemployed" ~ "Unemployed",
+  is.na(mydata$employ_status) ~ NA_character_)
 
@@
 var_label(mydata$phq_bin) <- "Depression/Anxiety"
+var_label(mydata$employ_collapse) <- "Employment status"
 
-mydata_complete <- filter(mydata, !is.na(age), !is.na(reth), !is.na(marital_status), !is.na(educ_level), !is.na(public_benefits), !is.na(gender), !is.na(confidants2), !is.na(years_cityflint), !is.na(current_zip), !is.na(blood_test_after_april_2014), !is.na(blood_test_before_april_2014), !is.na(elevated_lead_before_april_2014), !is.na(elevated_lead_after_april_2014), !is.na(rashes_before_april_2014), !is.na(rashes_after_april_2014), !is.na(hairloss_before_april_2014), !is.na(hairloss_after_april_2014), !is.na(nausea_before_april_2014), !is.na(nausea_after_april_2014), !is.na(irritable_before_april_2014), !is.na(irritable_after_april_2014), !is.na(ptsdscore), !is.na(phq), gender != "Transgender Woman", !is.na(num_time_notice))
+mydata_complete <- filter(mydata, !is.na(age), !is.na(reth), !is.na(marital_status), !is.na(educ_level), !is.na(public_benefits), !is.na(gender), !is.na(confidants2), !is.na(years_cityflint), !is.na(current_zip), !is.na(blood_test_after_april_2014), !is.na(blood_test_before_april_2014), !is.na(elevated_lead_before_april_2014), !is.na(elevated_lead_after_april_2014), !is.na(rashes_before_april_2014), !is.na(rashes_after_april_2014), !is.na(hairloss_before_april_2014), !is.na(hairloss_after_april_2014), !is.na(nausea_before_april_2014), !is.na(nausea_after_april_2014), !is.na(irritable_before_april_2014), !is.na(irritable_after_april_2014), !is.na(ptsdscore), !is.na(phq), gender != "Transgender Woman", !is.na(num_time_notice), !is.na(employ_collapse))
 ```
 
-We assemble some descriptives and maps on the complete data:
+We assemble some descriptives on the data:
 ```{r, echo=TRUE, message=FALSE, warning=FALSE}
+table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "employ_collapse", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata, includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+
+table_outcomes <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "collapserace", data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)
+
+kable(print(table_predictors, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:18, 20:22, 24:26)) %>% kable_styling(position="center")
+
+kable(print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:7, 9:12, 14:17, 19:22, 24:27, 29:32, 36:38)) %>% kable_styling(position="center")
+
+table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "employ_collapse", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)
+
+table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)
+
+kable(print(table_predictors_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:18, 20:22, 24:26)) %>% kable_styling(position="center")
+
+kable(print(table_outcomes_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:7, 9:12, 14:17, 19:22, 24:27, 29:32, 36:38)) %>% kable_styling(position="center")
+```
+
+We make maps and descriptive statistics:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 zcta1 <- zctas(cb = TRUE, starts_with = c("4850", "48532"), class = "sf") %>% filter(ZCTA5CE10 != "48509")
@@
 flintdat2 <- full_join(flintdat, totalpop, by=c("zip" = "current_zip")) 
+sites <- read_csv("survey_locations.csv")
 
-popmap <- ggplot(data=flintdat2) + geom_sf(data=flintdat2, aes(geometry = geometry, fill = factor(pop)), size=0, alpha = 0.6) + geom_sf(data=flint_boundary, aes(geometry=geometry), fill=NA, color = "black") + geom_sf_label(aes(geometry = geometry, label = paste0(zip, " (", pop, ")"))) + xlab(" ") + ylab(" ") + theme(rect = element_blank(), axis.ticks = element_blank(), axis.line=element_blank(),axis.text.x=element_blank(), axis.text.y=element_blank(), legend.position = "none") + scale_fill_grey()
+popmap <- ggplot(data=flintdat2) + geom_sf(data=flintdat2, aes(geometry = geometry, fill = factor(pop)), size=0, alpha = 0.6) + geom_sf(data=flint_boundary, aes(geometry=geometry), fill=NA, color = "black") + geom_sf_label(aes(geometry = geometry, label = paste0(zip, " (", pop, ")"))) + xlab(" ") + ylab(" ") + theme(rect = element_blank(), axis.ticks = element_blank(), axis.line=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank(), legend.position = "none") + scale_fill_grey() + geom_point(data = sites, aes(x = Longitude, y = Latitude), color = "red", shape = 8)
 
@@
 
-ggsave(filename = "mymap.pdf", plot = popmap, width = 8, height = 8)
+ggsave(filename = "~/Desktop/Research/Jerel Flint/Publications/Paper 1 - Adult Health/mymap.pdf", plot = popmap, width = 8, height = 8)
 
-var_label(mydata_complete$collapseeduc) <- "Education level"
-var_label(mydata_complete$public_benefits) <- "Receives public benefits"
-var_label(mydata_complete$collapsemarital) <- "Marital status"
-var_label(mydata_complete$num_time_notice) <- "How long after water switch to notice water issue? (months)"
-var_label(mydata_complete$blood_test_after_april_2014) <- "Received blood lead test"
-var_label(mydata_complete$elevated_lead_after_april_2014) <- "Had elevated lead"
-var_label(mydata_complete$rashes_after_april_2014) <- "Had rashes"
-var_label(mydata_complete$hairloss_after_april_2014) <- "Had hair loss"
-var_label(mydata_complete$nausea_after_april_2014) <- "Had nausea"
-var_label(mydata_complete$irritable_after_april_2014) <- "Was irritable"
-var_label(mydata_complete$ptsd_bin) <- "PTSD"
-var_label(mydata_complete$phq_bin) <- "Depression/Anxiety"
+#table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata, includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
 
-table_missing <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2", "num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "include", data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+#table_outcomes <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "collapserace", data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)
 
-table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata, includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
+#kable(print(table_predictors, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:16, 18:20)) %>% kable_styling(position="center")
 
-table_outcomes <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "collapserace", data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)
+#kable(print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:7, 9:12, 14:17, 19:22, 24:27, 29:32, 36:38)) %>% kable_styling(position="center")
 
-kable(print(table_predictors, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(5:9, 11:13, 15:17)) %>% kable_styling(position="center")
+#table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)
 
-kable(print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:10, 12:14, 16:18, 20:22, 24:26)) %>% kable_styling(position="center")
+#table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)
 
-table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)
+#kable(print(table_predictors_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:16, 18:20)) %>% kable_styling(position="center")
 
-table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)
-
-kable(print(table_missing, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:16, 18:20, 26:28, 30:32, 34:36, 38:40, 42:44)) %>% kable_styling(position="center")
-
-test <- print(table_missing, contDigits=1, varLabel = T, printToggle=FALSE)
-
-kable(print(table_predictors_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(5:9, 11:13, 15:17)) %>% kable_styling(position="center")
-
-kable(print(table_outcomes_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:10, 12:14, 16:18, 20:22, 24:26)) %>% kable_styling(position="center")
-```
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-knitr::include_graphics("~/Desktop/Research/Jerel Flint/Analyses/sample_inclusion.png")
+#kable(print(table_outcomes_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:7, 9:12, 14:17, 19:22, 24:27, 29:32, 36:38)) %>% kable_styling(position="center")
 ```
@@
 
+Per reviewer request, we use multiple imputation with chained equations to impute missingness in the dataset:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+mydata$collapsezip <- ifelse(mydata$current_zip==48502, 2, mydata$current_zip)
+mydata$collapsezip <- factor(mydata$collapsezip, levels=c(2:7), labels=c("48502/48503", "48504", "48505", "48506", "48507", "48532"))
+mydata$collapsepubben <- ifelse(mydata$public_benefits=="Yes", "Yes", "No")
+mydata$collapsegender <- ifelse(mydata$gender=="Transgender Woman", "Female", mydata$gender)
+mydata$rash_collapse_before <- ifelse(mydata$rashes_before_april_2014=="Yes", 1, 0)
+mydata$hair_collapse_before <- ifelse(mydata$hairloss_before_april_2014=="Yes", 1, 0)
+mydata$nausea_collapse_before <- ifelse(mydata$nausea_before_april_2014=="Yes", 1, 0)
+mydata$irritable_collapse_before <- ifelse(mydata$irritable_before_april_2014=="Yes", 1, 0)
+mydata$bloodtest_collapse_before <- ifelse(mydata$blood_test_before_april_2014=="Yes", 1, 0)
+
+mydata_complete <- select(mydata, age, collapsegender, collapserace, collapsepubben, collapseeduc, employ_collapse, number_children, years_cityflint, confidants2, collapsezip, ptsd_bin, phq_bin, rash_collapse, hair_collapse, nausea_collapse, irritable_collapse, overall_collapse, elevated_collapse, bloodtest_collapse, num_time_notice, rash_collapse_before, hair_collapse_before, nausea_collapse_before, irritable_collapse_before, bloodtest_collapse_before)
+
+mydata_complete$collapsegender <- factor(mydata_complete$collapsegender)
+mydata_complete$collapserace <- factor(mydata_complete$collapserace)
+mydata_complete$collapsepubben <- factor(mydata_complete$collapsepubben)
+mydata_complete$collapseeduc <- factor(mydata_complete$collapseeduc)
+mydata_complete$employ_collapse <- factor(mydata_complete$employ_collapse)
+mydata_complete$collapsezip <- factor(mydata_complete$collapsezip)
+mydata_complete$ptsd_bin <- factor(mydata_complete$ptsd_bin)
+mydata_complete$phq_bin <- factor(mydata_complete$phq_bin)
+mydata_complete$rash_collapse <- factor(mydata_complete$rash_collapse)
+mydata_complete$hair_collapse <- factor(mydata_complete$hair_collapse)
+mydata_complete$nausea_collapse <- factor(mydata_complete$nausea_collapse)
+mydata_complete$irritable_collapse <- factor(mydata_complete$irritable_collapse)
+mydata_complete$elevated_collapse <- factor(mydata_complete$elevated_collapse)
+mydata_complete$bloodtest_collapse <- factor(mydata_complete$bloodtest_collapse)
+mydata_complete$rash_collapse_before <- factor(mydata_complete$rash_collapse_before)
+mydata_complete$hair_collapse_before <- factor(mydata_complete$hair_collapse_before)
+mydata_complete$nausea_collapse_before <- factor(mydata_complete$nausea_collapse_before)
+mydata_complete$irritable_collapse_before <- factor(mydata_complete$irritable_collapse_before)
+mydata_complete$bloodtest_collapse_before <- factor(mydata_complete$bloodtest_collapse_before)
+
+imp <- mice(mydata_complete, maxit = 0)
+
+predM <- imp$predictorMatrix
+meth <- imp$method
+
+set.seed(123)
+imp2 <- mice(mydata_complete, m = 25, print = FALSE)
+
+imp_long <- mice::complete(imp2, action="long", include = TRUE)
+imp_long$zip2 <- case_when(
+  imp_long$collapsezip=="48502/48503" ~ "48502/48503",
+  imp_long$collapsezip=="48504" ~ "48504",
+  imp_long$collapsezip=="48505" ~ "48505",
+  imp_long$collapsezip=="48506" ~ "48506",
+  imp_long$collapsezip=="48507" | imp_long$collapsezip=="48532" ~ "48507/48532"
+)
+
+imp_long$collapseeduc2 <- case_when(
+  imp_long$collapseeduc=="Less than high school" | imp_long$collapseeduc=="High school" ~ "High school or less",
+  imp_long$collapseeduc=="Some college" ~ "Some college",
+  imp_long$collapseeduc=="Associate's" | imp_long$collapseeduc=="College degree or more" ~ "Associate's or more"
+)
+
+imp_long$zip2 <- with(imp_long, as.factor(imp_long$zip2))
+imp_long$collapseeduc2 <- with(imp_long, as.factor(imp_long$collapseeduc2))
+imp_long_mids<-as.mids(imp_long)
+```
+
 As we know, when trying to understand the effect of a mediated effect on some outcome, we DO NOT adjust for the mediator.
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-mydata_complete$collapsezip <- ifelse(mydata_complete$current_zip==48502, 2, mydata_complete$current_zip)
-mydata_complete$collapsezip <- factor(mydata_complete$collapsezip, levels=c(2:7), labels=c("48502/48503", "48504", "48505", "48506", "48507", "48532"))
-mydata_complete$collapsepubben <- ifelse(mydata_complete$public_benefits=="Yes", "Yes", "No")
+effect_estims <- data.frame("Outcome" = NA, "Predictor" = NA, "Estimate" = NA, "SE" = NA, "Pval" = NA)
 
-ptsd_dem <- glm(ptsd_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+ptsd_dem <- with(imp_long_mids, glm(ptsd_bin ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))
 
-summary(ptsd_dem)
+summary(pool(ptsd_dem))
 
-phq_dem <- glm(phq_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+subdat <- data.frame("Outcome" = rep("PTSD", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(ptsd_dem))[-1,2], "SE" = summary(pool(ptsd_dem))[-1,3], "Pval" = summary(pool(ptsd_dem))[-1,6])
 
-summary(phq_dem)
+effect_estims <- rbind(effect_estims, subdat)
 
-rash_dem <- glm(rash_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+phq_dem <- with(imp_long_mids, glm(phq_bin ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))
 
-summary(rash_dem)
+summary(pool(phq_dem))
 
-hairloss_dem <- glm(hair_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+subdat <- data.frame("Outcome" = rep("PHQ", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed",  "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(phq_dem))[-1,2], "SE" = summary(pool(phq_dem))[-1,3], "Pval" = summary(pool(phq_dem))[-1,6])
 
-summary(hairloss_dem)
+effect_estims <- rbind(effect_estims, subdat)
 
-nausea_dem <- glm(nausea_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+rash_dem <- with(imp_long_mids, glm(rash_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))
 
-summary(nausea_dem)
+summary(pool(rash_dem))
 
-irritable_dem <- glm(irritable_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+subdat <- data.frame("Outcome" = rep("Rashes", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(rash_dem))[-1,2], "SE" = summary(pool(rash_dem))[-1,3], "Pval" = summary(pool(rash_dem))[-1,6])
 
-summary(irritable_dem)
+effect_estims <- rbind(effect_estims, subdat)
 
-overall_dem <- glm(overall_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="poisson")
+hairloss_dem <- with(imp_long_mids, glm(hair_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))
 
-summary(overall_dem)
+summary(pool(hairloss_dem))
 
-bloodlead_dem <- logistf(elevated_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data = mydata_complete)
+subdat <- data.frame("Outcome" = rep("Hair loss", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(hairloss_dem))[-1,2], "SE" = summary(pool(hairloss_dem))[-1,3], "Pval" = summary(pool(hairloss_dem))[-1,6])
 
-test1 <- summary(bloodlead_dem)
+effect_estims <- rbind(effect_estims, subdat)
 
-gettest_dem <- glm(bloodtest_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete, family="binomial")
+nausea_dem <- with(imp_long_mids, glm(nausea_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))
 
-summary(gettest_dem)
+summary(pool(nausea_dem))
 
-time_dem <- lm(log(num_time_notice) ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip, data=mydata_complete)
+subdat <- data.frame("Outcome" = rep("Nausea", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(nausea_dem))[-1,2], "SE" = summary(pool(nausea_dem))[-1,3], "Pval" = summary(pool(nausea_dem))[-1,6])
 
-summary(time_dem)
+effect_estims <- rbind(effect_estims, subdat)
 
-mydata_complete$rash_collapse_before <- ifelse(mydata_complete$rashes_before_april_2014=="Yes", "Yes", "No")
-mydata_complete$hair_collapse_before <- ifelse(mydata_complete$hairloss_before_april_2014=="Yes", "Yes", "No")
-mydata_complete$nausea_collapse_before <- ifelse(mydata_complete$nausea_before_april_2014=="Yes", "Yes", "No")
-mydata_complete$irritable_collapse_before <- ifelse(mydata_complete$irritable_before_april_2014=="Yes", "Yes", "No")
-mydata_complete$bloodtest_collapse_before <- ifelse(mydata_complete$blood_test_before_april_2014=="Yes", "Yes", "No")
+irritable_dem <- with(imp_long_mids, glm(irritable_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))
 
-ptsd_symp <- glm(ptsd_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + overall_collapse + elevated_collapse + bloodtest_collapse + num_time_notice, data=mydata_complete, family="binomial")
+summary(pool(irritable_dem))
 
-summary(ptsd_symp)
+subdat <- data.frame("Outcome" = rep("Agitation", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(irritable_dem))[-1,2], "SE" = summary(pool(irritable_dem))[-1,3], "Pval" = summary(pool(irritable_dem))[-1,6])
 
-phq_symp <- glm(phq_bin ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + overall_collapse + elevated_collapse + bloodtest_collapse + num_time_notice, data=mydata_complete, family="binomial")
+effect_estims <- rbind(effect_estims, subdat)
 
-summary(phq_symp)
+overall_dem <- with(imp_long_mids, glm(overall_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="poisson"))
 
-rash_symp <- logistf(rash_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + hair_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + rash_collapse_before, data=mydata_complete)
+summary(pool(overall_dem))
 
-test2 <- summary(rash_symp)
+subdat <- data.frame("Outcome" = rep("Overall", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(overall_dem))[-1,2], "SE" = summary(pool(overall_dem))[-1,3], "Pval" = summary(pool(overall_dem))[-1,6])
 
-hairloss_symp <- logistf(hair_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + rash_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + hair_collapse_before, data=mydata_complete)
+effect_estims <- rbind(effect_estims, subdat)
 
-test3 <- summary(hairloss_symp)
+#bloodlead_dem <- with(imp_long_mids, logistf(elevated_collapse ~ age + collapsegender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2))
 
-nausea_symp <- logistf(nausea_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + rash_collapse + hair_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + nausea_collapse_before, data=mydata_complete)
+#bloodlead_dem <- lapply(1:5, function(X) logistf(data = select(list_imps[[X]], elevated_collapse, age, collapsegender, collapserace, collapsepubben, number_children, years_cityflint, confidants2, zip2), elevated_collapse ~ age + collapsegender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2, pl = TRUE, dataout = TRUE))
 
-test4 <- summary(nausea_symp)
+bloodlead_dem <- with(imp_long_mids, glm(elevated_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family = "binomial"))
 
-irritable_symp <- logistf(irritable_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + rash_collapse + hair_collapse + nausea_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + irritable_collapse_before, data=mydata_complete)
+#test1 <- summary(bloodlead_dem)
 
-test5 <- summary(irritable_symp)
+#test <- CLIP.confint(obj = bloodlead_dem)
+summary(pool(bloodlead_dem))
 
-overall_bloodlead <- glm(overall_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + collapsezip + elevated_collapse + bloodtest_collapse + num_time_notice + rash_collapse_before + hair_collapse_before + nausea_collapse_before + irritable_collapse_before, data=mydata_complete, family="poisson")
+subdat <- data.frame("Outcome" = rep("Elevated BLLs", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(bloodlead_dem))[-1,2], "SE" = summary(pool(bloodlead_dem))[-1,3], "Pval" = summary(pool(bloodlead_dem))[-1,6])
 
-summary(overall_bloodlead)
+effect_estims <- rbind(effect_estims, subdat)
+
+gettest_dem <- with(imp_long_mids, glm(bloodtest_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family="binomial"))
+
+summary(pool(gettest_dem))
+
+subdat <- data.frame("Outcome" = rep("Get tested", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(gettest_dem))[-1,2], "SE" = summary(pool(gettest_dem))[-1,3], "Pval" = summary(pool(gettest_dem))[-1,6])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+time_dem <- with(imp_long_mids, lm(log(num_time_notice) ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2))
+
+summary(pool(time_dem))
+
+subdat <- data.frame("Outcome" = rep("Time to notice", 17), "Predictor" = c("Age", "Male", "Other race", "White", "Receives benefits", "High school or less", "Some college", "Other employment", "Retired", "Unemployed", "Number of children", "Years in Flint", "Network size", "Zip 48504", "Zip 48505", "Zip 48506", "Zip 48507/48532"), "Estimate" = summary(pool(time_dem))[-1,2], "SE" = summary(pool(time_dem))[-1,3], "Pval" = summary(pool(time_dem))[-1,6])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+ptsd_symp <- with(imp_long_mids, glm(ptsd_bin ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2 + overall_collapse + elevated_collapse + bloodtest_collapse + num_time_notice, family="binomial"))
+
+summary(pool(ptsd_symp))
+
+subdat <- data.frame("Outcome" = rep("PTSD", 4), "Predictor" = c("Number of symptoms", "Elevated BLLs", "Get tested", "Time to notice"), "Estimate" = summary(pool(ptsd_symp))[19:22,2], "SE" = summary(pool(ptsd_symp))[19:22,3], "Pval" = summary(pool(ptsd_symp))[19:22,6])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+phq_symp <- with(imp_long_mids, glm(phq_bin ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2 + overall_collapse + elevated_collapse + bloodtest_collapse + num_time_notice, family="binomial"))
+
+summary(pool(phq_symp))
+
+subdat <- data.frame("Outcome" = rep("PHQ", 4), "Predictor" = c("Number of symptoms", "Elevated BLLs", "Get tested", "Time to notice"), "Estimate" = summary(pool(phq_symp))[19:22,2], "SE" = summary(pool(phq_symp))[19:22,3], "Pval" = summary(pool(phq_symp))[19:22,6])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+#rash_symp <- logistf(rash_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2 + hair_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + rash_collapse_before, data=mydata_complete)
+
+#test2 <- summary(rash_symp)
+
+rash_symp <- with(imp_long_mids, glm(rash_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2 + hair_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + rash_collapse_before, family = "binomial"))
+
+summary(pool(rash_symp))
+
+subdat <- data.frame("Outcome" = rep("Rashes", 7), "Predictor" = c("Hair loss", "Nausea", "Agitation", "Elevated BLLs", "Get tested", "Time to notice", "Rashes before"), "Estimate" = summary(pool(rash_symp))[19:25,2], "SE" = summary(pool(rash_symp))[19:25,3], "Pval" = summary(pool(rash_symp))[19:25,6])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+#hairloss_symp <- logistf(hair_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2 + rash_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + hair_collapse_before, data=mydata_complete)
+
+#test3 <- summary(hairloss_symp)
+
+hairloss_symp <- with(imp_long_mids, glm(hair_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2 + rash_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + hair_collapse_before, family = "binomial"))
+
+summary(pool(hairloss_symp))
+
+subdat <- data.frame("Outcome" = rep("Hair loss", 7), "Predictor" = c("Rashes", "Nausea", "Agitation", "Elevated BLLs", "Get tested", "Time to notice", "Hair loss before"), "Estimate" = summary(pool(hairloss_symp))[19:25,2], "SE" = summary(pool(hairloss_symp))[19:25,3], "Pval" = summary(pool(hairloss_symp))[19:25,6])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+#nausea_symp <- logistf(nausea_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2 + rash_collapse + hair_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + nausea_collapse_before, data=mydata_complete)
+
+#test4 <- summary(nausea_symp)
+
+nausea_symp <- with(imp_long_mids, glm(nausea_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2 + rash_collapse + hair_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + nausea_collapse_before, family = "binomial"))
+
+summary(pool(nausea_symp))
+
+subdat <- data.frame("Outcome" = rep("Nausea", 7), "Predictor" = c("Rashes", "Hair loss", "Agitation", "Elevated BLLs", "Get tested", "Time to notice", "Nausea before"), "Estimate" = summary(pool(nausea_symp))[19:25,2], "SE" = summary(pool(nausea_symp))[19:25,3], "Pval" = summary(pool(nausea_symp))[19:25,6])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+#irritable_symp <- logistf(irritable_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2 + rash_collapse + hair_collapse + nausea_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + irritable_collapse_before, data=mydata_complete)
+
+#test5 <- summary(irritable_symp)
+
+irritable_symp <- with(imp_long_mids, glm(irritable_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2 + rash_collapse + hair_collapse + nausea_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + irritable_collapse_before, family = "binomial"))
+
+summary(pool(irritable_symp))
+
+subdat <- data.frame("Outcome" = rep("Agitation", 7), "Predictor" = c("Rashes", "Hair loss", "Nausea", "Elevated BLLs", "Get tested", "Time to notice", "Agitation before"), "Estimate" = summary(pool(irritable_symp))[19:25,2], "SE" = summary(pool(irritable_symp))[19:25,3], "Pval" = summary(pool(irritable_symp))[19:25,6])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+overall_bloodlead <- with(imp_long_mids, glm(overall_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2 + elevated_collapse + bloodtest_collapse + num_time_notice + rash_collapse_before + hair_collapse_before + nausea_collapse_before + irritable_collapse_before, family = "poisson"))
+
+summary(pool(overall_bloodlead))
+
+subdat <- data.frame("Outcome" = rep("Overall symptoms", 7), "Predictor" = c("Elevated BLLs", "Get tested", "Time to notice", "Rashes before", "Hair loss before", "Nausea before", "Agitation before"), "Estimate" = summary(pool(overall_bloodlead))[19:25,2], "SE" = summary(pool(overall_bloodlead))[19:25,3], "Pval" = summary(pool(overall_bloodlead))[19:25,6])
+
+effect_estims <- rbind(effect_estims, subdat)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-#Assembling a data frame of desired coefficients, confidence intervals, and p-values:
-myresults <- data.frame("Outcome" = c(rep("PTSD", length(summary(ptsd_dem)$coefficients[-1,1])), rep("PHQ", length(summary(phq_dem)$coefficients[-1,1])), rep("Rashes", length(summary(rash_dem)$coefficients[-1,1])), rep("Hairloss", length(summary(hairloss_dem)$coefficients[-1,1])), rep("Nausea", length(summary(nausea_dem)$coefficients[-1,1])), rep("Irritable", length(summary(irritable_dem)$coefficients[-1,1])), rep("Overall", length(summary(overall_dem)$coefficients[-1,1])), rep("Elevated lead", length(test1$coefficients[-1])), rep("Get tested", length(summary(gettest_dem)$coefficients[-1,1])), rep("Time to notice", length(summary(time_dem)$coefficients[-1,1])), rep("PTSD", length(summary(ptsd_symp)$coefficients[15:18,1])), rep("PHQ", length(summary(phq_symp)$coefficients[15:18,1])), rep("Rashes", length(test2$coefficients[15:20])), rep("Hairloss", length(test3$coefficients[15:20])), rep("Nausea", length(test4$coefficients[15:20])), rep("Irritable", length(test5$coefficients[15:20])), rep("Overall", length(summary(overall_bloodlead)$coefficients[15:17,1]))))
+effect_estims <- effect_estims[-1,]
+effect_estims$Lower <- effect_estims$Estimate - 1.96*effect_estims$SE
+effect_estims$Upper <- effect_estims$Estimate + 1.96*effect_estims$SE
 
-myresults$Predictor <- c(rownames(summary(ptsd_dem)$coefficients[-1,]), rownames(summary(phq_dem)$coefficients[-1,]), rownames(summary(rash_dem)$coefficients[-1,]), rownames(summary(hairloss_dem)$coefficients[-1,]), rownames(summary(nausea_dem)$coefficients[-1,]), rownames(summary(irritable_dem)$coefficients[-1,]), rownames(summary(overall_dem)$coefficients[-1,]), names(test1$coefficients[-1]), rownames(summary(gettest_dem)$coefficients[-1,]), rownames(summary(time_dem)$coefficients[-1,]), rownames(summary(ptsd_symp)$coefficients[15:18,]), rownames(summary(phq_symp)$coefficients[15:18,]), names(test2$coefficients[15:20]), names(test3$coefficients[15:20]), names(test4$coefficients[15:20]), names(test5$coefficients[15:20]), rownames(summary(overall_bloodlead)$coefficients[15:17,]))
+pretty_effects <- data.frame("Outcome" = effect_estims$Outcome, "Predictor" = effect_estims$Predictor, "Estimate" = exp(effect_estims$Estimate), "Lower" = exp(effect_estims$Lower), "Upper" = exp(effect_estims$Upper), "BHpvalue" = round(p.adjust(effect_estims$Pval, method="BH"), digits = 2))
 
-myresults$Coefficient <- c(summary(ptsd_dem)$coefficients[-1,1], summary(phq_dem)$coefficients[-1,1], summary(rash_dem)$coefficients[-1,1], summary(hairloss_dem)$coefficients[-1,1], summary(nausea_dem)$coefficients[-1,1], summary(irritable_dem)$coefficients[-1,1], summary(overall_dem)$coefficients[-1,1], test1$coefficients[-1], summary(gettest_dem)$coefficients[-1,1], summary(time_dem)$coefficients[-1,1], summary(ptsd_symp)$coefficients[15:18,1], summary(phq_symp)$coefficients[15:18,1], test2$coefficients[15:20], test3$coefficients[15:20], test4$coefficients[15:20], test5$coefficients[15:20], summary(overall_bloodlead)$coefficients[15:17,1])
+pretty_effects$Label <- paste0(round(pretty_effects$Estimate, digits = 1), " (", round(pretty_effects$Lower, digits = 1), ", ", round(pretty_effects$Upper, digits = 1), ")")
 
-myresults$Lower <- c(summary(ptsd_dem)$coefficients[-1,1]-1.96*summary(ptsd_dem)$coefficients[-1,2], summary(phq_dem)$coefficients[-1,1]-1.96*summary(phq_dem)$coefficients[-1,2], summary(rash_dem)$coefficients[-1,1]-1.96*summary(rash_dem)$coefficients[-1,2], summary(hairloss_dem)$coefficients[-1,1]-1.96*summary(hairloss_dem)$coefficients[-1,2], summary(nausea_dem)$coefficients[-1,1]-1.96*summary(nausea_dem)$coefficients[-1,2], summary(irritable_dem)$coefficients[-1,1]-1.96*summary(irritable_dem)$coefficients[-1,2], summary(overall_dem)$coefficients[-1,1]-1.96*summary(overall_dem)$coefficients[-1,2], test1$ci.lower[-1], summary(gettest_dem)$coefficients[-1,1]-1.96*summary(gettest_dem)$coefficients[-1,2], summary(time_dem)$coefficients[-1,1]-1.96*summary(time_dem)$coefficients[-1,2], summary(ptsd_symp)$coefficients[15:18,1]-1.96*summary(ptsd_symp)$coefficients[15:18,2], summary(phq_symp)$coefficients[15:18,1]-1.96*summary(phq_symp)$coefficients[15:18,2], test2$ci.lower[15:20], test3$ci.lower[15:20], test4$ci.lower[15:20], test5$ci.lower[15:20], summary(overall_bloodlead)$coefficients[15:17,1]-1.96*summary(overall_bloodlead)$coefficients[15:17,2])
-
-myresults$Upper <- c(summary(ptsd_dem)$coefficients[-1,1]+1.96*summary(ptsd_dem)$coefficients[-1,2], summary(phq_dem)$coefficients[-1,1]+1.96*summary(phq_dem)$coefficients[-1,2], summary(rash_dem)$coefficients[-1,1]+1.96*summary(rash_dem)$coefficients[-1,2], summary(hairloss_dem)$coefficients[-1,1]+1.96*summary(hairloss_dem)$coefficients[-1,2], summary(nausea_dem)$coefficients[-1,1]+1.96*summary(nausea_dem)$coefficients[-1,2], summary(irritable_dem)$coefficients[-1,1]+1.96*summary(irritable_dem)$coefficients[-1,2], summary(overall_dem)$coefficients[-1,1]+1.96*summary(overall_dem)$coefficients[-1,2], test1$ci.upper[-1], summary(gettest_dem)$coefficients[-1,1]+1.96*summary(gettest_dem)$coefficients[-1,2], summary(time_dem)$coefficients[-1,1]+1.96*summary(time_dem)$coefficients[-1,2], summary(ptsd_symp)$coefficients[15:18,1]+1.96*summary(ptsd_symp)$coefficients[15:18,2], summary(phq_symp)$coefficients[15:18,1]+1.96*summary(phq_symp)$coefficients[15:18,2], test2$ci.upper[15:20], test3$ci.upper[15:20], test4$ci.upper[15:20], test5$ci.upper[15:20], summary(overall_bloodlead)$coefficients[15:17,1]+1.96*summary(overall_bloodlead)$coefficients[15:17,2])
-
-myresults$pvalue <- c(summary(ptsd_dem)$coefficients[-1,4], summary(phq_dem)$coefficients[-1,4], summary(rash_dem)$coefficients[-1,4], summary(hairloss_dem)$coefficients[-1,4], summary(nausea_dem)$coefficients[-1,4], summary(irritable_dem)$coefficients[-1,4], summary(overall_dem)$coefficients[-1,4], test1$prob[-1], summary(gettest_dem)$coefficients[-1,4], summary(time_dem)$coefficients[-1,4], summary(ptsd_symp)$coefficients[15:18,4], summary(phq_symp)$coefficients[15:18,4], test2$prob[15:20], test3$prob[15:20], test4$prob[15:20], test5$prob[15:20], summary(overall_bloodlead)$coefficients[15:17,4])
-
-myresults$BHpvalue <- p.adjust(myresults$pvalue, method="BH")
-myresults$sig <- ifelse(myresults$BHpvalue <=0.05, "LOOK", NA_character_)
-
-myresults$Predictor_clean <- case_when(
-  myresults$Predictor=="age" ~ "Age",
-  myresults$Predictor=="genderMale" ~ "Male",
-  myresults$Predictor=="collapseraceOther" ~ "Other race",
-  myresults$Predictor=="collapseraceWhite" ~ "White race",
-  myresults$Predictor=="collapseeducHigh school" ~ "High school graduate",
-  myresults$Predictor=="collapseeducSome college" ~ "Some college",
-  myresults$Predictor=="collapseeducAssociate's" ~ "Associate's degree",
-  myresults$Predictor=="collapseeducCollege degree or more" ~ "College degree or more",
-  myresults$Predictor=="collapsepubbenYes" ~ "Receives public benefits",
-  myresults$Predictor=="collapsemaritalSeparated" ~ "Separated",
-  myresults$Predictor=="collapsemaritalSingle (never married)" ~ "Single",
-  myresults$Predictor=="years_cityflint" ~ "Years in Flint",
-  myresults$Predictor=="confidants2" ~ "Network size",
-  myresults$Predictor=="collapsezip48504" ~ "Zipcode 48504",
-  myresults$Predictor=="collapsezip48505" ~ "Zipcode 48505",
-  myresults$Predictor=="collapsezip48506" ~ "Zipcode 48506",
-  myresults$Predictor=="collapsezip48507" ~ "Zipcode 48507",
-  myresults$Predictor=="collapsezip48532" ~ "Zipcode 48532",
-  myresults$Predictor=="rash_collapse" ~ "Rashes",
-  myresults$Predictor=="hair_collapse" ~ "Hair loss",
-  myresults$Predictor=="nausea_collapse" ~ "Nausea",
-  myresults$Predictor=="irritable_collapse" ~ "Irritability",
-  myresults$Predictor=="elevated_collapse" ~ "Elevated BLL",
-  myresults$Predictor=="bloodtest_collapse" ~ "Screened for lead",
-  myresults$Predictor=="num_time_notice" ~ "Months to notice problem"
-)
-
-myresults$Predictor_clean <- factor(myresults$Predictor_clean, levels= c("Age", "Male", "Other race", "White race", "High school graduate", "Some college", "Associate's degree", "College degree or more", "Receives public benefits", "Separated", "Single", "Years in Flint", "Network size", "Zipcode 48504", "Zipcode 48505", "Zipcode 48506", "Zipcode 48507", "Zipcode 48532", "Months to notice problem", "Screened for lead", "Elevated BLL", "Rashes", "Hair loss", "Nausea", "Irritability"), ordered=TRUE)
-
-table3_results <- filter(myresults, Outcome=="Time to notice" | Outcome=="Get tested" | Outcome=="Elevated lead") %>%
-  mutate(Label = paste(round(exp(Coefficient), digits=1), " (", round(exp(Lower), digits=1), ",", round(exp(Upper), digits=1), ")", sep=""), Pvalue = round(BHpvalue, digits=2)) %>% select(Outcome, Predictor_clean, Label, Pvalue)
-
-table4_results <- filter(myresults, Outcome=="Rashes" | Outcome=="Hairloss" | Outcome=="Nausea" | Outcome=="Irritable") %>%
-  mutate(Label = paste(round(exp(Coefficient), digits=1), " (", round(exp(Lower), digits=1), ",", round(exp(Upper), digits=1), ")", sep=""), Pvalue = round(BHpvalue, digits=2)) %>% select(Outcome, Predictor_clean, Label, Pvalue)
-
-table4_resultsb <- filter(myresults, Outcome=="Overall") %>%
-  mutate(Label = paste(round(Coefficient, digits=1), " (", round(Lower, digits=1), ",", round(Upper, digits=1), ")", sep=""), Pvalue = round(BHpvalue, digits=2)) %>% select(Outcome, Predictor_clean, Label, Pvalue)
-
-table5_results <- filter(myresults, Outcome=="PTSD" | Outcome=="PHQ") %>%
-  mutate(Label = paste(round(exp(Coefficient), digits=1), " (", round(exp(Lower), digits=1), ",", round(exp(Upper), digits=1), ")", sep=""), Pvalue = round(BHpvalue, digits=2)) %>% select(Outcome, Predictor_clean, Label, Pvalue)
-
+pretty_effects2 <- select(pretty_effects, Outcome, Predictor, Label, BHpvalue)
 #ptsd_plot <- ggplot(myresults[myresults$Outcome=="PTSD",], aes(fct_rev(Predictor_clean), Coefficient)) + geom_point() + geom_errorbar(aes(ymin=Lower, ymax=Upper, width=0.1)) + coord_flip(ylim=c(-2.35, 5.5)) + labs(y = "Odds Ratio and 95% CI", x = "", caption=TeX('Protective $\\leftarrow \\rightarrow$ Harmful' )) + geom_hline(yintercept=0, linetype="dashed", color = "black") + theme(panel.background = element_rect(fill="white"), panel.grid.major = element_blank(), panel.grid.minor=element_blank(), legend.position="bottom", text=element_text(size=14), plot.caption = element_text(size=14, hjust = 0.15)) + geom_rect(fill="white", ymin=4.7, ymax=Inf, xmin=-Inf, xmax=Inf) + annotate(geom = 'text', label = myresults$Label[myresults$Outcome=="PTSD"], x = myresults$Predictor_clean[myresults$Outcome=="PTSD"], y = 3.5, hjust = 0, vjust = 0.5) + scale_y_continuous(breaks=log(c(0.1, 0.25, 0.5, 1, 2, 4, 10)), labels=c("0.1","0.25", "0.5", "1.0", "2.0", "4.0", "10.0")) + ggtitle("Outcome: Trauma Symptoms")

### 2021-05-27 papertwo_child_health.Rmd
Updates before resubmission to JURH

--- 2020-11-23 papertwo_child_health.Rmd
@@
 author: "Elizabeth Chase"
-date: "10/16/2020"
+date: "5/10/2021"
 output: pdf_document
@@
 
-```{r setup, include=FALSE, echo=TRUE}
+```{r setup, include=FALSE, echo=FALSE}
 library(knitr)
@@
 library(kableExtra)
-library(tigris)
-library(sf)
-library(spdep)
 library(logistf)
@@
 
-subadult <- mutate(adult_clean_eliz, parbloodtestf = blood_test_after_april_2014, parbllf = elevated_lead_after_april_2014, parrashesf = rashes_after_april_2014, parhairf = hairloss_after_april_2014, parnausf = nausea_after_april_2014, parirrf = irritable_after_april_2014, parbloodtestc = getscreened, parbllc = elevated_collapse, parrashesc = rash_collapse, parhairc = hair_collapse, parnausc = nausea_collapse, parirrc = irritable_collapse, paroverall = overall_collapse) %>% select(inclusion, unique_id, age, gender, collapserace, collapseeduc, have_health_insurance, public_benefits, water_exaggerated, children_health_harmed, trust_government_in_future, drink_tap_in_three_years, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, political_affiliation, nightmares, avoided_thinking_crisis, onguard_watchful, numb_detached, felt_guilty, ptsdscore, phq, parbloodtestf, parbllf, parrashesf, parhairf, parnausf, parirrf, parbloodtestc, parbllc, parrashesc, parhairc, parnausc, parirrc, paroverall, confidants2, number_children, employ_status)
+adult_clean_eliz$num_time_notice <- case_when(
+  adult_clean_eliz$noticed_water_issue=="1 year *AFTER* it was switched" ~ 12,
+  adult_clean_eliz$noticed_water_issue=="2 months *AFTER* it was switched" ~ 2,
+  adult_clean_eliz$noticed_water_issue=="Unsure/Don't know" ~ NA_real_,
+  adult_clean_eliz$noticed_water_issue=="2 years *AFTER* it was switched" ~ 24,
+  adult_clean_eliz$noticed_water_issue=="Less than 1 month *AFTER* the water source was switched" ~ 0.5,
+  adult_clean_eliz$noticed_water_issue=="1 month *AFTER* it was switched" ~ 1,
+  adult_clean_eliz$noticed_water_issue=="3 months *AFTER* it was switched" ~ 3,
+  adult_clean_eliz$noticed_water_issue=="1 year and 2 months *AFTER* it was switched" ~ 14,
+  adult_clean_eliz$noticed_water_issue=="6 months *AFTER* it was switched" ~ 6,
+  adult_clean_eliz$noticed_water_issue=="9 months *AFTER* it was switched" ~ 9,
+  adult_clean_eliz$noticed_water_issue=="1 year and 6 months *AFTER* it was switched" ~ 18,
+  adult_clean_eliz$noticed_water_issue=="7 months *AFTER* it was switched" ~ 7,
+  adult_clean_eliz$noticed_water_issue=="4 years or more *AFTER* it was switched" ~ 4,
+  adult_clean_eliz$noticed_water_issue=="10 months *AFTER* it was switched" ~ 10,
+  adult_clean_eliz$noticed_water_issue=="5 months *AFTER* it was switched" ~ 5,
+  adult_clean_eliz$noticed_water_issue=="11 months *AFTER* it was switched" ~ 11,
+  adult_clean_eliz$noticed_water_issue=="4 months *AFTER* it was switched" ~ 4,
+  adult_clean_eliz$noticed_water_issue=="1 year and 5 months *AFTER* it was switched" ~ 17,
+  adult_clean_eliz$noticed_water_issue=="8 months *AFTER* it was switched" ~ 8,
+  adult_clean_eliz$noticed_water_issue=="3 years *AFTER* it was switched" ~ 36,
+  adult_clean_eliz$noticed_water_issue=="2 year and 1 month *AFTER* it was switched" ~ 25,
+  adult_clean_eliz$noticed_water_issue=="2 year and 6 months *AFTER* it was switched" ~ 30,
+  adult_clean_eliz$noticed_water_issue=="1 year and 3 months *AFTER* it was switched" ~ 15,
+  adult_clean_eliz$noticed_water_issue=="1 year and 1 month *AFTER* it was switched" ~ 13
+)
+
+adult_clean_eliz$waterlinereplaced <- ifelse(adult_clean_eliz$water_line_status_after_april2014=="My lead/water lines were replaced", 1, ifelse(is.na(adult_clean_eliz$water_line_status_after_april2014), NA_real_, 0))
+
+subadult <- mutate(adult_clean_eliz, parbloodtestf = blood_test_after_april_2014, parbllf = elevated_lead_after_april_2014, parrashesf = rashes_after_april_2014, parhairf = hairloss_after_april_2014, parnausf = nausea_after_april_2014, parirrf = irritable_after_april_2014, parbloodtestc = getscreened, parbllc = elevated_collapse, parrashesc = rash_collapse, parhairc = hair_collapse, parnausc = nausea_collapse, parirrc = irritable_collapse, paroverall = overall_collapse) %>% select(inclusion, unique_id, age, gender, collapserace, collapseeduc, have_health_insurance, public_benefits, water_exaggerated, children_health_harmed, trust_government_in_future, drink_tap_in_three_years, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, political_affiliation, nightmares, avoided_thinking_crisis, onguard_watchful, numb_detached, felt_guilty, ptsdscore, phq, parbloodtestf, parbllf, parrashesf, parhairf, parnausf, parirrf, parbloodtestc, parbllc, parrashesc, parhairc, parnausc, parirrc, paroverall, confidants2, number_children, employ_status, num_time_notice, watertestbinary, current_zip, waterlinereplaced)
 
@@
 
-child_adult$gettested <- ifelse(child_adult$blood_test_after_april_2014=="Yes" & child_adult$blood_test_before_april_2014=="No", 1, ifelse(is.na(child_adult$blood_test_after_april_2014) | is.na(child_adult$blood_test_before_april_2014), NA_real_, 0))
+samp1 <- nrow(child_adult)
 
-child_adult$elevbll <- ifelse(child_adult$elevated_lead_after_april_2014=="Yes" & child_adult$elevated_lead_before_april_2014=="No", 1, ifelse(is.na(child_adult$elevated_lead_after_april_2014) | is.na(child_adult$elevated_lead_before_april_2014), NA_real_, 0))
+#child_adult <- filter(child_adult, age.x >= 5)
+child_adult <- filter(child_adult, age.x >= 0.5)
+samp2 <- nrow(child_adult)
 
-child_adult$rash <- ifelse(child_adult$rash_after_april_2014=="Yes" & child_adult$rash_before_april_2014=="No", 1, ifelse(is.na(child_adult$rash_after_april_2014) | is.na(child_adult$rash_before_april_2014), NA_real_, 0))
+##child_adult <- filter(child_adult, relationship == "Your child" | relationship == "Your grandchild")
 
-child_adult$hair <- ifelse(child_adult$hairloss_after_april_2014=="Yes" & child_adult$hairloss_before_april_2014=="No", 1, ifelse(is.na(child_adult$hairloss_after_april_2014) | is.na(child_adult$hairloss_before_april_2014), NA_real_, 0))
+#child_adult$gettested <- ifelse(child_adult$blood_test_after_april_2014=="Yes" & child_adult$blood_test_before_april_2014=="No", 1, ifelse(is.na(child_adult$blood_test_after_april_2014) | is.na(child_adult$blood_test_before_april_2014), NA_real_, 0))
 
-child_adult$learn <- ifelse(child_adult$learning_after_april_2014=="Yes" & child_adult$learning_before_april_2014=="No", 1, ifelse(is.na(child_adult$learning_after_april_2014) | is.na(child_adult$learning_before_april_2014), NA_real_, 0))
+child_adult$gettested <- ifelse(child_adult$blood_test_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$blood_test_after_april_2014), NA_real_, 0))
 
-child_adult$hyper <- ifelse(child_adult$hyper_after_april_2014=="Yes" & child_adult$hyper_before_april_2014=="No", 1, ifelse(is.na(child_adult$hyper_after_april_2014) | is.na(child_adult$hyper_before_april_2014), NA_real_, 0))
+#child_adult$elevbll <- ifelse(child_adult$elevated_lead_after_april_2014=="Yes" & child_adult$elevated_lead_before_april_2014=="No", 1, ifelse(is.na(child_adult$elevated_lead_after_april_2014) | is.na(child_adult$elevated_lead_before_april_2014), NA_real_, 0))
 
-child_adult$irritable <- ifelse(child_adult$irritable_after_april_2014=="Yes" & child_adult$irritable_before_april_2014=="No", 1, ifelse(is.na(child_adult$irritable_after_april_2014) | is.na(child_adult$irritable_before_april_2014), NA_real_, 0))
+child_adult$elevbll <- ifelse(child_adult$elevated_lead_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$elevated_lead_after_april_2014), NA_real_, 0))
+
+#child_adult$rash <- ifelse(child_adult$rash_after_april_2014=="Yes" & child_adult$rash_before_april_2014=="No", 1, ifelse(is.na(child_adult$rash_after_april_2014) | is.na(child_adult$rash_before_april_2014), NA_real_, 0))
+
+child_adult$rash <- ifelse(child_adult$rash_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$rash_after_april_2014), NA_real_, 0))
+
+#child_adult$hair <- ifelse(child_adult$hairloss_after_april_2014=="Yes" & child_adult$hairloss_before_april_2014=="No", 1, ifelse(is.na(child_adult$hairloss_after_april_2014) | is.na(child_adult$hairloss_before_april_2014), NA_real_, 0))
+
+child_adult$hair <- ifelse(child_adult$hairloss_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$hairloss_after_april_2014), NA_real_, 0))
+
+#child_adult$learn <- ifelse(child_adult$learning_after_april_2014=="Yes" & child_adult$learning_before_april_2014=="No", 1, ifelse(is.na(child_adult$learning_after_april_2014) | is.na(child_adult$learning_before_april_2014), NA_real_, 0))
+
+child_adult$learn <- ifelse(child_adult$learning_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$learning_after_april_2014), NA_real_, 0))
+
+#child_adult$hyper <- ifelse(child_adult$hyper_after_april_2014=="Yes" & child_adult$hyper_before_april_2014=="No", 1, ifelse(is.na(child_adult$hyper_after_april_2014) | is.na(child_adult$hyper_before_april_2014), NA_real_, 0))
+
+child_adult$hyper <- ifelse(child_adult$hyper_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$hyper_after_april_2014), NA_real_, 0))
+
+#child_adult$irritable <- ifelse(child_adult$irritable_after_april_2014=="Yes" & child_adult$irritable_before_april_2014=="No", 1, ifelse(is.na(child_adult$irritable_after_april_2014) | is.na(child_adult$irritable_before_april_2014), NA_real_, 0))
+
+child_adult$irritable <- ifelse(child_adult$irritable_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$irritable_after_april_2014), NA_real_, 0))
+
+child_adult$watersource2 <- ifelse(child_adult$watersource=="Bottled water", 1, ifelse(is.na(child_adult$watersource), NA_real_, 0))
+
+child_adult$employ_status2 <- ifelse(child_adult$employ_status=="Employed", "Employed", ifelse(child_adult$employ_status=="Unemployed", "Unemployed", ifelse(is.na(child_adult$employ_status), NA_character_, "Other")))
 
@@
 )
+
+exam <- select(child_adult, child, unique_id, relationship, age.x, gender.x, public_benefits, gettested, elevbll, rash, hair, learn, hyper, irritable, overall_symp, racecollapse, blood_test_after_april_2014, water_exaggerated)
+
+child_adult2 <- child_adult[complete.cases(exam)]
+child_adult <- child_adult2
 ```
 
-First, let's get some descriptives:
-```{r, echo=TRUE, message=FALSE, warning=FALSE}
-child_adult$relationship <- factor(child_adult$relationship, levels=c("Your child", "Your brother or stepbrother", "Your sister or stepsister", "Your niece or nephew", "Your friend's or acquaintance's child or relative", "Your grandchild", "Other relationship"), ordered=TRUE)
+## Introductory Remarks
 
+This report was an attempt to respond to two key reviewer concerns: 1) the presence of children under age 5 in our data--and thus not alive in April 2014, when the water switch happened, and 2) what to do with children who were described by a caregiver who wasn't their parent or grandparent.
+
+I tried a number of things to figure out what to do with children under age 5.
+Part of the problem here is that we were looking at excess mortality outcomes (i.e.
+"Did the child have this symptom after but not before April 2014?"), and for children under age 5, this wasn't defined, since the child wasn't alive before April 2014.
+I considered looking at 1) just the after outcome ("Did the child have this symptom after April 2014, regardless of whether they had it before 2014?") or 2) forcibly assuming that children under age 5 didn't have the symptom before April 2014.
+I was disturbed that these two outcome definitions resulted in  different results, with outcome definition (2) yielding many significant results, while outcome definition (1) yielded almost no significant results and different directions of association.
+That's bad news.
+Initially, I thought we would exclude all children under age 5.
+However, after more discussions with Jerel, we instead decided to restrict to children ages 6 months and up, and use outcome definition (1).
+
+I then looked a little more closely at the second inclusion criteria: children described by an aunt/uncle/babysitter/sibling, rather than a parent/grandparent.
+After investigating these children more closely, I concluded that we should keep them.
+They aren't significantly different from children described by a parent/grandparent, and including them in the sample doesn't affect the direction/magnitude of any associations, but it *does* increase our sample size enough to start seeing significant findings, because the larger sample size shrinks the standard errors.
+
+Therefore, I have concluded that our inclusion criteria will be children ages 6 months and up, considering outcomes based on just after April 2014 (and not before) described by any caregiver living in the City of Flint.
+
+\newpage
+
+## Descriptives
+
+Initially, our data consisted of `r samp1` children.
+I then impose our first inclusion criterion: children age 6 months and up.
+This takes the sample down to `r samp2` children.
+Then I restrict to children with complete data for all predictors used in modeling.
+This results in a sample of `r nrow(child_adult)` children.
+
+Here are some descriptives on these children:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+child_adult$relationship <- factor(child_adult$relationship, levels=c("Your child", "Your grandchild", "Your sister or stepsister", "Your brother or stepbrother", "Your niece or nephew", "Your friend's or acquaintance's child or relative", "Other relationship"), ordered = TRUE)
+child_adult$watersource2 <- factor(child_adult$watersource2, levels=c(0, 1), labels=c("Non-bottled water", "Bottled water"))
 child_adult$gettested <- factor(child_adult$gettested, levels=c(0, 1), labels=c("No", "Yes"))
@@
 var_label(child_adult$gender.x) <- "Child gender"
-var_label(child_adult$watersource) <- "Child water source"
-var_label(child_adult$gettested) <- "Blood lead test after April 2014 and not before"
-var_label(child_adult$elevbll) <- "Elevated BLLs after April 2014 and not before"
-var_label(child_adult$rash) <- "Rashes after April 2014 and not before"
-var_label(child_adult$hair) <- "Hair loss after April 2014 and not before"
-var_label(child_adult$learn) <- "Learning delays after April 2014 and not before"
-var_label(child_adult$hyper) <- "Hyperactivity after April 2014 and not before"
-var_label(child_adult$irritable) <- "Irritability after April 2014 and not before"
-var_label(child_adult$overall_symp) <- "Total number of symptoms after April 2014 and not before"
+var_label(child_adult$watersource2) <- "Child water source"
+var_label(child_adult$gettested) <- "Blood lead test after April 2014"
+var_label(child_adult$elevbll) <- "Elevated BLLs after April 2014"
+var_label(child_adult$rash) <- "Rashes after April 2014"
+var_label(child_adult$hair) <- "Hair loss after April 2014"
+var_label(child_adult$learn) <- "Learning delays after April 2014"
+var_label(child_adult$hyper) <- "Hyperactivity after April 2014"
+var_label(child_adult$irritable) <- "Irritability after April 2014"
+var_label(child_adult$overall_symp) <- "Total number of symptoms after April 2014"
 var_label(child_adult$gendercollapse) <- "Guardian's gender"
@@
 var_label(child_adult$age.y) <- "Guardian's age"
-var_label(child_adult$employ_status) <- "Guardian's employment status"
+var_label(child_adult$employ_status2) <- "Guardian's employment status"
 
@@
 
-child_adult <- arrange(child_adult, unique_id, racecollapse)
+child_adult$racecollapse2 <- case_when(
+  child_adult$racecollapse=="Black" ~ "Black",
+  child_adult$racecollapse=="White" | child_adult$racecollapse=="Other" ~ "White/Other",
+  is.na(child_adult$racecollapse) ~ NA_character_
+)
+
+child_adult$racecollapse2 <- factor(child_adult$racecollapse2)
+
+child_adult <- arrange(child_adult, unique_id, racecollapse, racecollapse2)
 
@@
 pvalues <- rbind(pvalues, data.frame("Outcome" = "Gender", "Pvalue" = anova(m)$`Pr(>F)`))
-m <- art(factor(watersource, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$watersource),])
-pvalues <- rbind(pvalues, data.frame("Outcome" = "Watersource", "Pvalue" = anova(m)$`Pr(>F)`))
+m <- art(factor(watersource2, ordered=TRUE) ~ racecollapse2 + (1 | unique_id), data=child_adult[!is.na(child_adult$watersource2),])
+#pvalues <- rbind(pvalues, data.frame("Outcome" = "Watersource", "Pvalue" = anova(m)$`Pr(>F)`))
+pvalues <- rbind(pvalues, data.frame("Outcome" = "Watersource", "Pvalue" = NA_real_))
 m <- art(factor(gettested, ordered=TRUE) ~ racecollapse + (1 | unique_id), data=child_adult[!is.na(child_adult$gettested),])
@@
 pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian receives public benefits", "Pvalue" = anova(m)$`Pr(>F)`))
-m <- art(factor(racecollapse, ordered=TRUE) ~ factor(employ_status, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$employ_status),])
+m <- art(factor(racecollapse, ordered=TRUE) ~ factor(employ_status2, ordered=TRUE) + (1 | unique_id), data=child_adult[!is.na(child_adult$employ_status2),])
 pvalues <- rbind(pvalues, data.frame("Outcome" = "Guardian's employment status", "Pvalue" = anova(m)$`Pr(>F)`))
@@
 
-table_pred <- CreateTableOne(vars=c("relationship", "age.x", "gender.x", "watersource", "age.y", "gendercollapse", "collapserace", "collapseeduc", "public_benefits", "employ_status"), strata = "racecollapse", data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)
+table_pred <- CreateTableOne(vars=c("relationship", "age.x", "gender.x", "age.y", "gendercollapse", "collapserace", "collapseeduc", "public_benefits", "employ_status2"), strata = "racecollapse", data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)
 
-table_pred_nostrat <- CreateTableOne(vars=c("relationship", "age.x", "gender.x", "watersource", "age.y", "gendercollapse", "collapserace", "collapseeduc", "public_benefits", "employ_status"), data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)
+table_pred_nostrat <- CreateTableOne(vars=c("relationship", "age.x", "gender.x", "age.y", "gendercollapse", "collapserace", "collapseeduc", "public_benefits", "employ_status2"), data=child_adult, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)
 
@@
 
-kable(print(table_pred, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:9, 13:18, 22:24, 26:30, 32:34, 36:39)) %>% kable_styling(position="center")
+test <- print(table_pred, contDigits=1, varLabel = T, printToggle=FALSE)
+test["Child's relationship to survey respondent (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Relationship", 2], digits = 3))
+test["Child age (mean (SD))", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Child age", 2], digits = 3))
+test["Child gender = Male (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Gender", 2], digits = 3))
+test["Guardian's age (mean (SD))", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian age", 2], digits = 3))
+test["Guardian's gender = Male (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's Gender", 2], digits = 3))
+test["Guardian's race/ethnicity (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's Race", 2], digits = 3))
+test["Guardian's education (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's Education", 2], digits = 3))
+test["Guardian receives public benefits (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian receives public benefits", 2], digits = 3))
+test["Guardian's employment status (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Guardian's employment status", 2], digits = 3))
 
-kable(print(table_pred_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:9, 13:18, 22:24, 26:30, 32:34, 36:39)) %>% kable_styling(position="center")
+test2 <- print(table_outcome, contDigits=1, varLabel = T, printToggle=FALSE)
+test2["Blood lead test after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="BloodTest", 2], digits = 3))
+test2["Elevated BLLs after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="BLLs", 2], digits = 3))
+test2["Rashes after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Rash", 2], digits = 3))
+test2["Hair loss after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Hairloss", 2], digits = 3))
+test2["Learning delays after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Learning", 2], digits = 3))
+test2["Hyperactivity after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Hyper", 2], digits = 3))
+test2["Irritability after April 2014 = Yes (%)", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Irritable", 2], digits = 3))
+test2["Total number of symptoms after April 2014 (mean (SD))", "p"] <- paste0(round(pvalues[pvalues$Outcome=="Overall", 2], digits = 3))
 
-kable(print(table_outcome, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:5, 7:9, 11:13, 15:17, 19:21, 23:25, 27:29)) %>% kable_styling(position="center")
+kable(test, booktabs=T) %>% add_indent(c(3:9, 15:17, 19:23, 25:27, 29:31)) %>% kable_styling(position="center")
 
-kable(print(table_outcome_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:5, 7:9, 11:13, 15:17, 19:21, 23:25, 27:29)) %>% kable_styling(position="center")
+kable(print(table_pred_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(3:9, 15:17, 19:23, 25:27, 29:31)) %>% kable_styling(position="center")
+
+kable(test2, booktabs=T) %>% kable_styling(position="center")
+
+kable(print(table_outcome_nostrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% kable_styling(position="center")
 ```
 
-Now, onto modeling for children health outcomes:
-```{r, echo=TRUE, message=FALSE, warning=FALSE}
+\newpage
+
+## Multivariable modeling results
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 #For water source:
+child_adult$water_exaggeratedbinary <- as.numeric(child_adult$water_exaggerated=="Agree" | child_adult$water_exaggerated=="Strongly Agree")
 child_adult$pubben <- ifelse(child_adult$public_benefits=="Yes", 1, ifelse(is.na(child_adult$public_benefits), NA_real_, 0))
@@
 
-watersource_model <- glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ##issues with convergence; did not include
+##watersource_model <- glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ##issues with convergence; did not include
+
+##summary(watersource_model)
 
 #For getting tested:
-#child_adult$gettested <- ifelse(child_adult$blood_test_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$blood_test_after_april_2014), NA_real_, 0))
+tested_model_noadult <- glmer(gettested ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
+tested_model_adult <- glmer(gettested ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = child_adult, family = "binomial")
 
-tested_model_noadult <- glmer(gettested ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
+summary(tested_model_noadult)
+summary(tested_model_adult)
 
-effects_mat <- data.frame("Outcome" = rep("Get tested", 5), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits"), "Estimate" = summary(tested_model_noadult)$coefficients[-1,1], "StErr" = summary(tested_model_noadult)$coefficients[-1,2], "Pvalue" = summary(tested_model_noadult)$coefficients[-1,4])
+effects_mat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = c(summary(tested_model_noadult)$coefficients[-1,1], summary(tested_model_adult)$coefficients[7,1]), "StErr" = c(summary(tested_model_noadult)$coefficients[-1,2], summary(tested_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(tested_model_noadult)$coefficients[-1,4], summary(tested_model_adult)$coefficients[7,4]))
 
 #For having elevated BLLs:
-#child_adult$elevbll <- ifelse(child_adult$elevated_lead_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$elevated_lead_after_april_2014), NA_real_, 0))
+#bll_model_noadult <- glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
+#bll_model_adult <- glmer(elevbll ~ gender.x + scale(age.x) + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial") # Not included due to convergence issues
 
-bll_model_noadult <- glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-bll_model_adult <- glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial") # + parbllc
+#summary(bll_model_noadult)
+#summary(bll_model_adult)
 
-subdat <- data.frame("Outcome" = rep("Elevated BLLs", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(bll_model_noadult)$coefficients[-1,1], summary(bll_model_adult)$coefficients[7,1]), "StErr" = c(summary(bll_model_noadult)$coefficients[-1,2], summary(bll_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(bll_model_noadult)$coefficients[-1,4], summary(bll_model_adult)$coefficients[7,4]))
+#subdat <- data.frame("Outcome" = rep("Elevated BLLs", 5), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits"), "Estimate" = c(summary(bll_model_noadult)$coefficients[-1,1]), "StErr" = c(summary(bll_model_noadult)$coefficients[-1,2]), "Pvalue" = c(summary(bll_model_noadult)$coefficients[-1,4]))
 
-effects_mat <- rbind(effects_mat, subdat)
+#effects_mat <- rbind(effects_mat, subdat)
 
 #For having rashes:
-#child_adult$rash <- ifelse(child_adult$rash_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$rash_after_april_2014), NA_real_, 0))
+rash_model_noadult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
+summary(rash_model_noadult)
+rash_model_adult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
+summary(rash_model_adult)
 
-rash_model_noadult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-rash_model_adult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial")
-
-subdat <- data.frame("Outcome" = rep("Rashes", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(rash_model_noadult)$coefficients[-1,1], summary(rash_model_adult)$coefficients[7,1]), "StErr" = c(summary(rash_model_noadult)$coefficients[-1,2], summary(rash_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(rash_model_noadult)$coefficients[-1,4], summary(rash_model_adult)$coefficients[7,4]))
+subdat <- data.frame("Outcome" = rep("Rashes", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(rash_model_noadult)$coefficients[-1,1], summary(rash_model_adult)$coefficients[7,1]), "StErr" = c(summary(rash_model_noadult)$coefficients[-1,2], summary(rash_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(rash_model_noadult)$coefficients[-1,4], summary(rash_model_adult)$coefficients[7,4]))
 
@@
 #For having hair loss:
-#child_adult$hair <- ifelse(child_adult$hairloss_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$hairloss_after_april_2014), NA_real_, 0))
+#hair_model_noadult <- glmer(hair ~ gender.x + scale(age.x) + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include
+#summary(hair_model_noadult)
+#hair_model_adult <- glmer(hair ~ gender.x + scale(age.x) + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include
+#summary(hair_model_adult)
 
-hair_model_noadult <- glmer(hair ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include
-hair_model_adult <- glmer(hair ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include
+#subdat <- data.frame("Outcome" = rep("Hairloss", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(hair_model_noadult)$coefficients[-1,1], summary(hair_model_adult)$coefficients[7,1]), "StErr" = c(summary(hair_model_noadult)$coefficients[-1,2], summary(hair_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(hair_model_noadult)$coefficients[-1,4], summary(hair_model_adult)$coefficients[7,4]))
+
+#effects_mat <- rbind(effects_mat, subdat)
 
 #For having learning delays:
-#child_adult$learn <- ifelse(child_adult$learning_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$learning_after_april_2014), NA_real_, 0))
+learn_model_noadult <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
+summary(learn_model_noadult)
 
-learn_model_noadult <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-learn_model_layer2 <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial")
+learn_model_layer2 <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
+summary(learn_model_layer2)
 
-subdat <- data.frame("Outcome" = rep("Learning Delays", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(learn_model_noadult)$coefficients[-1,1], summary(learn_model_layer2)$coefficients[7,1]), "StErr" = c(summary(learn_model_noadult)$coefficients[-1,2], summary(learn_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(learn_model_noadult)$coefficients[-1,4], summary(learn_model_layer2)$coefficients[7,4]))
+subdat <- data.frame("Outcome" = rep("Learning Delays", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(learn_model_noadult)$coefficients[-1,1], summary(learn_model_layer2)$coefficients[7,1]), "StErr" = c(summary(learn_model_noadult)$coefficients[-1,2], summary(learn_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(learn_model_noadult)$coefficients[-1,4], summary(learn_model_layer2)$coefficients[7,4]))
 
@@
 #For having hyperactivity:
-#child_adult$hyper <- ifelse(child_adult$hyper_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$hyper_after_april_2014), NA_real_, 0))
+hyper_model_noadult <- glmer(hyper ~ gender.x + scale(age.x) + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
+summary(hyper_model_noadult)
 
-hyper_model_noadult <- glmer(hyper ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-hyper_model_layer2 <- glmer(hyper ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial")
+hyper_model_layer2 <- glmer(hyper ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
+summary(hyper_model_layer2)
 
-subdat <- data.frame("Outcome" = rep("Hyperactivity", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(hyper_model_noadult)$coefficients[-1,1], summary(hyper_model_layer2)$coefficients[7,1]), "StErr" = c(summary(hyper_model_noadult)$coefficients[-1,2], summary(hyper_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(hyper_model_noadult)$coefficients[-1,4], summary(hyper_model_layer2)$coefficients[7,4]))
+subdat <- data.frame("Outcome" = rep("Hyperactivity", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(hyper_model_noadult)$coefficients[-1,1], summary(hyper_model_layer2)$coefficients[7,1]), "StErr" = c(summary(hyper_model_noadult)$coefficients[-1,2], summary(hyper_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(hyper_model_noadult)$coefficients[-1,4], summary(hyper_model_layer2)$coefficients[7,4]))
 
@@
 #For having irritability:
-#child_adult$irritable <- ifelse(child_adult$irritable_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$irritable_after_april_2014), NA_real_, 0))
+irr_model_noadult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
+summary(irr_model_noadult)
+irr_model_adult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
+summary(irr_model_adult)
 
-irr_model_noadult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-irr_model_adult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult, family = "binomial")
-
-subdat <- data.frame("Outcome" = rep("Irritability", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(irr_model_noadult)$coefficients[-1,1], summary(irr_model_adult)$coefficients[7,1]), "StErr" = c(summary(irr_model_noadult)$coefficients[-1,2], summary(irr_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(irr_model_noadult)$coefficients[-1,4], summary(irr_model_adult)$coefficients[7,4]))
+subdat <- data.frame("Outcome" = rep("Irritability", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(irr_model_noadult)$coefficients[-1,1], summary(irr_model_adult)$coefficients[7,1]), "StErr" = c(summary(irr_model_noadult)$coefficients[-1,2], summary(irr_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(irr_model_noadult)$coefficients[-1,4], summary(irr_model_adult)$coefficients[7,4]))
 
@@
 #For overall symptoms:
-overall_model_noadult <- glmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult)
-overall_model_adult <- glmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + gettested + (1 | unique_id), data = child_adult)
+overall_model_noadult <- lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult)
+summary(overall_model_noadult)
 
-subdat <- data.frame("Outcome" = rep("Overall Symptoms", 6), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits", "Child Screened"), "Estimate" = c(summary(overall_model_noadult)$coefficients[-1,1], summary(overall_model_adult)$coefficients[7,1]), "StErr" = c(summary(overall_model_noadult)$coefficients[-1,2], summary(overall_model_adult)$coefficients[7,2]), "Pvalue" = pnorm(c(summary(overall_model_noadult)$coefficients[-1,3], summary(overall_model_adult)$coefficients[7,3]), lower.tail = FALSE))
+overall_model_adult <- lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + water_exaggeratedbinary + (1 | unique_id), data = child_adult)
+summary(overall_model_adult)
+
+subdat <- data.frame("Outcome" = rep("Overall Symptoms", 7), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = c(summary(overall_model_noadult)$coefficients[-1,1], summary(overall_model_adult)$coefficients[7:8,1]), "StErr" = c(summary(overall_model_noadult)$coefficients[-1,2], summary(overall_model_adult)$coefficients[7:8,2]), "Pvalue" = pnorm(c(summary(overall_model_noadult)$coefficients[-1,3], summary(overall_model_adult)$coefficients[7:8,3]), lower.tail = FALSE))
 
@@
 
-And now modeling for adult experiences:
-```{r, echo=TRUE, message=FALSE, warning=FALSE}
-##Assembling child health indicators:
-child_sum <- group_by(child_adult, unique_id) %>% summarise(child_screen = as.numeric(sum(as.numeric(gettested)-1, na.rm=TRUE) > 0), child_symps = sum(overall_symp), child_bll = as.numeric(sum(as.numeric(elevbll)-1, na.rm=TRUE) > 0), child_rash = as.numeric(sum(as.numeric(rash)-1, na.rm=TRUE) > 0), child_hair = as.numeric(sum(as.numeric(hair)-1, na.rm=TRUE) > 0), child_learning = as.numeric(sum(as.numeric(learn)-1, na.rm=TRUE) > 0), child_hyper = as.numeric(sum(as.numeric(hyper)-1, na.rm=TRUE) > 0), child_irritable = as.numeric(sum(as.numeric(irritable)-1, na.rm=TRUE) > 0))
-
-child_adult_sub <- unique(select(child_adult, unique_id, age.y, gendercollapse, collapserace, collapseeduc, pubben, water_exaggerated, children_health_harmed, trust_government_in_future, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, ptsdscore, phq, parbloodtestc, parbllc, parrashesc, parhairc, parnausc, parirrc, paroverall, confidants2, number_children))
-
-child_adult_sum <- left_join(child_adult_sub, child_sum, by=c("unique_id"))
-
-##Outcome: believing water crisis exaggerated
-exaggerated_layer1 <- glm(as.numeric(water_exaggerated=="Agree" | water_exaggerated=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 + number_children, data = child_adult_sum, family = "binomial")
-exaggerated_layer2 <- logistf(as.numeric(water_exaggerated=="Agree" | water_exaggerated=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 +  number_children + paroverall + child_symps + child_screen + child_bll + child_rash + child_learning + child_hyper + child_irritable, data = child_adult_sum)
-test <- summary(exaggerated_layer2)
-
-subdat <- data.frame("Outcome" = rep("Crisis Exaggerated", 15), "Variable" = c("Guardian Age", "Guardian Male", "Guardian Race-Other", "Guardian Race-White", "Public Benefits", "Number of confidants", "Number of children", "Number of adult symptoms", "Number of child symptoms", "Child screened", "Child with BLL", "Child with Rash", "Child with Learning", "Child with Hyper", "Child with Irritability"), "Estimate" = c(summary(exaggerated_layer1)$coefficients[-1,1], test$coefficients[9:16]), "StErr" = c(summary(exaggerated_layer1)$coefficients[-1,2], sqrt(diag(test$var)[9:16])), "Pvalue" = c(summary(exaggerated_layer1)$coefficients[-1,4], test$prob[9:16]))
-
-effects_mat <- rbind(effects_mat, subdat)
-
-##Outcome: believing children's health was harmed
-health_layer1 <- glm(as.numeric(children_health_harmed=="Agree" | children_health_harmed=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 + number_children, data = child_adult_sum, family = "binomial")
-health_layer2 <- glm(as.numeric(children_health_harmed=="Agree" | children_health_harmed=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 +  number_children + paroverall + child_symps + child_screen + child_bll + child_rash + child_learning + child_hyper + child_irritable, data = child_adult_sum, family = "binomial")
-
-subdat <- data.frame("Outcome" = rep("Children's Health Harmed", 15), "Variable" = c("Guardian Age", "Guardian Male", "Guardian Race-Other", "Guardian Race-White", "Public Benefits", "Number of confidants", "Number of children", "Number of adult symptoms", "Number of child symptoms", "Child screened", "Child with BLL", "Child with Rash", "Child with Learning", "Child with Hyper", "Child with Irritability"), "Estimate" = c(summary(health_layer1)$coefficients[-1,1], summary(health_layer2)$coefficients[9:16,1]), "StErr" = c(summary(health_layer1)$coefficients[-1,2], summary(health_layer2)$coefficients[9:16,2]), "Pvalue" = c(summary(health_layer1)$coefficients[-1,4], summary(health_layer2)$coefficients[9:16,4]))
-
-effects_mat <- rbind(effects_mat, subdat)
-
-##Outcome: having trust in government
-trust_layer1 <- glm(as.numeric(trust_government_in_future=="Agree" | trust_government_in_future=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 + number_children, data = child_adult_sum, family = "binomial")
-trust_layer2 <- glm(as.numeric(trust_government_in_future=="Agree" | trust_government_in_future=="Strongly Agree") ~ age.y + gendercollapse + collapserace + pubben + confidants2 +  number_children + paroverall + child_symps + child_screen + child_bll + child_rash + child_learning + child_hyper + child_irritable, data = child_adult_sum, family = "binomial")
-
-subdat <- data.frame("Outcome" = rep("Trust government", 15), "Variable" = c("Guardian Age", "Guardian Male", "Guardian Race-Other", "Guardian Race-White", "Public Benefits", "Number of confidants", "Number of children", "Number of adult symptoms", "Number of child symptoms", "Child screened", "Child with BLL", "Child with Rash", "Child with Learning", "Child with Hyper", "Child with Irritability"), "Estimate" = c(summary(trust_layer1)$coefficients[-1,1], summary(trust_layer2)$coefficients[9:16,1]), "StErr" = c(summary(trust_layer1)$coefficients[-1,2], summary(trust_layer2)$coefficients[9:16,2]), "Pvalue" = c(summary(trust_layer1)$coefficients[-1,4], summary(trust_layer2)$coefficients[9:16,4]))
-
-effects_mat <- rbind(effects_mat, subdat)
-
-##Outcome: PTSD
-ptsd_layer1 <- glm(as.numeric(ptsdscore >= 3) ~ age.y + gendercollapse + collapserace + pubben + confidants2 + number_children, data = child_adult_sum, family = "binomial")
-ptsd_layer2 <- glm(as.numeric(ptsdscore >= 3) ~ age.y + gendercollapse + collapserace + pubben + confidants2 +  number_children + paroverall + child_symps + child_screen + child_bll + child_rash + child_learning + child_hyper + child_irritable, data = child_adult_sum, family = "binomial")
-
-subdat <- data.frame("Outcome" = rep("PTSD", 15), "Variable" = c("Guardian Age", "Guardian Male", "Guardian Race-Other", "Guardian Race-White", "Public Benefits", "Number of confidants", "Number of children", "Number of adult symptoms", "Number of child symptoms", "Child screened", "Child with BLL", "Child with Rash", "Child with Learning", "Child with Hyper", "Child with Irritability"), "Estimate" = c(summary(ptsd_layer1)$coefficients[-1,1], summary(ptsd_layer2)$coefficients[9:16,1]), "StErr" = c(summary(ptsd_layer1)$coefficients[-1,2], summary(ptsd_layer2)$coefficients[9:16,2]), "Pvalue" = c(summary(ptsd_layer1)$coefficients[-1,4], summary(ptsd_layer2)$coefficients[9:16,4]))
-
-effects_mat <- rbind(effects_mat, subdat)
-
-##Outcome: PHQ
-phq_layer1 <- glm(as.numeric(phq >= 6) ~ age.y + gendercollapse + collapserace + pubben + confidants2 + number_children, data = child_adult_sum, family = "binomial")
-phq_layer2 <- glm(as.numeric(phq >= 6) ~ age.y + gendercollapse + collapserace + pubben + confidants2 +  number_children + paroverall + child_symps + child_screen + child_bll + child_rash + child_learning + child_hyper + child_irritable, data = child_adult_sum, family = "binomial")
-
-subdat <- data.frame("Outcome" = rep("Depression", 15), "Variable" = c("Guardian Age", "Guardian Male", "Guardian Race-Other", "Guardian Race-White", "Public Benefits", "Number of confidants", "Number of children", "Number of adult symptoms", "Number of child symptoms", "Child screened", "Child with BLL", "Child with Rash", "Child with Learning", "Child with Hyper", "Child with Irritability"), "Estimate" = c(summary(phq_layer1)$coefficients[-1,1], summary(phq_layer2)$coefficients[9:16,1]), "StErr" = c(summary(phq_layer1)$coefficients[-1,2], summary(phq_layer2)$coefficients[9:16,2]), "Pvalue" = c(summary(phq_layer1)$coefficients[-1,4], summary(phq_layer2)$coefficients[9:16,4]))
-
-effects_mat <- rbind(effects_mat, subdat)
-```
-
-Now we tidy up our effects matrix and apply a multiple testing correction:
-```{r, echo=TRUE, message=FALSE, warning=FALSE}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 effects_mat$BHpvalue <- p.adjust(effects_mat$Pvalue, method="BH")
@@
 pretty_effects <- select(effects_mat, Outcome, Variable, label, BHpvalue)
+pretty_effects$BHpvalue <- round(pretty_effects$BHpvalue, 3)
+rownames(pretty_effects) <- NULL
+
+kable(pretty_effects, col.names = c("Outcome", "Predictor", "Odds Ratio (95% CI)", "P-value"))
 ```
+
+Note that these modeling results doesn't include one important outcomes: child water source.
+I was unable to get this model to fit stably because of the small number of children not drinking bottled water.
+In addition, I couldn't consider the effect of the caregiver believing the water crisis was exaggerated on most of the outcomes because of convergence issues, and similarly with the relationship between the child being tested and the child having elevated BLLs.

### 2021-10-05 paperfour_healthbehaviors.Rmd
Update to include analysis for health behavior paper, and to revise child health analysis using Bayesian models.

---
title: 'Manuscript 4: Health Behaviors after the Crisis'
author: "Elizabeth Chase"
date: "5/28/2021"
output: pdf_document
---

```{r setup, include=FALSE, echo=TRUE}
library(knitr)
opts_chunk$set(collapse=TRUE, fig.align='center', out.extra = '', fig.pos= "h", tidy=TRUE, tidy.opts=list(blank=TRUE, width.cutoff=40), warning=FALSE,message=FALSE)
options(scipen=999)

rm(list=ls())

library(tidyverse)
library(gridExtra)
library(RColorBrewer)
library(tableone)
library(latex2exp)
library(labelled)
library(kableExtra)
library(logistf)
library(mice)
library(survival)
library(survminer)
library(MASS)
library(ggalluvial)

mydata <- readRDS("~/Desktop/Research/Jerel Flint/Analyses/adult_data_clean.rds")

load("~/Desktop/Research/Jerel Flint/Analyses/child_long.RData")

child_sub <- group_by(child_final, unique_id) %>% summarize(bottledwater_child = sum(as.numeric(watersource=="Bottled water"), na.rm = TRUE), testpost2014_child = sum(as.numeric(blood_test_after_april_2014=="Yes"), na.rm = TRUE), bllpost2014_child = sum(as.numeric(elevated_lead_after_april_2014=="Yes"), na.rm = TRUE))

mydata <- left_join(mydata, child_sub, by = c("unique_id"))

mydata$bottledwater_child[mydata$number_children == 0] <- 0 
mydata$testpost2014_child[mydata$number_children == 0] <- 0 
mydata$bllpost2014_child[mydata$number_children == 0] <- 0

mydata$num_time_notice <- case_when(
  mydata$noticed_water_issue=="1 year *AFTER* it was switched" ~ 12,
  mydata$noticed_water_issue=="2 months *AFTER* it was switched" ~ 2,
  mydata$noticed_water_issue=="Unsure/Don't know" ~ NA_real_,
  mydata$noticed_water_issue=="2 years *AFTER* it was switched" ~ 24,
  mydata$noticed_water_issue=="Less than 1 month *AFTER* the water source was switched" ~ 0.5,
  mydata$noticed_water_issue=="1 month *AFTER* it was switched" ~ 1,
  mydata$noticed_water_issue=="3 months *AFTER* it was switched" ~ 3,
  mydata$noticed_water_issue=="1 year and 2 months *AFTER* it was switched" ~ 14,
  mydata$noticed_water_issue=="6 months *AFTER* it was switched" ~ 6,
  mydata$noticed_water_issue=="9 months *AFTER* it was switched" ~ 9,
  mydata$noticed_water_issue=="1 year and 6 months *AFTER* it was switched" ~ 18,
  mydata$noticed_water_issue=="7 months *AFTER* it was switched" ~ 7,
  mydata$noticed_water_issue=="4 years or more *AFTER* it was switched" ~ 4,
  mydata$noticed_water_issue=="10 months *AFTER* it was switched" ~ 10,
  mydata$noticed_water_issue=="5 months *AFTER* it was switched" ~ 5,
  mydata$noticed_water_issue=="11 months *AFTER* it was switched" ~ 11,
  mydata$noticed_water_issue=="4 months *AFTER* it was switched" ~ 4,
  mydata$noticed_water_issue=="1 year and 5 months *AFTER* it was switched" ~ 17,
  mydata$noticed_water_issue=="8 months *AFTER* it was switched" ~ 8,
  mydata$noticed_water_issue=="3 years *AFTER* it was switched" ~ 36,
  mydata$noticed_water_issue=="2 year and 1 month *AFTER* it was switched" ~ 25,
  mydata$noticed_water_issue=="2 year and 6 months *AFTER* it was switched" ~ 30,
  mydata$noticed_water_issue=="1 year and 3 months *AFTER* it was switched" ~ 15,
  mydata$noticed_water_issue=="1 year and 1 month *AFTER* it was switched" ~ 13
)

mydata$notice_date <- as.Date("2014-04-25") + (mydata$num_time_notice*30)

mydata$long_ago_test[mydata$watertestnum==0 & is.na(mydata$long_ago_test)] <- 0
mydata$water_test_event_ind <- ifelse(!is.na(mydata$long_ago_test), 1, ifelse(mydata$watertestnum==0 & is.na(mydata$long_ago_test), 0, NA_real_))

mydata$last_test_date <- mydata$survey_date - (mydata$long_ago_test*30)
mydata$water_test_surv <- round(as.numeric(mydata$last_test_date - as.Date("2014-04-25"))/30, digits = 0)
mydata$water_test_event_ind[mydata$water_test_surv < 0 & !is.na(mydata$water_test_surv)] <- 0
mydata$water_test_surv[mydata$water_test_surv < 0 & !is.na(mydata$water_test_surv)] <- round(as.numeric(mydata$survey_date[mydata$water_test_surv < 0 & !is.na(mydata$water_test_surv)] - as.Date("2014-04-25"))/30, digits = 0)

mydata$waterlinereplaced_longago_num <- case_when(
  mydata$waterline_replaced_when=="1 month ago" ~ 1,
  mydata$waterline_replaced_when=="1 year ago" ~ 12,
  mydata$waterline_replaced_when=="1 year and 10 months ago" ~ 22,
  mydata$waterline_replaced_when=="1 year and 2 months ago" ~ 14,
  mydata$waterline_replaced_when=="1 year and 3 months ago" ~ 15,
  mydata$waterline_replaced_when=="1 year and 4 months ago" ~ 16,
  mydata$waterline_replaced_when=="1 year and 6 months ago" ~ 18,
  mydata$waterline_replaced_when=="1 year and 7 months ago" ~ 19,
  mydata$waterline_replaced_when=="10 months ago" ~ 10,
  mydata$waterline_replaced_when=="2 months ago" ~ 2,
  mydata$waterline_replaced_when=="2 years ago" ~ 24,
  mydata$waterline_replaced_when=="2 years and 1 month ago" ~ 25,
  mydata$waterline_replaced_when=="2 years and 3 months ago" ~ 27,
  mydata$waterline_replaced_when=="2 years and 4 months ago" ~ 28,
  mydata$waterline_replaced_when=="2 years and 6 months ago" ~ 30,
  mydata$waterline_replaced_when=="2 years and 7 months ago" ~ 31,
  mydata$waterline_replaced_when=="3 months ago" ~ 3,
  mydata$waterline_replaced_when=="3 years and 6 months ago" ~ 42,
  mydata$waterline_replaced_when=="4 months ago" ~ 4,
  mydata$waterline_replaced_when=="4 years and 6 months ago" ~ 54,
  mydata$waterline_replaced_when=="5 months ago" ~ 5,
  mydata$waterline_replaced_when=="6 months ago" ~ 6,
  mydata$waterline_replaced_when=="6 OR MORE YEARS AGO" ~ 72,
  mydata$waterline_replaced_when=="7 months ago" ~ 7,
  mydata$waterline_replaced_when=="8 months ago" ~ 8,
  mydata$waterline_replaced_when=="Less than 1 month ago" ~ 0.5,
)

mydata$waterline_cured_ind <- ifelse(mydata$water_line_status_after_april2014=="A mailing or official said that my lead/water line did not need to be replaced" | mydata$water_line_status_after_april2014=="I don't live in a home" | mydata$water_line_status_after_april2014=="I know my lead/water line didn't need to be replaced but wasn't told this in a mailing or by an official", 1, ifelse(mydata$water_line_status_after_april2014=="I don't know what the status is" | mydata$water_line_status_after_april2014=="Other" | is.na(mydata$water_line_status_after_april2014), NA_real_, 0))

mydata$waterline_replaced_eventind <- ifelse(!is.na(mydata$waterlinereplaced_longago_num) | mydata$water_line_status_after_april2014=="My lead/water lines were replaced", 1, ifelse(mydata$waterline_cured_ind==1 | mydata$water_line_status_after_april2014=="I was offered a lead/water line replacement but I refused it" | mydata$water_line_status_after_april2014=="My lead/water lines haven't been replaced but I was told in a mailing/by an official they will be", 0, NA_real_))

mydata$waterlinereplaced_longago_num[mydata$waterline_replaced_eventind==0] <- 0

mydata$waterline_date <- mydata$survey_date - (mydata$waterlinereplaced_longago_num*30)

mydata$water_line_surv <- round(as.numeric(mydata$waterline_date - as.Date("2014-04-25"))/30, digits = 0)
mydata$waterline_replaced_eventind[mydata$water_line_surv < 0 & !is.na(mydata$water_line_surv)] <- 0
mydata$water_line_surv[mydata$water_line_surv < 0 & !is.na(mydata$water_line_surv)] <- round(as.numeric(mydata$survey_date[mydata$water_line_surv < 0 & !is.na(mydata$water_line_surv)] - as.Date("2014-04-25"))/30, digits = 0)
```

We start with our own data exploration: 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
print("Age:")
quantile(mydata$age)
ggplot(data = mydata, aes(x = age)) + geom_histogram() + theme_bw() + xlab("Age")

print("Gender:")
table(mydata$gender, useNA = "ifany")

print("Race/Ethnicity:")
table(mydata$reth, useNA = "ifany")

print("Education:")
table(mydata$educ_level, useNA = "ifany")

print("Marital status:")
table(mydata$marital_status, useNA = "ifany")

print("Employment status:")
table(mydata$employ_status, useNA = "ifany")

print("Years lived in Flint:")
quantile(mydata$years_cityflint)
ggplot(data = mydata, aes(x = years_cityflint)) + geom_histogram() + theme_bw() + xlab("Years in Flint")

print("Current housing:")
table(mydata$current_housing, useNA = "ifany")

print("Current ZIP code:")
table(mydata$current_zip, useNA = "ifany")

print("Health insurance:")
table(mydata$have_health_insurance, useNA = "ifany")

print("Vehicle access:")
table(mydata$access_vehicle, useNA = "ifany")

print("Water source:")
table(mydata$water_source, useNA = "ifany")

print("Months to notice a problem:")
print(paste0("Number missing: ", length(which(is.na(mydata$num_time_notice)))))
quantile(mydata$num_time_notice, na.rm = TRUE)
ggplot(data = mydata, aes(x = num_time_notice)) + geom_histogram() + theme_bw() + xlab("Months to notice a problem")

print("How many times waterline tested:")
print(paste0("Number missing: ", length(which(is.na(mydata$watertestnum)))))
quantile(mydata$watertestnum, na.rm = TRUE)
ggplot(data = mydata, aes(x = watertestnum)) + geom_histogram() + theme_bw() + xlab("Number of times tested")

print("Time of last water line test:")
print(paste0("Number missing: ", length(which(is.na(mydata$water_test_event_ind)))))
ggplot(data = mydata, aes(x = last_test_date)) + geom_bar() + theme_bw() + xlab("Last test date")
km_watertest <- survfit(Surv(water_test_surv, water_test_event_ind) ~ 1, data = mydata, conf.type = "log-log")
ggsurvplot(km_watertest, data=mydata, conf.int=TRUE, risk.table=TRUE, xlab = "Time (months)", 
                                title = "Time to Last Water Test")

print("Last water line test result:")
table(mydata$collapse_last_test, useNA = "ifany")

print("Adult blood test before April 2014:")
table(mydata$blood_test_before_april_2014, useNA = "ifany")

print("Adult blood test after April 2014:")
table(mydata$blood_test_after_april_2014, useNA = "ifany")

print("Elevated BLLs before April 2014:")
table(mydata$elevated_lead_before_april_2014, useNA = "ifany")

print("Elevated BLLs after April 2014:")
table(mydata$elevated_lead_after_april_2014, useNA = "ifany")

print("Current water source:")
table(mydata$current_water_source, useNA = "ifany")

print("Bottled water for drinking:")
table(mydata$bottled_water_drink, useNA = "ifany")

print("Bottled water for cooking:")
table(mydata$bottled_water_cook, useNA = "ifany")

print("Bottled water for bathing:")
table(mydata$bottled_water_bathe, useNA = "ifany")

print("Bottled water for brushing teeth:")
table(mydata$bottled_water_teeth, useNA = "ifany")

print("Bottled water for cleaning:")
table(mydata$bottled_water_cleaning, useNA = "ifany")

print("Bottled water for other purpose:")
table(mydata$bottled_water_other, useNA = "ifany")

print("Number of bottles per day:")
quantile(mydata$num_bottles_per_day, na.rm = TRUE)
print(paste0("Number missing: ", length(which(is.na(mydata$num_bottles_per_day)))))
ggplot(data = mydata, aes(x = num_bottles_per_day)) + geom_histogram() + theme_bw() + xlab("Number of bottles used per day")

print("Bottle disposal habits:")
table(mydata$water_bottle_disposal, useNA = "ifany")

print("Water line status after April 2014:")
table(mydata$water_line_status_after_april2014, useNA = "ifany")

print("Water line replaced when:")
print(paste0("Number missing: ", length(which(is.na(mydata$waterline_replaced_eventind)))))
ggplot(data = mydata, aes(x = waterline_date)) + geom_bar() + theme_bw() + xlab("Date of waterline replacement")
km_waterline <- survfit(Surv(water_line_surv, waterline_replaced_eventind) ~ 1, data = mydata[mydata$waterline_cured_ind==0,], conf.type = "log-log")
ggsurvplot(km_waterline, data=mydata[mydata$waterline_cured_ind==0,], conf.int=TRUE, risk.table=TRUE, xlab = "Time (months)", title = "Time to Waterline Replacement")

print("Ever used water pod:")
table(mydata$used_water_pod, useNA = "ifany")

print("Currently use water pod:")
table(mydata$get_free_bottled_water, useNA = "ifany")

print("Don't get bottled water because didn't know about it:")
table(mydata$no_free_bottles_dont_know, useNA = "ifany")

print("Don't get bottled water because of supply limits:")
table(mydata$no_free_bottles_supply_limit, useNA = "ifany")

print("Don't get bottled water because they're too far:")
table(mydata$no_free_bottles_too_far, useNA = "ifany")

print("Don't get bottled water because I lack transportation:")
table(mydata$no_free_bottles_no_transport, useNA = "ifany")

print("Don't get bottled water because their hours are bad:")
table(mydata$no_free_bottles_bad_hours, useNA = "ifany")

print("Don't get bottled water because the lines are long:")
table(mydata$no_free_bottles_long_lines, useNA = "ifany")

print("Don't get bottled water because I use my tap water:")
table(mydata$no_free_bottles_use_tap, useNA = "ifany")

print("Don't get bottled water because of another reason:")
table(mydata$no_free_bottles_other, useNA = "ifany")

print("Bottled water site:")
table(mydata$bottle_site, useNA = "ifany")

print("Will drink tap water in three years:")
table(mydata$drink_tap_in_three_years, useNA = "ifany")

print("Social network size:")
quantile(mydata$confidants2)
ggplot(data = mydata, aes(x = confidants2)) + geom_histogram() + theme_bw() + xlab("Social network size")

print("Number of children in care:")
quantile(mydata$number_children)
ggplot(data = mydata, aes(x = number_children)) + geom_histogram() + theme_bw() + xlab("Number of children in care")

print("Percent of children in care drinking bottled water:")
table(mydata$bottledwater_child/mydata$number_children, useNA = "ifany")
ggplot(data = mydata, aes(x = bottledwater_child/number_children)) + geom_bar() + theme_bw() + xlab("Percent of children drinking bottled water")

print("Percent of children in care tested for BLLs post-2014:")
table(mydata$testpost2014_child/mydata$number_children, useNA = "ifany")
ggplot(data = mydata, aes(x = testpost2014_child/number_children)) + geom_bar() + theme_bw() + xlab("Percent of children tested for BLLs after 2014")

print("Percent of children in care with elevated BLLs post-2014:")
table(mydata$bllpost2014_child/mydata$number_children, useNA = "ifany")
ggplot(data = mydata, aes(x = bllpost2014_child/number_children)) + geom_bar() + theme_bw() + xlab("Percent of children with elevated BLLs after 2014")

print("Child age:")
quantile(child_final$age)
ggplot(data = child_final, aes(x = age)) + geom_histogram() + theme_bw() + xlab("Child age")

print("Child gender:")
table(child_final$gender, useNA = "ifany")

print("Child race:")
table(child_final$reth, useNA = "ifany")

print("Child water source:")
table(child_final$watersource, useNA = "ifany")

print("Child tested for BLLs pre-2014:")
table(child_final$blood_test_before_april_2014, useNA = "ifany")

print("Child tested for BLLs post-2014:")
table(child_final$blood_test_after_april_2014, useNA = "ifany")

print("Child had elevated BLLs pre-2014:")
table(child_final$elevated_lead_before_april_2014, useNA = "ifany")

print("Child had elevated BLLs post-2014:")
table(child_final$elevated_lead_after_april_2014, useNA = "ifany")
```

Now, we do the multiple imputation we'll need for modeling further down the line:
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache = TRUE}
vars<-c("age",
        "gender",
        "reth",
        "educ_level",
        "public_benefits",
        "employ_status",
        "marital_status",
        "years_cityflint",
        "current_housing",
        "current_zip",
        "have_health_insurance",
        "access_vehicle",
        "water_source",
        "num_time_notice",
        "watertestnum",
        "water_test_surv", 
        "water_test_event_ind",
        "collapse_last_test",
        "blood_test_before_april_2014",
        "blood_test_after_april_2014",
        "elevated_lead_before_april_2014",
        "elevated_lead_after_april_2014",
        "current_water_source",
        "bottled_water_drink",
        "bottled_water_cook",
        "bottled_water_bathe",
        "bottled_water_teeth",
        "bottled_water_cleaning",
        "bottled_water_other",
        "num_bottles_per_day",
        "number_children",
        "water_bottle_disposal",
        "water_line_status_after_april2014",
        "water_line_surv", 
        "waterline_replaced_eventind",
        "waterline_cured_ind",
        "used_water_pod",
        "get_free_bottled_water",
        "no_free_bottles_dont_know",
        "no_free_bottles_supply_limit",
        "no_free_bottles_too_far",
        "no_free_bottles_no_transport",
        "no_free_bottles_bad_hours",
        "no_free_bottles_long_lines",
        "no_free_bottles_use_tap",
        "no_free_bottles_other",
        "bottle_site",
        "drink_tap_in_three_years",
        "confidants2",
        "bllpost2014_child",
        "testpost2014_child",
        "bottledwater_child"
        )

missing_plot <- VIM::aggr(mydata[,vars],
                          numbers = T,
                          sortVars = T,
                          cex.lab=0.8,
                          cex.axis=0.8,
                          # col = c("lightgreen", "darkred", "orange"),
                          # labels=str_sub(names(train[,vars]), 1, 8),
                          ylab=c("Missing Value Counts"
                                 , "Pattern"))
missing_plot

mydata_complete <- mydata[,vars]

#mydata_complete$gender <- factor(mydata_complete$gender)
mydata_complete$reth <- factor(mydata_complete$reth)
mydata_complete$educ_level <- factor(mydata_complete$educ_level)
mydata_complete$employ_status <- factor(mydata_complete$employ_status)
mydata_complete$marital_status <- factor(mydata_complete$marital_status)
mydata_complete$current_housing <- factor(mydata_complete$current_housing)
mydata_complete$current_zip <- factor(mydata_complete$current_zip)
#mydata_complete$have_health_insurance <- factor(mydata_complete$have_health_insurance)
mydata_complete$access_vehicle <- factor(mydata_complete$access_vehicle)
mydata_complete$water_source <- factor(mydata_complete$water_source)
mydata_complete$water_test_event_ind <- factor(mydata_complete$water_test_event_ind)
mydata_complete$collapse_last_test <- factor(mydata_complete$collapse_last_test)
mydata_complete$get_free_bottled_water <- factor(mydata_complete$get_free_bottled_water)
mydata_complete$used_water_pod <- factor(mydata_complete$used_water_pod)
mydata_complete$waterline_replaced_eventind <- factor(mydata_complete$waterline_replaced_eventind)
mydata_complete$water_line_status_after_april2014 <- factor(mydata_complete$water_line_status_after_april2014)
mydata_complete$water_bottle_disposal <- factor(mydata_complete$water_bottle_disposal)
mydata_complete$bottled_water_other <- factor(mydata_complete$bottled_water_other)
mydata_complete$bottled_water_cleaning <- factor(mydata_complete$bottled_water_cleaning)
mydata_complete$bottled_water_teeth <- factor(mydata_complete$bottled_water_teeth)
mydata_complete$bottled_water_bathe <- factor(mydata_complete$bottled_water_bathe)
mydata_complete$bottled_water_cook <- factor(mydata_complete$bottled_water_cook)
mydata_complete$bottled_water_drink <- factor(mydata_complete$bottled_water_drink)
mydata_complete$current_water_source <- factor(mydata_complete$current_water_source)
mydata_complete$blood_test_before_april_2014 <- factor(mydata_complete$blood_test_before_april_2014)
mydata_complete$blood_test_after_april_2014 <- factor(mydata_complete$blood_test_after_april_2014)
mydata_complete$elevated_lead_before_april_2014 <- factor(mydata_complete$elevated_lead_before_april_2014)
mydata_complete$elevated_lead_after_april_2014 <- factor(mydata_complete$elevated_lead_after_april_2014)
mydata_complete$no_free_bottles_long_lines <- factor(mydata_complete$no_free_bottles_long_lines)
mydata_complete$no_free_bottles_bad_hours <- factor(mydata_complete$no_free_bottles_bad_hours)
mydata_complete$no_free_bottles_no_transport <- factor(mydata_complete$no_free_bottles_no_transport)
mydata_complete$no_free_bottles_too_far <- factor(mydata_complete$no_free_bottles_too_far)
mydata_complete$no_free_bottles_supply_limit <- factor(mydata_complete$no_free_bottles_supply_limit)
mydata_complete$no_free_bottles_dont_know <- factor(mydata_complete$no_free_bottles_dont_know)
mydata_complete$no_free_bottles_use_tap <- factor(mydata_complete$no_free_bottles_use_tap)
mydata_complete$no_free_bottles_other <- factor(mydata_complete$no_free_bottles_other)
mydata_complete$drink_tap_in_three_years <- factor(mydata_complete$drink_tap_in_three_years, levels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"), ordered = TRUE)
mydata_complete$bottle_site <- factor(mydata_complete$bottle_site)

imp <- mice(mydata_complete, maxit = 0)

predM <- imp$predictorMatrix
meth <- imp$method

set.seed(217)
imp2 <- mice(mydata_complete, m = 25, print = FALSE)
```

Now we create derived variables:
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache = TRUE}
imp_long <- mice::complete(imp2, action="long", include = TRUE)
imp_long$zip2 <- case_when(
  imp_long$current_zip=="48502" | imp_long$current_zip=="48503" ~ "48502/48503",
  imp_long$current_zip=="48504" ~ "48504",
  imp_long$current_zip=="48505" ~ "48505",
  imp_long$current_zip=="48506" ~ "48506",
  imp_long$current_zip=="48507" | imp_long$current_zip=="48532" ~ "48507/48532"
)

imp_long$educ_level2 <- case_when(
  imp_long$educ_level=="Less than a high school diploma" | imp_long$educ_level=="High school degree or equivalent (e.g. GED)" ~ "High school or less",
  imp_long$educ_level=="Some college, no degree" ~ "Some college",
  imp_long$educ_level=="Associate degree" | imp_long$educ_level=="Bachelor's degree" | imp_long$educ_level=="Master's, Doctoral or Professional degree" ~ "Associate's or more"
)

imp_long$public_benefits2 <- ifelse(imp_long$public_benefits=="Yes", "Yes", "No")
imp_long$gender2 <- ifelse(imp_long$gender=="Transgender Woman", "Female", imp_long$gender)

imp_long$marital_status2 <- case_when(
  imp_long$marital_status=="Single (never married)" ~ "Single (never married)",
  imp_long$marital_status=="Married" ~ "Married", 
  imp_long$marital_status=="Separated" | imp_long$marital_status=="Divorced" | imp_long$marital_status=="Widowed" ~ "Separated"
)

imp_long$employ_status2 <- case_when(
  imp_long$employ_status=="Jobs/sporadic" | imp_long$employ_status=="Other" ~ "Other",
  imp_long$employ_status=="Retired" ~ "Retired",
  imp_long$employ_status=="Employed" ~ "Employed",
  imp_long$employ_status=="Unemployed" ~ "Unemployed",
  is.na(imp_long$employ_status) ~ NA_character_)

imp_long$reth2 <- case_when(
  imp_long$reth=="Black" ~ "Black",
  imp_long$reth=="White" ~ "White",
  imp_long$reth=="Mixed Race" | imp_long$reth=="American Indian" | imp_long$reth=="Other race" | imp_long$reth=="Asian" | imp_long$reth=="Hispanic/Latinx" ~ "Other"
)

imp_long$current_housing2 <- case_when(
  imp_long$current_housing=="You own a home" ~ "Owned home",
  imp_long$current_housing=="You rent a home" ~ "Rented home",
  imp_long$current_housing=="You are staying with family or a friend" | imp_long$current_housing=="You are at a shelter" | imp_long$current_housing=="You are crashing/couch-surfing somewhere" | imp_long$current_housing=="You are on the streets" ~ "Unstable housing",
  imp_long$current_housing=="You are at a retirement facility" | imp_long$current_housing=="You are in an in-patient setting (e.g., rehab)" | imp_long$current_housing=="Other" ~ "Other housing"
)

imp_long$have_health_insurance2 <- ifelse(imp_long$have_health_insurance=="Unsure/Don't know", "No", imp_long$have_health_insurance)

imp_long$water_source2 <- ifelse(imp_long$water_source=="Tap water through the City of Flint (Water Department etc.)", "Tap water through the City of Flint", "Other")

imp_long$current_water_source2 <- case_when(
  imp_long$current_water_source=="Bottled water" | imp_long$current_water_source=="I don't drink any water at home" ~ "Bottled water",
  imp_long$current_water_source=="Tap water (with a filter)" | imp_long$current_water_source=="Water from a filtration system" ~ "Filtered tap water",
  imp_long$current_water_source=="Tap water (without a filter)" ~ "Unfiltered tap water"
)

imp_long$zip2 <- with(imp_long, factor(imp_long$zip2))
imp_long$educ_level2 <- with(imp_long, factor(imp_long$educ_level2, levels = c("High school or less", "Some college", "Associate's or more")))
imp_long$public_benefits2 <- with(imp_long, factor(imp_long$public_benefits2))
imp_long$marital_status2 <- with(imp_long, factor(imp_long$marital_status2))
imp_long$employ_status2 <- with(imp_long, factor(imp_long$employ_status2))
imp_long$reth2 <- with(imp_long, factor(imp_long$reth2))
imp_long$current_housing2 <- with(imp_long, factor(imp_long$current_housing2, levels = c("Owned home", "Rented home", "Unstable housing", "Other housing")))
imp_long$have_health_insurance2 <- with(imp_long, factor(imp_long$have_health_insurance2))
imp_long$water_source2 <- with(imp_long, factor(imp_long$water_source2, levels = c("Tap water through the City of Flint", "Other")))
imp_long$current_water_source2 <- with(imp_long, factor(imp_long$current_water_source2, levels = c("Unfiltered tap water", "Filtered tap water", "Bottled water"), ordered = TRUE))

var_label(imp_long$age) <- "Age"
var_label(imp_long$gender2) <- "Gender"
var_label(imp_long$reth2) <- "Race"
var_label(imp_long$educ_level2) <- "Education"
var_label(imp_long$public_benefits) <- "Public benefits status"
var_label(imp_long$employ_status2) <- "Employment status"
var_label(imp_long$marital_status2) <- "Marital status"
var_label(imp_long$years_cityflint) <- "Years lived in Flint"
var_label(imp_long$current_housing2) <- "Housing situation"
var_label(imp_long$zip2) <- "Zipcode"
var_label(imp_long$have_health_insurance2) <- "Health insurance"
var_label(imp_long$access_vehicle) <- "Vehicle access"
var_label(imp_long$water_source2) <- "Home water source"
var_label(imp_long$num_time_notice) <- "Months to notice a problem"
var_label(imp_long$watertestnum) <- "Number of water lead tests"
var_label(imp_long$water_test_surv) <- "Months from water switch to last water test"
var_label(imp_long$collapse_last_test) <- "Last water test result"
var_label(imp_long$blood_test_after_april_2014) <- "Got blood lead test after April 2014"
var_label(imp_long$blood_test_before_april_2014) <- "Got blood lead test before April 2014"
var_label(imp_long$elevated_lead_after_april_2014) <- "Diagnosed with elevated blood lead after April 2014"
var_label(imp_long$current_water_source2) <- "Current drinking water source"
var_label(imp_long$bottled_water_drink) <- "Uses bottled water to drink"
var_label(imp_long$bottled_water_cook) <- "Uses bottled water to cook"
var_label(imp_long$bottled_water_bathe) <- "Uses bottled water to bathe"
var_label(imp_long$bottled_water_teeth) <- "Uses bottled water to brush teeth"
var_label(imp_long$bottled_water_cleaning) <- "Uses bottled water to clean"
var_label(imp_long$bottled_water_other) <- "Uses bottled water for another purpose"
var_label(imp_long$num_bottles_per_day) <- "Number of standard (16.9 oz.) bottles of water used per day"
var_label(imp_long$number_children) <- "Number of children in care"
var_label(imp_long$water_bottle_disposal) <- "Disposal method for bottled water"
var_label(imp_long$water_line_status_after_april2014) <- "Current status of water line"
var_label(imp_long$water_line_surv) <- "Months from water switch to water line replacement"
var_label(imp_long$used_water_pod) <- "Ever used water pod (free bottled water)"
var_label(imp_long$get_free_bottled_water) <- "Currently uses water pod (free bottled water)"
var_label(imp_long$no_free_bottles_dont_know) <- "Didn't use water pods because didn't know about them"
var_label(imp_long$no_free_bottles_supply_limit) <- "Didn't use water pods because of supply limits"
var_label(imp_long$no_free_bottles_too_far) <- "Didn't use water pods because too far away"
var_label(imp_long$no_free_bottles_no_transport) <- "Didn't use water pods because of lack of transportation"
var_label(imp_long$no_free_bottles_bad_hours) <- "Didn't use water pods because they had bad hours"
var_label(imp_long$no_free_bottles_long_lines) <- "Didn't use water pods because of long lines"
var_label(imp_long$no_free_bottles_use_tap) <- "Didn't use water pods because I used my tap water"
var_label(imp_long$no_free_bottles_other) <- "Didn't use water pods for some other reason"
var_label(imp_long$bottle_site) <- "Water pod site"
var_label(imp_long$drink_tap_in_three_years) <- "Are you likely to drink the tap water in three years (~June 2022)?"
var_label(imp_long$confidants2) <- "Network size"
var_label(imp_long$bllpost2014_child) <- "Number of children with elevated BLLs"
var_label(imp_long$testpost2014_child) <- "Number of children tested for lead post-2014"
var_label(imp_long$bottledwater_child) <- "Number of children drinking bottled water"

imp_long_mids<-as.mids(imp_long)
```

Now we get our descriptives:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
table_predictors <- CreateTableOne(vars=c("age", "gender2", "educ_level2","marital_status2", "public_benefits", "have_health_insurance2", "employ_status2","years_cityflint","current_housing2","zip2","access_vehicle","water_source2","number_children","confidants2"), strata = "reth2", data=filter(imp_long, .imp==0), includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

test3 <- print(table_predictors, contDigits=1, varLabel = T, printToggle=FALSE)
test3["Age (mean (SD))", "p"] <- round(kruskal.test(age ~ reth2, data = filter(imp_long, .imp==0))$p.value, digits = 2)
test3["Years lived in Flint (mean (SD))", "p"] <- round(kruskal.test(years_cityflint ~ reth2, data = filter(imp_long, .imp==0))$p.value, digits = 2)
test3["Number of children in care (mean (SD))", "p"] <- round(kruskal.test(number_children ~ reth2, data = filter(imp_long, .imp==0))$p.value, digits = 2)
test3["Network size (mean (SD))", "p"] <- round(kruskal.test(confidants2 ~ reth2, data = filter(imp_long, .imp==0))$p.value, digits = 2)

table_outcomes <- CreateTableOne(vars=c("num_time_notice","watertestnum","water_test_surv", "collapse_last_test", "blood_test_after_april_2014","elevated_lead_after_april_2014","current_water_source2","used_water_pod","get_free_bottled_water","bottle_site","bottled_water_drink","bottled_water_cook","bottled_water_bathe","bottled_water_teeth","bottled_water_cleaning","bottled_water_other", "num_bottles_per_day","water_bottle_disposal","no_free_bottles_dont_know","no_free_bottles_supply_limit","no_free_bottles_too_far","no_free_bottles_no_transport","no_free_bottles_bad_hours","no_free_bottles_long_lines","no_free_bottles_use_tap","no_free_bottles_other","water_line_status_after_april2014","water_line_surv", "drink_tap_in_three_years"), strata = "reth2", data=filter(imp_long, .imp==0), includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))

table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender2", "educ_level2","marital_status2", "public_benefits", "have_health_insurance2", "employ_status2","years_cityflint","current_housing2","zip2","access_vehicle","water_source2","number_children","confidants2"), data=filter(imp_long, .imp==0), argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)

table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice","watertestnum","water_test_surv", "collapse_last_test", "blood_test_after_april_2014","elevated_lead_after_april_2014","current_water_source2","used_water_pod","get_free_bottled_water","bottle_site","bottled_water_drink","bottled_water_cook","bottled_water_bathe","bottled_water_teeth","bottled_water_cleaning","bottled_water_other", "num_bottles_per_day","water_bottle_disposal","no_free_bottles_dont_know","no_free_bottles_supply_limit","no_free_bottles_too_far","no_free_bottles_no_transport","no_free_bottles_bad_hours","no_free_bottles_long_lines","no_free_bottles_use_tap","no_free_bottles_other","water_line_status_after_april2014","water_line_surv", "drink_tap_in_three_years"), data=filter(imp_long, .imp==0), argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)

test <- print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE)
test2 <- print(table_outcomes_notstrat, contDigits=1, varLabel = T, printToggle=FALSE)

test["Months to notice a problem (mean (SD))", "p"] <- round(kruskal.test(num_time_notice ~ reth2, data = filter(imp_long, .imp==0))$p.value, digits = 2)
test["Number of water lead tests (mean (SD))", "p"] <- round(kruskal.test(watertestnum ~ reth2, data = filter(imp_long, .imp==0))$p.value, digits = 2)

km_waterline <- survfit(Surv(water_line_surv, as.numeric(waterline_replaced_eventind)-1) ~ 1, data = filter(imp_long, .imp==0, waterline_cured_ind==0))
print(km_waterline)
km_waterline_reth <- survfit(Surv(water_line_surv, as.numeric(waterline_replaced_eventind)-1) ~ reth2, data = filter(imp_long, .imp==0, waterline_cured_ind==0), conf.type = "log-log")
print(km_waterline_reth)

waterline_reth <- c("55 (53, 58)", "53 (46, 64)", "54 (49, 56)")
waterline_overall <- "54 (53, 56)"

testresults <- survdiff(Surv(water_line_surv, as.numeric(waterline_replaced_eventind)-1) ~ reth2, data = filter(imp_long, .imp==0, waterline_cured_ind==0))

test["Months from water switch to water line replacement (mean (SD))", c("Black", "Other", "White")] <- waterline_reth
test2["Months from water switch to water line replacement (mean (SD))", "Overall"] <- waterline_overall
test["Months from water switch to water line replacement (mean (SD))", "p"] <- round(dchisq(testresults$chisq, df = 2)*2, digits = 2)

km_watertest <- survfit(Surv(water_test_surv, as.numeric(water_test_event_ind)-1) ~ 1, data = filter(imp_long, .imp==0), conf.type = "log-log")
print(km_watertest)
km_watertest_reth <- survfit(Surv(water_test_surv, as.numeric(water_test_event_ind)-1) ~ reth2, data = filter(imp_long, .imp==0), conf.type = "log-log")
print(km_watertest_reth)

watertest_reth <- c("53 (53, 58)", "62 (57, 64)", "55 (53, 62)")
watertest_overall <- "56 (53, 59)"

test["Months from water switch to last water test (mean (SD))", c("Black", "Other", "White")] <- watertest_reth
test2["Months from water switch to last water test (mean (SD))", "Overall"] <- watertest_overall
test["Months from water switch to last water test (mean (SD))", "p"] <- round(dchisq(survdiff(Surv(water_test_surv, as.numeric(water_test_event_ind)-1) ~ reth2, data = filter(imp_long, .imp==0))$chisq, df = 2)*2, digits = 2)

subdat <- filter(imp_long, .imp==0)
medians <- c(median(subdat$num_time_notice[subdat$reth2=="Black"], na.rm = TRUE), median(subdat$num_time_notice[subdat$reth2=="Other"], na.rm = TRUE), median(subdat$num_time_notice[subdat$reth2=="White"], na.rm = TRUE))
mins <- c(min(subdat$num_time_notice[subdat$reth2=="Black"], na.rm = TRUE), min(subdat$num_time_notice[subdat$reth2=="Other"], na.rm = TRUE), min(subdat$num_time_notice[subdat$reth2=="White"], na.rm = TRUE))
maxs <- c(max(subdat$num_time_notice[subdat$reth2=="Black"], na.rm = TRUE), max(subdat$num_time_notice[subdat$reth2=="Other"], na.rm = TRUE), max(subdat$num_time_notice[subdat$reth2=="White"], na.rm = TRUE))

test["Months to notice a problem (mean (SD))", c("Black", "Other", "White")] <- paste0(round(medians, digits = 1), " (", round(mins, digits = 1), ", ", round(maxs, digits = 1), ")")

test2["Months to notice a problem (mean (SD))", "Overall"] <- paste0(round(median(subdat$num_time_notice, na.rm = TRUE), digits = 1), " (", round(min(subdat$num_time_notice, na.rm = TRUE), digits = 1), ", ", round(max(subdat$num_time_notice, na.rm = TRUE), digits = 1), ")")

kable(test3, booktabs=T) %>% add_indent(c(5:7, 9:11, 13:15, 18:22, 25:28, 30:34, 37:39)) %>% kable_styling(position="center")

kable(print(table_predictors_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(5:7, 9:11, 13:15, 18:22, 25:28, 30:34, 37:39)) %>% kable_styling(position="center")

kable(test, booktabs=T) %>% add_indent(c(6:10, 12:15, 17:20, 22:25, 28:30, 32:47, 56:60, 70:77, 80:85)) %>% kable_styling(position="center")

kable(test2, booktabs=T) %>% add_indent(c(6:10, 12:15, 17:20, 22:25, 28:30, 32:47, 56:60, 70:77, 80:85)) %>% kable_styling(position="center")
```

We generate some figures:
```{r, echo=FALSE, message=FALSE, warning=FALSE, eval = TRUE}
imp_long$watertestbinary <- as.numeric(imp_long$watertestnum > 0)
imp_long$watertestbinary[is.na(imp_long$watertestbinary)] <- 2
imp_long$watertestbinary <- factor(imp_long$watertestbinary, levels=c(1, 0, 2), labels=c("Yes", "No", "Missing"), ordered = TRUE)
imp_long$collapse_last_testmis <- case_when(
  imp_long$collapse_last_test=="Acceptable levels of lead" ~ "Safe",
  imp_long$collapse_last_test=="Unsure if tested" | is.na(imp_long$collapse_last_test)~ "Missing",
  imp_long$collapse_last_test=="Not tested" ~ "Not \ntested",
  imp_long$collapse_last_test=="Unsafe levels of lead" ~ "Unsafe"
)

imp_long$collapse_last_testmis <- factor(imp_long$collapse_last_testmis, levels=c("Safe", "Unsafe", "Not \ntested", "Missing"), ordered = TRUE)

imp_long$blood_test_after_april_2014mis <- case_when(
  imp_long$blood_test_after_april_2014=="Yes" ~ "Yes",
  imp_long$blood_test_after_april_2014=="No" ~ "No",
  imp_long$blood_test_after_april_2014=="Unsure" | is.na(imp_long$blood_test_after_april_2014) ~ "Missing"
)

imp_long$elevated_lead_after_april_2014mis <- case_when(
  imp_long$elevated_lead_after_april_2014=="Yes" ~ "Yes",
  imp_long$elevated_lead_after_april_2014=="No" ~ "No",
  imp_long$elevated_lead_after_april_2014=="Unsure" | is.na(imp_long$elevated_lead_after_april_2014) ~ "Missing"
)

alluvial_dat1 <- filter(imp_long, .imp==0) %>% dplyr::select(watertestbinary, collapse_last_testmis, blood_test_after_april_2014mis, elevated_lead_after_april_2014mis) %>% count(watertestbinary, collapse_last_testmis, blood_test_after_april_2014mis, elevated_lead_after_april_2014mis) %>% rename(Freq = n)

ggplot(alluvial_dat1, aes(y = Freq, axis1 = watertestbinary, axis2 = blood_test_after_april_2014mis, axis3 = elevated_lead_after_april_2014mis, axis4 = collapse_last_testmis)) + geom_alluvium(aes(fill = watertestbinary)) + geom_stratum(width = 1/3) + geom_text(stat = "stratum", aes(label = after_stat(stratum))) + scale_x_continuous(breaks = 1:4, labels = c("Had water test", "Had blood test", "Elevated BLLs", "Last water test result")) + theme_bw() + theme(legend.position = "none") + scale_fill_manual(values = c("mediumpurple4", "darkred", "gray74")) + ylab("Number of Respondents") + ggtitle("Participation in Testing")

alluvial_dat2 <- filter(imp_long, .imp==0, bottled_water_drink=="Yes") %>% dplyr::select(bottled_water_cook, bottled_water_bathe, bottled_water_teeth, bottled_water_cleaning, bottled_water_other) %>% count(bottled_water_cook, bottled_water_bathe, bottled_water_teeth, bottled_water_cleaning, bottled_water_other) %>% rename(Freq = n)

ggplot(alluvial_dat2, aes(y = Freq, axis1 = bottled_water_cook, axis2 = bottled_water_bathe, axis3 = bottled_water_teeth, axis4 = bottled_water_cleaning, axis5 = bottled_water_other)) + geom_alluvium(aes(fill = bottled_water_cook)) + geom_stratum(width = 1/8) + geom_text(stat = "stratum", aes(label = after_stat(stratum))) + scale_x_continuous(breaks = 1:5, labels = c("Cooking", "Bathing", "Toothbrushing", "Cleaning", "Other use")) + theme_bw() + theme(legend.position = "none") + scale_fill_manual(values = c("mediumpurple4", "darkred")) + ylab("Number of Respondents") + ggtitle("Bottled Water Uses in Addition to Drinking")

alluvial_dat3 <- filter(imp_long, .imp==0, get_free_bottled_water=="No") %>% dplyr::select(no_free_bottles_dont_know, no_free_bottles_supply_limit, no_free_bottles_too_far, no_free_bottles_no_transport, no_free_bottles_bad_hours, no_free_bottles_long_lines, no_free_bottles_use_tap, no_free_bottles_other) %>% count(no_free_bottles_dont_know, no_free_bottles_supply_limit, no_free_bottles_too_far, no_free_bottles_no_transport, no_free_bottles_bad_hours, no_free_bottles_long_lines, no_free_bottles_use_tap, no_free_bottles_other) %>% rename(Freq = n)

ggplot(alluvial_dat3, aes(y = Freq, axis1 = no_free_bottles_dont_know, axis2 = no_free_bottles_supply_limit, axis3 = no_free_bottles_too_far, axis4 = no_free_bottles_no_transport, axis5 = no_free_bottles_bad_hours, axis6 = no_free_bottles_long_lines, axis7 = no_free_bottles_use_tap, axis8 = no_free_bottles_other)) + geom_alluvium(aes(fill = no_free_bottles_dont_know)) + geom_stratum(width = 1/8) + geom_text(stat = "stratum", aes(label = after_stat(stratum))) + scale_x_continuous(breaks = 1:8, labels = c("Didn't know", "Supply limit", "Too far", "No transportation", "Bad hours", "Long lines", "Use tap instead", "Other reason")) + theme_bw() + theme(legend.position = "none", axis.text.x = element_text(angle=45, vjust = 0.5)) + scale_fill_manual(values = c("mediumpurple4", "darkred")) + ylab("Number of Respondents") + ggtitle("Reasons for Not Currently Using Water Pods")

timingdat <- data.frame("Date" = c(mydata$notice_date, mydata$last_test_date, mydata$waterline_date), "Type" = rep(c("Noticed water issue", "Last water test", "Waterline replaced"), each = nrow(mydata)))

timingdat$Type <- factor(timingdat$Type, levels=c("Noticed water issue", "Last water test", "Waterline replaced"), ordered = TRUE)

ggplot(timingdat, aes(x = Date, fill = Type, color = Type)) + geom_histogram(position = "dodge") + ylab("Number of Respondents") + theme_bw() + scale_fill_manual(values = c("mediumpurple4", "gray74", "darkred")) + scale_color_manual(values = c("mediumpurple4", "gray74", "darkred")) + ggtitle("Timing of Water Crisis Response") #+ coord_cartesian(ylim = c(0, 60))
```

We do the modeling:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
effect_estims <- data.frame("Outcome" = NA, "Predictor" = NA, "Estimate" = NA, "SE" = NA, "Pval" = NA)

time_to_notice <- with(imp_long_mids, lm(log(num_time_notice) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + water_source2 + access_vehicle + number_children + confidants2))

summary(pool(time_to_notice))

subdat <- data.frame("Outcome" = rep("Time to notice", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(time_to_notice))$estimate[-1], "SE" = summary(pool(time_to_notice))$std.error[-1], "Pval" = summary(pool(time_to_notice))$p.value[-1])

effect_estims <- rbind(effect_estims, subdat)

number_water_tests <- with(imp_long_mids, lm(log(watertestnum + 0.1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2))

summary(pool(number_water_tests))

subdat <- data.frame("Outcome" = rep("Number of water tests", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(number_water_tests))$estimate[-1], "SE" = summary(pool(number_water_tests))$std.error[-1], "Pval" = summary(pool(number_water_tests))$p.value[-1])

effect_estims <- rbind(effect_estims, subdat)

last_water_test_time <- with(imp_long_mids, coxph(Surv(water_test_surv, as.numeric(water_test_event_ind)-1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2))

summary(pool(last_water_test_time))

subdat <- data.frame("Outcome" = rep("Time to last water test", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(last_water_test_time))$estimate, "SE" = summary(pool(last_water_test_time))$std.error, "Pval" = summary(pool(last_water_test_time))$p.value)

effect_estims <- rbind(effect_estims, subdat)

last_test_result <- with(imp_long_mids, glm(as.numeric(collapse_last_test=="Acceptable levels of lead") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial"))

summary(pool(last_test_result))

subdat <- data.frame("Outcome" = rep("Last water test result", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(last_test_result))$estimate[-1], "SE" = summary(pool(last_test_result))$std.error[-1], "Pval" = summary(pool(last_test_result))$p.value[-1])

effect_estims <- rbind(effect_estims, subdat)

blood_test <- with(imp_long_mids, glm(as.numeric(blood_test_after_april_2014=="Yes") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial"))

summary(pool(blood_test))

subdat <- data.frame("Outcome" = rep("Blood test", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(blood_test))$estimate[-1], "SE" = summary(pool(blood_test))$std.error[-1], "Pval" = summary(pool(blood_test))$p.value[-1])

effect_estims <- rbind(effect_estims, subdat)

## This model could not be fit because of small sample sizes.
#elev_blls <- with(imp_long_mids, glm(as.numeric(elevated_lead_after_april_2014=="Yes") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + water_source2 + number_children + confidants2, family = "binomial"))

#summary(pool(elev_blls))

#subdat <- data.frame("Outcome" = rep("Elevated BLLs", 18), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Other water source (ref: Flint tap water)", "Number of children", "Network size"), "Estimate" = summary(pool(elev_blls))$estimate[-1], "SE" = summary(pool(elev_blls))$std.error[-1], "Pval" = summary(pool(elev_blls))$p.value[-1])

#effect_estims <- rbind(effect_estims, subdat)

currentwatersource <- with(imp_long_mids, polr(current_water_source2 ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, Hess = TRUE))

summary(pool(currentwatersource))

subdat <- data.frame("Outcome" = rep("Current drinking water source", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(currentwatersource))$estimate[1:22], "SE" = summary(pool(currentwatersource))$std.error[1:22], "Pval" = NA)

effect_estims <- rbind(effect_estims, subdat)

water_pod_past <- with(imp_long_mids, glm(used_water_pod ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial"))

summary(pool(water_pod_past))

subdat <- data.frame("Outcome" = rep("Used water pod in the past", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(water_pod_past))$estimate[-1], "SE" = summary(pool(water_pod_past))$std.error[-1], "Pval" = summary(pool(water_pod_past))$p.value[-1])

effect_estims <- rbind(effect_estims, subdat)

water_pod_now <- with(imp_long_mids, glm(get_free_bottled_water ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial"))

summary(pool(water_pod_now))

subdat <- data.frame("Outcome" = rep("Use water pod now", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(water_pod_now))$estimate[-1], "SE" = summary(pool(water_pod_now))$std.error[-1], "Pval" = summary(pool(water_pod_now))$p.value[-1])

effect_estims <- rbind(effect_estims, subdat)

number_bottles <- with(imp_long_mids, glm(num_bottles_per_day ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "quasipoisson"))

summary(pool(number_bottles))

subdat <- data.frame("Outcome" = rep("Number of bottles per day", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(number_bottles))$estimate[-1], "SE" = summary(pool(number_bottles))$std.error[-1], "Pval" = summary(pool(number_bottles))$p.value[-1])

effect_estims <- rbind(effect_estims, subdat)

recycle_bottles <- with(imp_long_mids, glm(as.numeric(water_bottle_disposal=="I don't ever have plastic water bottles at home" | water_bottle_disposal=="Keep/save them for re-use or another purpose" | water_bottle_disposal=="Recycle them") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial"))

summary(pool(recycle_bottles))

subdat <- data.frame("Outcome" = rep("Bottle disposal", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(recycle_bottles))$estimate[-1], "SE" = summary(pool(recycle_bottles))$std.error[-1], "Pval" = summary(pool(recycle_bottles))$p.value[-1])

effect_estims <- rbind(effect_estims, subdat)

waterlinestatus <- with(imp_long_mids, glm(as.numeric(water_line_status_after_april2014=="A mailing or official said that my lead/water line did not need to be replaced" | water_line_status_after_april2014=="I was offered a lead/water line replacement but I refused it" | water_line_status_after_april2014=="My lead/water lines were replaced") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial"))

summary(pool(waterlinestatus))

subdat <- data.frame("Outcome" = rep("Water line status", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(waterlinestatus))$estimate[-1], "SE" = summary(pool(waterlinestatus))$std.error[-1], "Pval" = summary(pool(waterlinestatus))$p.value[-1])

effect_estims <- rbind(effect_estims, subdat)

water_line_time <- with(imp_long_mids, coxph(Surv(water_line_surv, as.numeric(waterline_replaced_eventind)-1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2))

summary(pool(water_line_time))

subdat <- data.frame("Outcome" = rep("Time to water line replacement", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(water_line_time))$estimate, "SE" = summary(pool(water_line_time))$std.error, "Pval" = summary(pool(water_line_time))$p.value)

effect_estims <- rbind(effect_estims, subdat)

drinktap <- with(imp_long_mids, polr(drink_tap_in_three_years ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, Hess = TRUE))

summary(pool(drinktap))

subdat <- data.frame("Outcome" = rep("Likely to drink tap in three years?", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(drinktap))$estimate[1:22], "SE" = summary(pool(drinktap))$std.error[1:22], "Pval" = NA)

effect_estims <- rbind(effect_estims, subdat)

#child_test <- with(imp_long_mids, glm(testpost2014_child ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + confidants2 + factor(blood_test_after_april_2014, ordered = FALSE) + offset(number_children), family = "quasipoisson"))

#summary(pool(child_test))

#subdat <- data.frame("Outcome" = rep("Got child tested", 23), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Network size", "Adult not tested (ref: Adult tested)", "Adult unsure if tested (ref: Adult tested)"), "Estimate" = summary(pool(child_test))$estimate[-1], "SE" = summary(pool(child_test))$std.error[-1], "Pval" = summary(pool(child_test))$p.value[-1])

#effect_estims <- rbind(effect_estims, subdat)

##This model not included because of stability issues:

#child_bll <- with(imp_long_mids, glm(bllpost2014_child ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + confidants2 + as.numeric(elevated_lead_after_april_2014=="Yes") + offset(number_children), family = "quasipoisson"))

#summary(pool(child_bll))

#subdat <- data.frame("Outcome" = rep("Child had elevated BLLs", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Network size", "Adult has elevated BLLs (ref: Adult has normal/unsure BLLs)"), "Estimate" = summary(pool(child_bll))$estimate[-1], "SE" = summary(pool(child_bll))$std.error[-1], "Pval" = summary(pool(child_bll))$p.value[-1])

#effect_estims <- rbind(effect_estims, subdat)

#child_bottled <- with(imp_long_mids, glm(bottledwater_child ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + confidants2 + factor(current_water_source2, ordered = FALSE) + offset(number_children), family = "quasipoisson"))

#summary(pool(child_bottled))

#subdat <- data.frame("Outcome" = rep("Child uses bottled water", 23), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Network size", "Adult uses filtered tap water (ref: Adult uses unfiltered water)", "Adult uses bottled water (ref: Adult uses unfiltered water)"), "Estimate" = summary(pool(child_bottled))$estimate[-1], "SE" = summary(pool(child_bottled))$std.error[-1], "Pval" = summary(pool(child_bottled))$p.value[-1])

#effect_estims <- rbind(effect_estims, subdat)
```

Since we fit quite a few models, we use the FDR to adjust for our multiple testing.
```{r, echo=FALSE, message=FALSE, warning=FALSE, eval = TRUE}
effect_estims <- effect_estims[-1,]
effect_estims$Pval[is.na(effect_estims$Pval)] <- 2*pnorm(abs(effect_estims$Estimate[is.na(effect_estims$Pval)]/effect_estims$SE[is.na(effect_estims$Pval)]), lower.tail = FALSE)
effect_estims$Lower <- effect_estims$Estimate - 1.96*effect_estims$SE
effect_estims$Upper <- effect_estims$Estimate + 1.96*effect_estims$SE

pretty_effects <- data.frame("Outcome" = effect_estims$Outcome, "Predictor" = effect_estims$Predictor, "Estimate" = exp(effect_estims$Estimate), "Lower" = exp(effect_estims$Lower), "Upper" = exp(effect_estims$Upper), "BHpvalue" = round(p.adjust(effect_estims$Pval, method="BH"), digits = 2))

pretty_effects$Label <- paste0(round(pretty_effects$Estimate, digits = 1), " (", round(pretty_effects$Lower, digits = 1), ", ", round(pretty_effects$Upper, digits = 1), ")")

pretty_effects2 <- dplyr::select(pretty_effects, Outcome, Predictor, Label, BHpvalue)

pretty_effects2[pretty_effects2$BHpvalue <= 0.05,]
```

```

### 2021-10-05 papertwo_child_health.Rmd
Update to include analysis for health behavior paper, and to revise child health analysis using Bayesian models.

@@
 author: "Elizabeth Chase"
-date: "5/10/2021"
+date: "10/5/2021"
 output: pdf_document
@@
 library(lme4)
+library(rstanarm)
 
@@
 
-subadult <- mutate(adult_clean_eliz, parbloodtestf = blood_test_after_april_2014, parbllf = elevated_lead_after_april_2014, parrashesf = rashes_after_april_2014, parhairf = hairloss_after_april_2014, parnausf = nausea_after_april_2014, parirrf = irritable_after_april_2014, parbloodtestc = getscreened, parbllc = elevated_collapse, parrashesc = rash_collapse, parhairc = hair_collapse, parnausc = nausea_collapse, parirrc = irritable_collapse, paroverall = overall_collapse) %>% select(inclusion, unique_id, age, gender, collapserace, collapseeduc, have_health_insurance, public_benefits, water_exaggerated, children_health_harmed, trust_government_in_future, drink_tap_in_three_years, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, political_affiliation, nightmares, avoided_thinking_crisis, onguard_watchful, numb_detached, felt_guilty, ptsdscore, phq, parbloodtestf, parbllf, parrashesf, parhairf, parnausf, parirrf, parbloodtestc, parbllc, parrashesc, parhairc, parnausc, parirrc, paroverall, confidants2, number_children, employ_status, num_time_notice, watertestbinary, current_zip, waterlinereplaced)
+subadult <- mutate(adult_clean_eliz, parbloodtestf = blood_test_after_april_2014, parbllf = elevated_lead_after_april_2014, parrashesf = rashes_after_april_2014, parhairf = hairloss_after_april_2014, parnausf = nausea_after_april_2014, parirrf = irritable_after_april_2014, parbloodtestc = getscreened, parbllc = elevated_collapse, parrashesc = rash_collapse, parhairc = hair_collapse, parnausc = nausea_collapse, parirrc = irritable_collapse, paroverall = overall_collapse) %>% dplyr::select(inclusion, unique_id, age, gender, collapserace, collapseeduc, have_health_insurance, public_benefits, water_exaggerated, children_health_harmed, trust_government_in_future, drink_tap_in_three_years, satisfied_flint_government, satisfied_state_government, satisfied_federal_government, political_affiliation, nightmares, avoided_thinking_crisis, onguard_watchful, numb_detached, felt_guilty, ptsdscore, phq, parbloodtestf, parbllf, parrashesf, parhairf, parnausf, parirrf, parbloodtestc, parbllc, parrashesc, parhairc, parnausc, parirrc, paroverall, confidants2, number_children, employ_status, num_time_notice, watertestbinary, current_zip, waterlinereplaced)
 
@@
 
-#child_adult$gettested <- ifelse(child_adult$blood_test_after_april_2014=="Yes" & child_adult$blood_test_before_april_2014=="No", 1, ifelse(is.na(child_adult$blood_test_after_april_2014) | is.na(child_adult$blood_test_before_april_2014), NA_real_, 0))
-
 child_adult$gettested <- ifelse(child_adult$blood_test_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$blood_test_after_april_2014), NA_real_, 0))
-
-#child_adult$elevbll <- ifelse(child_adult$elevated_lead_after_april_2014=="Yes" & child_adult$elevated_lead_before_april_2014=="No", 1, ifelse(is.na(child_adult$elevated_lead_after_april_2014) | is.na(child_adult$elevated_lead_before_april_2014), NA_real_, 0))
 
@@
 
-#child_adult$rash <- ifelse(child_adult$rash_after_april_2014=="Yes" & child_adult$rash_before_april_2014=="No", 1, ifelse(is.na(child_adult$rash_after_april_2014) | is.na(child_adult$rash_before_april_2014), NA_real_, 0))
-
 child_adult$rash <- ifelse(child_adult$rash_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$rash_after_april_2014), NA_real_, 0))
-
-#child_adult$hair <- ifelse(child_adult$hairloss_after_april_2014=="Yes" & child_adult$hairloss_before_april_2014=="No", 1, ifelse(is.na(child_adult$hairloss_after_april_2014) | is.na(child_adult$hairloss_before_april_2014), NA_real_, 0))
 
@@
 
-#child_adult$learn <- ifelse(child_adult$learning_after_april_2014=="Yes" & child_adult$learning_before_april_2014=="No", 1, ifelse(is.na(child_adult$learning_after_april_2014) | is.na(child_adult$learning_before_april_2014), NA_real_, 0))
-
 child_adult$learn <- ifelse(child_adult$learning_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$learning_after_april_2014), NA_real_, 0))
 
-#child_adult$hyper <- ifelse(child_adult$hyper_after_april_2014=="Yes" & child_adult$hyper_before_april_2014=="No", 1, ifelse(is.na(child_adult$hyper_after_april_2014) | is.na(child_adult$hyper_before_april_2014), NA_real_, 0))
-
 child_adult$hyper <- ifelse(child_adult$hyper_after_april_2014=="Yes", 1, ifelse(is.na(child_adult$hyper_after_april_2014), NA_real_, 0))
-
-#child_adult$irritable <- ifelse(child_adult$irritable_after_april_2014=="Yes" & child_adult$irritable_before_april_2014=="No", 1, ifelse(is.na(child_adult$irritable_after_april_2014) | is.na(child_adult$irritable_before_april_2014), NA_real_, 0))
 
@@
 
-symp_sub <- select(child_adult, gettested, elevbll, rash, hair, learn, hyper, irritable)
+symp_sub <- dplyr::select(child_adult, gettested, elevbll, rash, hair, learn, hyper, irritable)
 
@@
 
-exam <- select(child_adult, child, unique_id, relationship, age.x, gender.x, public_benefits, gettested, elevbll, rash, hair, learn, hyper, irritable, overall_symp, racecollapse, blood_test_after_april_2014, water_exaggerated)
+exam <- dplyr::select(child_adult, child, unique_id, relationship, age.x, gender.x, public_benefits, gettested, elevbll, rash, hair, learn, hyper, irritable, overall_symp, racecollapse, blood_test_after_april_2014, water_exaggerated)
 
@@
 ## Introductory Remarks
+
+Note: May 2021
 
@@
 Therefore, I have concluded that our inclusion criteria will be children ages 6 months and up, considering outcomes based on just after April 2014 (and not before) described by any caregiver living in the City of Flint.
+
+Note: Oct. 2021
+
+This analysis was redone using Bayesian models, in order to meet a reviewer request for models that would not converge using REML.
+This allows us to address the issues with small sample size and separation in the data.
 
@@
 
-## Multivariable modeling results
+## Multivariable modeling results (normal priors)
 
@@
 
-##watersource_model <- glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ##issues with convergence; did not include
+watersource_model <- stan_glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id),
+                               data = child_adult, 
+                               family = "binomial", seed = 12)
 
-##summary(watersource_model)
+mysum <- summary(watersource_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+effects_mat <- data.frame("Outcome" = rep("Child drinks bottled water", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
 
 #For getting tested:
-tested_model_noadult <- glmer(gettested ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-tested_model_adult <- glmer(gettested ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = child_adult, family = "binomial")
+tested_model <- stan_glmer(gettested ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = child_adult, family = "binomial", seed = 13)
 
-summary(tested_model_noadult)
-summary(tested_model_adult)
+mysum <- summary(tested_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
 
-effects_mat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = c(summary(tested_model_noadult)$coefficients[-1,1], summary(tested_model_adult)$coefficients[7,1]), "StErr" = c(summary(tested_model_noadult)$coefficients[-1,2], summary(tested_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(tested_model_noadult)$coefficients[-1,4], summary(tested_model_adult)$coefficients[7,4]))
+mysum
 
-#For having elevated BLLs:
-#bll_model_noadult <- glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-#bll_model_adult <- glmer(elevbll ~ gender.x + scale(age.x) + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial") # Not included due to convergence issues
-
-#summary(bll_model_noadult)
-#summary(bll_model_adult)
-
-#subdat <- data.frame("Outcome" = rep("Elevated BLLs", 5), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits"), "Estimate" = c(summary(bll_model_noadult)$coefficients[-1,1]), "StErr" = c(summary(bll_model_noadult)$coefficients[-1,2]), "Pvalue" = c(summary(bll_model_noadult)$coefficients[-1,4]))
-
-#effects_mat <- rbind(effects_mat, subdat)
-
-#For having rashes:
-rash_model_noadult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-summary(rash_model_noadult)
-rash_model_adult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
-summary(rash_model_adult)
-
-subdat <- data.frame("Outcome" = rep("Rashes", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(rash_model_noadult)$coefficients[-1,1], summary(rash_model_adult)$coefficients[7,1]), "StErr" = c(summary(rash_model_noadult)$coefficients[-1,2], summary(rash_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(rash_model_noadult)$coefficients[-1,4], summary(rash_model_adult)$coefficients[7,4]))
+subdat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])
 
@@
 
-#For having hair loss:
-#hair_model_noadult <- glmer(hair ~ gender.x + scale(age.x) + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include
-#summary(hair_model_noadult)
-#hair_model_adult <- glmer(hair ~ gender.x + scale(age.x) + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include
-#summary(hair_model_adult)
+#For having elevated BLLs (restricting to children who were screened):
+bll_model <- stan_glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = filter(child_adult, gettested=="Yes"), family = "binomial", seed = 14)
 
-#subdat <- data.frame("Outcome" = rep("Hairloss", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(hair_model_noadult)$coefficients[-1,1], summary(hair_model_adult)$coefficients[7,1]), "StErr" = c(summary(hair_model_noadult)$coefficients[-1,2], summary(hair_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(hair_model_noadult)$coefficients[-1,4], summary(hair_model_adult)$coefficients[7,4]))
+mysum <- summary(bll_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
 
-#effects_mat <- rbind(effects_mat, subdat)
+mysum
+
+subdat <- data.frame("Outcome" = rep("Elevated BLLs", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])
+
+effects_mat <- rbind(effects_mat, subdat)
+
+#For having rashes:
+rash_model <- stan_glmer(rash ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested  + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 15)
+
+mysum <- summary(rash_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Rashes", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
+
+effects_mat <- rbind(effects_mat, subdat)
+
+#For having hair loss
+hair_model <- stan_glmer(hair ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 16)
+
+mysum <- summary(hair_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Hair loss", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
+
+effects_mat <- rbind(effects_mat, subdat)
 
 #For having learning delays:
-learn_model_noadult <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-summary(learn_model_noadult)
+learn_model <- stan_glmer(learn ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 17)
 
-learn_model_layer2 <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
-summary(learn_model_layer2)
+mysum <- summary(learn_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
 
-subdat <- data.frame("Outcome" = rep("Learning Delays", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(learn_model_noadult)$coefficients[-1,1], summary(learn_model_layer2)$coefficients[7,1]), "StErr" = c(summary(learn_model_noadult)$coefficients[-1,2], summary(learn_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(learn_model_noadult)$coefficients[-1,4], summary(learn_model_layer2)$coefficients[7,4]))
+mysum
+
+subdat <- data.frame("Outcome" = rep("Learning delays", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
 
@@
 #For having hyperactivity:
-hyper_model_noadult <- glmer(hyper ~ gender.x + scale(age.x) + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-summary(hyper_model_noadult)
+hyper_model <- stan_glmer(hyper ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 18)
 
-hyper_model_layer2 <- glmer(hyper ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
-summary(hyper_model_layer2)
+mysum <- summary(hyper_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
 
-subdat <- data.frame("Outcome" = rep("Hyperactivity", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(hyper_model_noadult)$coefficients[-1,1], summary(hyper_model_layer2)$coefficients[7,1]), "StErr" = c(summary(hyper_model_noadult)$coefficients[-1,2], summary(hyper_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(hyper_model_noadult)$coefficients[-1,4], summary(hyper_model_layer2)$coefficients[7,4]))
+mysum
+
+subdat <- data.frame("Outcome" = rep("Hyperactivity", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
 
@@
 #For having irritability:
-irr_model_noadult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-summary(irr_model_noadult)
-irr_model_adult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
-summary(irr_model_adult)
+irr_model <- stan_glmer(irritable ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 19)
 
-subdat <- data.frame("Outcome" = rep("Irritability", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(irr_model_noadult)$coefficients[-1,1], summary(irr_model_adult)$coefficients[7,1]), "StErr" = c(summary(irr_model_noadult)$coefficients[-1,2], summary(irr_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(irr_model_noadult)$coefficients[-1,4], summary(irr_model_adult)$coefficients[7,4]))
+mysum <- summary(irr_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Irritability", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
 
@@
 #For overall symptoms:
-overall_model_noadult <- lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult)
-summary(overall_model_noadult)
+overall_model <- stan_lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, seed = 20)
 
-overall_model_adult <- lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + water_exaggeratedbinary + (1 | unique_id), data = child_adult)
-summary(overall_model_adult)
+mysum <- summary(overall_model, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
 
-subdat <- data.frame("Outcome" = rep("Overall Symptoms", 7), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = c(summary(overall_model_noadult)$coefficients[-1,1], summary(overall_model_adult)$coefficients[7:8,1]), "StErr" = c(summary(overall_model_noadult)$coefficients[-1,2], summary(overall_model_adult)$coefficients[7:8,2]), "Pvalue" = pnorm(c(summary(overall_model_noadult)$coefficients[-1,3], summary(overall_model_adult)$coefficients[7:8,3]), lower.tail = FALSE))
+mysum
+
+subdat <- data.frame("Outcome" = rep("Total Symptoms", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
 
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-effects_mat$BHpvalue <- p.adjust(effects_mat$Pvalue, method="BH")
 
 effects_mat$lower <- case_when(
-  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate - 1.96*effects_mat$StErr,
-  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate - 1.96*effects_mat$StErr)
+  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Lower,
+  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Lower)
 )
@@
 effects_mat$upper <- case_when(
-  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate + 1.96*effects_mat$StErr,
-  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate + 1.96*effects_mat$StErr)
+  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Upper,
+  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Upper)
 )
 
-effects_mat$effect <- case_when(
+effects_mat$estimate <- case_when(
   effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate,
@@
 
-effects_mat$label <- paste0(round(effects_mat$effect, digits=1), " (", round(effects_mat$lower, digits = 1), ", ", round(effects_mat$upper, digits = 1), ")")
+effects_mat$label <- paste0(round(effects_mat$estimate, digits=1), " (", round(effects_mat$lower, digits = 1), ", ", round(effects_mat$upper, digits = 1), ")")
 
-pretty_effects <- select(effects_mat, Outcome, Variable, label, BHpvalue)
-pretty_effects$BHpvalue <- round(pretty_effects$BHpvalue, 3)
+pretty_effects <- dplyr::select(effects_mat, Outcome, Variable, label)
 rownames(pretty_effects) <- NULL
 
-kable(pretty_effects, col.names = c("Outcome", "Predictor", "Odds Ratio (95% CI)", "P-value"))
+kable(pretty_effects, col.names = c("Outcome", "Predictor", "Odds Ratio (95% CI)"))
 ```
 
-Note that these modeling results doesn't include one important outcomes: child water source.
-I was unable to get this model to fit stably because of the small number of children not drinking bottled water.
-In addition, I couldn't consider the effect of the caregiver believing the water crisis was exaggerated on most of the outcomes because of convergence issues, and similarly with the relationship between the child being tested and the child having elevated BLLs.
+## Multivariable modeling results (Cauchy priors for additional regularization)
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+#For water source:
+child_adult$water_exaggeratedbinary <- as.numeric(child_adult$water_exaggerated=="Agree" | child_adult$water_exaggerated=="Strongly Agree")
+child_adult$pubben <- ifelse(child_adult$public_benefits=="Yes", 1, ifelse(is.na(child_adult$public_benefits), NA_real_, 0))
+child_adult$bottledwater <- ifelse(child_adult$watersource=="Bottled water", 1, ifelse(is.na(child_adult$watersource), NA_real_, 0))
+child_adult$employcollapse <- ifelse(child_adult$employ_status=="Employed", "Employed", ifelse(child_adult$employ_status=="Unemployed", "Unemployed", ifelse(is.na(child_adult$employ_status), NA_character_, "Other")))
+
+watersource_model2 <- stan_glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id),
+                               data = child_adult, 
+                               family = "binomial", seed = 21,
+                               prior = cauchy(location = 0,
+                                              scale = 2.5,
+                                              autoscale = TRUE))
+
+mysum <- summary(watersource_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+effects_mat2 <- data.frame("Outcome" = rep("Child drinks bottled water", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
+
+#For getting tested:
+tested_model2 <- stan_glmer(gettested ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = child_adult, family = "binomial", seed = 22,
+                               prior = cauchy(location = 0,
+                                              scale = 2.5,
+                                              autoscale = TRUE))
+
+mysum <- summary(tested_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])
+
+effects_mat2 <- rbind(effects_mat2, subdat)
+
+#For having elevated BLLs (restricting to children who got screened):
+bll_model2 <- stan_glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = filter(child_adult, gettested=="Yes"), family = "binomial", seed = 23,
+                               prior = cauchy(location = 0,
+                                              scale = 2.5,
+                                              autoscale = TRUE))
+
+mysum <- summary(bll_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Elevated BLLs", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 5], "Lower" = mysum[2:7, 4], "Upper" = mysum[2:7, 6])
+
+effects_mat2 <- rbind(effects_mat2, subdat)
+
+#For having rashes:
+rash_model2 <- stan_glmer(rash ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested  + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 24,
+                               prior = cauchy(location = 0,
+                                              scale = 2.5,
+                                              autoscale = TRUE))
+
+mysum <- summary(rash_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Rashes", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
+
+effects_mat2 <- rbind(effects_mat2, subdat)
+
+#For having hair loss
+hair_model2 <- stan_glmer(hair ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 25,
+                               prior = cauchy(location = 0,
+                                              scale = 2.5,
+                                              autoscale = TRUE))
+
+mysum <- summary(hair_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Hair loss", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
+
+effects_mat2 <- rbind(effects_mat2, subdat)
+
+#For having learning delays:
+learn_model2 <- stan_glmer(learn ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 26,
+                               prior = cauchy(location = 0,
+                                              scale = 2.5,
+                                              autoscale = TRUE))
+
+mysum <- summary(learn_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Learning delays", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
+
+effects_mat2 <- rbind(effects_mat2, subdat)
+
+#For having hyperactivity:
+hyper_model2 <- stan_glmer(hyper ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 27,
+                               prior = cauchy(location = 0,
+                                              scale = 2.5,
+                                              autoscale = TRUE))
+
+mysum <- summary(hyper_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Hyperactivity", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
+
+effects_mat2 <- rbind(effects_mat2, subdat)
+
+#For having irritability:
+irr_model2 <- stan_glmer(irritable ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, family = "binomial", seed = 28,
+                               prior = cauchy(location = 0,
+                                              scale = 2.5,
+                                              autoscale = TRUE))
+
+mysum <- summary(irr_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Irritability", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
+
+effects_mat2 <- rbind(effects_mat2, subdat)
+
+#For overall symptoms:
+overall_model2 <- stan_lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll + (1 | unique_id), data = child_adult, seed = 29,
+                               prior = cauchy(location = 0,
+                                              scale = 2.5,
+                                              autoscale = TRUE))
+
+mysum <- summary(overall_model2, pars = c("(Intercept)", "gender.xMale", "age.x", "racecollapseOther", "racecollapseWhite", "pubben", "water_exaggeratedbinary", "gettestedYes", "elevbllYes", "Sigma[unique_id:(Intercept),(Intercept)]"), probs = c(0.025, 0.5, 0.975), digits = 2)
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Total Symptoms", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 5], "Lower" = mysum[2:9, 4], "Upper" = mysum[2:9, 6])
+
+effects_mat2 <- rbind(effects_mat2, subdat)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
+effects_mat2$lower <- case_when(
+  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Lower,
+  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Lower)
+)
+
+effects_mat2$upper <- case_when(
+  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Upper,
+  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Upper)
+)
+
+effects_mat2$estimate <- case_when(
+  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Estimate,
+  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Estimate)
+)
+
+effects_mat2$label <- paste0(round(effects_mat2$estimate, digits=1), " (", round(effects_mat2$lower, digits = 1), ", ", round(effects_mat2$upper, digits = 1), ")")
+
+pretty_effects2 <- dplyr::select(effects_mat2, Outcome, Variable, label)
+rownames(pretty_effects2) <- NULL
+
+kable(pretty_effects2, col.names = c("Outcome", "Predictor", "Odds Ratio (95% CI)"))
+```

### 2021-10-05 papertwo_child_health.Rmd
Minor change to correct issue with subsetting.

@@
 effects_mat2$lower <- case_when(
-  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Lower,
-  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Lower)
+  effects_mat2$Outcome=="Total Symptoms" ~ effects_mat2$Lower,
+  effects_mat2$Outcome!="Total Symptoms" ~ exp(effects_mat2$Lower)
 )
@@
 effects_mat2$upper <- case_when(
-  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Upper,
-  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Upper)
+  effects_mat2$Outcome=="Total Symptoms" ~ effects_mat2$Upper,
+  effects_mat2$Outcome!="Total Symptoms" ~ exp(effects_mat2$Upper)
 )
@@
 effects_mat2$estimate <- case_when(
-  effects_mat2$Outcome=="Overall Symptoms" ~ effects_mat2$Estimate,
-  effects_mat2$Outcome!="Overall Symptoms" ~ exp(effects_mat2$Estimate)
+  effects_mat2$Outcome=="Total Symptoms" ~ effects_mat2$Estimate,
+  effects_mat2$Outcome!="Total Symptoms" ~ exp(effects_mat2$Estimate)
 )

### 2021-12-07 papertwo_child_health.Rmd
Update to switch to GEE for child health analysis

--- 2021-05-27 papertwo_child_health.Rmd
@@
 library(lme4)
+library(rstanarm)
+library(gee)
 
@@
 
-## Multivariable modeling results
+## Multivariable modeling results (GEE)
 
@@
 
-##watersource_model <- glmer(bottledwater ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ##issues with convergence; did not include
-
-##summary(watersource_model)
+child_adult <- arrange(child_adult, unique_id)
 
 #For getting tested:
-tested_model_noadult <- glmer(gettested ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-tested_model_adult <- glmer(gettested ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + (1 | unique_id), data = child_adult, family = "binomial")
+tested_model <- gee((as.numeric(gettested)-1) ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary, id = unique_id, data = child_adult, family = "binomial", corstr = "exchangeable")
 
-summary(tested_model_noadult)
-summary(tested_model_adult)
+mysum <- summary(tested_model)$coefficients
 
-effects_mat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = c(summary(tested_model_noadult)$coefficients[-1,1], summary(tested_model_adult)$coefficients[7,1]), "StErr" = c(summary(tested_model_noadult)$coefficients[-1,2], summary(tested_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(tested_model_noadult)$coefficients[-1,4], summary(tested_model_adult)$coefficients[7,4]))
+mysum
 
-#For having elevated BLLs:
-#bll_model_noadult <- glmer(elevbll ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-#bll_model_adult <- glmer(elevbll ~ gender.x + scale(age.x) + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial") # Not included due to convergence issues
+effects_mat <- data.frame("Outcome" = rep("Get tested", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = mysum[2:7, 1], "SE" = mysum[2:7, 4])
 
-#summary(bll_model_noadult)
-#summary(bll_model_adult)
+#For having elevated BLLs (restricting to children who were screened):
+bll_model <- gee((as.numeric(elevbll)-1) ~ gender.x + age.x + racecollapse + pubben, id = unique_id, data = child_adult[child_adult$gettested=="Yes",], family = "binomial", corstr = "exchangeable")
 
-#subdat <- data.frame("Outcome" = rep("Elevated BLLs", 5), "Variable" = c("Gender", "Age", "Race-Other", "Race-White", "Public Benefits"), "Estimate" = c(summary(bll_model_noadult)$coefficients[-1,1]), "StErr" = c(summary(bll_model_noadult)$coefficients[-1,2]), "Pvalue" = c(summary(bll_model_noadult)$coefficients[-1,4]))
+mysum <- summary(bll_model)$coefficients
 
-#effects_mat <- rbind(effects_mat, subdat)
+mysum
 
-#For having rashes:
-rash_model_noadult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-summary(rash_model_noadult)
-rash_model_adult <- glmer(rash ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
-summary(rash_model_adult)
-
-subdat <- data.frame("Outcome" = rep("Rashes", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(rash_model_noadult)$coefficients[-1,1], summary(rash_model_adult)$coefficients[7,1]), "StErr" = c(summary(rash_model_noadult)$coefficients[-1,2], summary(rash_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(rash_model_noadult)$coefficients[-1,4], summary(rash_model_adult)$coefficients[7,4]))
+subdat <- data.frame("Outcome" = rep("Elevated BLLs", 5), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)"), "Estimate" = mysum[2:6, 1], "SE" = mysum[2:6, 4])
 
@@
 
-#For having hair loss:
-#hair_model_noadult <- glmer(hair ~ gender.x + scale(age.x) + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include
-#summary(hair_model_noadult)
-#hair_model_adult <- glmer(hair ~ gender.x + scale(age.x) + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial") ## convergence issues; did not include
-#summary(hair_model_adult)
+#For having rashes:
+rash_model <- gee((as.numeric(rash)-1) ~ gender.x + age.x + racecollapse + pubben + gettested  + elevbll, id = unique_id, data = child_adult, family = "binomial", corstr = "exchangeable")
 
-#subdat <- data.frame("Outcome" = rep("Hairloss", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(hair_model_noadult)$coefficients[-1,1], summary(hair_model_adult)$coefficients[7,1]), "StErr" = c(summary(hair_model_noadult)$coefficients[-1,2], summary(hair_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(hair_model_noadult)$coefficients[-1,4], summary(hair_model_adult)$coefficients[7,4]))
+mysum <- summary(rash_model)$coefficients
 
-#effects_mat <- rbind(effects_mat, subdat)
+mysum
+
+subdat <- data.frame("Outcome" = rep("Rashes", 7), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:8, 1], "SE" = mysum[2:8, 4])
+
+effects_mat <- rbind(effects_mat, subdat)
 
 #For having learning delays:
-learn_model_noadult <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-summary(learn_model_noadult)
+learn_model <- gee((as.numeric(learn)-1) ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll, id = unique_id, data = child_adult, family = "binomial", corstr = "exchangeable")
 
-learn_model_layer2 <- glmer(learn ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
-summary(learn_model_layer2)
+mysum <- summary(learn_model)$coefficients
 
-subdat <- data.frame("Outcome" = rep("Learning Delays", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(learn_model_noadult)$coefficients[-1,1], summary(learn_model_layer2)$coefficients[7,1]), "StErr" = c(summary(learn_model_noadult)$coefficients[-1,2], summary(learn_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(learn_model_noadult)$coefficients[-1,4], summary(learn_model_layer2)$coefficients[7,4]))
+mysum
+
+subdat <- data.frame("Outcome" = rep("Learning delays", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 1], "SE" = mysum[2:9, 4])
 
@@
 #For having hyperactivity:
-hyper_model_noadult <- glmer(hyper ~ gender.x + scale(age.x) + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-summary(hyper_model_noadult)
+hyper_model <- gee((as.numeric(hyper)-1) ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll, id = unique_id, data = child_adult, family = "binomial", corstr = "exchangeable")
 
-hyper_model_layer2 <- glmer(hyper ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
-summary(hyper_model_layer2)
+mysum <- summary(hyper_model)$coefficients
 
-subdat <- data.frame("Outcome" = rep("Hyperactivity", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(hyper_model_noadult)$coefficients[-1,1], summary(hyper_model_layer2)$coefficients[7,1]), "StErr" = c(summary(hyper_model_noadult)$coefficients[-1,2], summary(hyper_model_layer2)$coefficients[7,2]), "Pvalue" = c(summary(hyper_model_noadult)$coefficients[-1,4], summary(hyper_model_layer2)$coefficients[7,4]))
+mysum
+
+subdat <- data.frame("Outcome" = rep("Hyperactivity", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 1], "SE" = mysum[2:9, 4])
 
@@
 #For having irritability:
-irr_model_noadult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult, family = "binomial")
-summary(irr_model_noadult)
-irr_model_adult <- glmer(irritable ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + (1 | unique_id), data = child_adult, family = "binomial")
-summary(irr_model_adult)
+irr_model <- gee((as.numeric(irritable)-1) ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll, id = unique_id, data = child_adult, family = "binomial", corstr = "exchangeable")
 
-subdat <- data.frame("Outcome" = rep("Irritability", 6), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs"), "Estimate" = c(summary(irr_model_noadult)$coefficients[-1,1], summary(irr_model_adult)$coefficients[7,1]), "StErr" = c(summary(irr_model_noadult)$coefficients[-1,2], summary(irr_model_adult)$coefficients[7,2]), "Pvalue" = c(summary(irr_model_noadult)$coefficients[-1,4], summary(irr_model_adult)$coefficients[7,4]))
+mysum <- summary(irr_model)$coefficients
+
+mysum
+
+subdat <- data.frame("Outcome" = rep("Irritability", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 1], "SE" = mysum[2:9, 4])
 
@@
 #For overall symptoms:
-overall_model_noadult <- lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + (1 | unique_id), data = child_adult)
-summary(overall_model_noadult)
+overall_model <- gee(overall_symp ~ gender.x + age.x + racecollapse + pubben + water_exaggeratedbinary + gettested + elevbll, id = unique_id, data = child_adult, family = "poisson", corstr = "exchangeable")
+mysum <- summary(overall_model)$coefficients
 
-overall_model_adult <- lmer(overall_symp ~ gender.x + age.x + racecollapse + pubben + as.numeric(blood_test_after_april_2014=="Yes") + water_exaggeratedbinary + (1 | unique_id), data = child_adult)
-summary(overall_model_adult)
+mysum
 
-subdat <- data.frame("Outcome" = rep("Overall Symptoms", 7), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Child screened for BLLs (ref: Child not screened for BLLs)", "Water crisis was exaggerated (ref: Crisis not exaggerated)"), "Estimate" = c(summary(overall_model_noadult)$coefficients[-1,1], summary(overall_model_adult)$coefficients[7:8,1]), "StErr" = c(summary(overall_model_noadult)$coefficients[-1,2], summary(overall_model_adult)$coefficients[7:8,2]), "Pvalue" = pnorm(c(summary(overall_model_noadult)$coefficients[-1,3], summary(overall_model_adult)$coefficients[7:8,3]), lower.tail = FALSE))
+subdat <- data.frame("Outcome" = rep("Total Symptoms", 8), "Variable" = c("Male gender (ref: Female gender)", "Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Receives public benefits (ref: No benefits)", "Water crisis was exaggerated (ref: Crisis not exaggerated)", "Child screened for BLLs (ref: Child not screened)", "Child diagnosed with elevated BLLs (ref: Child had normal BLLs)"), "Estimate" = mysum[2:9, 1], "SE" = mysum[2:9, 4])
 
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
-effects_mat$BHpvalue <- p.adjust(effects_mat$Pvalue, method="BH")
+effects_mat$Lower <- exp(effects_mat$Estimate - 1.96*effects_mat$SE)
+effects_mat$Upper <- exp(effects_mat$Estimate + 1.96*effects_mat$SE)
+effects_mat$OR <- exp(effects_mat$Estimate)
+effects_mat$pvalue <- pnorm(abs(effects_mat$Estimate/effects_mat$SE), lower.tail = FALSE)
+effects_mat$BHPvalue <- p.adjust(effects_mat$pvalue, method="BH")
 
-effects_mat$lower <- case_when(
-  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate - 1.96*effects_mat$StErr,
-  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate - 1.96*effects_mat$StErr)
-)
+effects_mat$prettyp <- round(effects_mat$pvalue, digits = 2)
+effects_mat$prettypBH <- round(effects_mat$BHPvalue, digits = 2)
+effects_mat$sig <- effects_mat$pvalue < 0.05
 
-effects_mat$upper <- case_when(
-  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate + 1.96*effects_mat$StErr,
-  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate + 1.96*effects_mat$StErr)
-)
+effects_mat$label <- paste0(round(effects_mat$OR, digits=1), " (", round(effects_mat$Lower, digits = 1), ", ", round(effects_mat$Upper, digits = 1), ")")
 
-effects_mat$effect <- case_when(
-  effects_mat$Outcome=="Overall Symptoms" ~ effects_mat$Estimate,
-  effects_mat$Outcome!="Overall Symptoms" ~ exp(effects_mat$Estimate)
-)
-
-effects_mat$label <- paste0(round(effects_mat$effect, digits=1), " (", round(effects_mat$lower, digits = 1), ", ", round(effects_mat$upper, digits = 1), ")")
-
-pretty_effects <- select(effects_mat, Outcome, Variable, label, BHpvalue)
-pretty_effects$BHpvalue <- round(pretty_effects$BHpvalue, 3)
+pretty_effects <- dplyr::select(effects_mat, Outcome, Variable, label, prettypBH)
 rownames(pretty_effects) <- NULL
 
-kable(pretty_effects, col.names = c("Outcome", "Predictor", "Odds Ratio (95% CI)", "P-value"))
+kable(pretty_effects)
+#kable(pretty_effects, col.names = c("Outcome", "Predictor", "Odds Ratio (95% CI)"))
 ```
-
-Note that these modeling results doesn't include one important outcomes: child water source.
-I was unable to get this model to fit stably because of the small number of children not drinking bottled water.
-In addition, I couldn't consider the effect of the caregiver believing the water crisis was exaggerated on most of the outcomes because of convergence issues, and similarly with the relationship between the child being tested and the child having elevated BLLs.

### 2021-12-07 papertwo_child_health.Rmd
Updating readme and some documentation

@@
 This allows us to address the issues with small sample size and separation in the data.
+
+Note: Dec. 2021
+
+This analysis was redone using GEE, in order to meet a reviewer request for a non-Bayesian analysis and to deal with the large number of small clusters in the data.
 
@@
 
+Adjusting for multiple testing:
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}

### 2022-08-25 paperfour_healthbehaviors.Rmd
Updates in response to reviewer comments + tidying up

@@
 
-#mydata_complete$gender <- factor(mydata_complete$gender)
 mydata_complete$reth <- factor(mydata_complete$reth)
@@
 mydata_complete$current_zip <- factor(mydata_complete$current_zip)
-#mydata_complete$have_health_insurance <- factor(mydata_complete$have_health_insurance)
 mydata_complete$access_vehicle <- factor(mydata_complete$access_vehicle)
@@
 
-number_water_tests <- with(imp_long_mids, lm(log(watertestnum + 0.1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2))
+number_water_tests <- with(imp_long_mids, glm(watertestnum ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "poisson"))
 
@@
 
-## This model could not be fit because of small sample sizes.
-#elev_blls <- with(imp_long_mids, glm(as.numeric(elevated_lead_after_april_2014=="Yes") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + water_source2 + number_children + confidants2, family = "binomial"))
-
-#summary(pool(elev_blls))
-
-#subdat <- data.frame("Outcome" = rep("Elevated BLLs", 18), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Other water source (ref: Flint tap water)", "Number of children", "Network size"), "Estimate" = summary(pool(elev_blls))$estimate[-1], "SE" = summary(pool(elev_blls))$std.error[-1], "Pval" = summary(pool(elev_blls))$p.value[-1])
-
-#effect_estims <- rbind(effect_estims, subdat)
-
 currentwatersource <- with(imp_long_mids, polr(current_water_source2 ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, Hess = TRUE))
@@
 
-number_bottles <- with(imp_long_mids, glm(num_bottles_per_day ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "quasipoisson"))
+waterlinestatus <- with(filter(imp_long_mids, water_source2=="Tap water through the City of Flint"), glm(as.numeric(water_line_status_after_april2014=="A mailing or official said that my lead/water line did not need to be replaced" | water_line_status_after_april2014=="I was offered a lead/water line replacement but I refused it" | water_line_status_after_april2014=="My lead/water lines were replaced") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + number_children + confidants2, family = "binomial"))
 
-summary(pool(number_bottles))
+summary(pool(waterlinestatus))
 
-subdat <- data.frame("Outcome" = rep("Number of bottles per day", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(number_bottles))$estimate[-1], "SE" = summary(pool(number_bottles))$std.error[-1], "Pval" = summary(pool(number_bottles))$p.value[-1])
+subdat <- data.frame("Outcome" = rep("Water line status", 21), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(waterlinestatus))$estimate[-1], "SE" = summary(pool(waterlinestatus))$std.error[-1], "Pval" = summary(pool(waterlinestatus))$p.value[-1])
 
@@
 
-recycle_bottles <- with(imp_long_mids, glm(as.numeric(water_bottle_disposal=="I don't ever have plastic water bottles at home" | water_bottle_disposal=="Keep/save them for re-use or another purpose" | water_bottle_disposal=="Recycle them") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial"))
-
-summary(pool(recycle_bottles))
-
-subdat <- data.frame("Outcome" = rep("Bottle disposal", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(recycle_bottles))$estimate[-1], "SE" = summary(pool(recycle_bottles))$std.error[-1], "Pval" = summary(pool(recycle_bottles))$p.value[-1])
-
-effect_estims <- rbind(effect_estims, subdat)
-
-waterlinestatus <- with(imp_long_mids, glm(as.numeric(water_line_status_after_april2014=="A mailing or official said that my lead/water line did not need to be replaced" | water_line_status_after_april2014=="I was offered a lead/water line replacement but I refused it" | water_line_status_after_april2014=="My lead/water lines were replaced") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial"))
-
-summary(pool(waterlinestatus))
-
-subdat <- data.frame("Outcome" = rep("Water line status", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(waterlinestatus))$estimate[-1], "SE" = summary(pool(waterlinestatus))$std.error[-1], "Pval" = summary(pool(waterlinestatus))$p.value[-1])
-
-effect_estims <- rbind(effect_estims, subdat)
-
-water_line_time <- with(imp_long_mids, coxph(Surv(water_line_surv, as.numeric(waterline_replaced_eventind)-1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2))
+water_line_time <- with(filter(imp_long_mids, water_source2=="Tap water through the City of Flint"), coxph(Surv(water_line_surv, as.numeric(waterline_replaced_eventind)-1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + number_children + confidants2))
 
@@
 
-subdat <- data.frame("Outcome" = rep("Time to water line replacement", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(water_line_time))$estimate, "SE" = summary(pool(water_line_time))$std.error, "Pval" = summary(pool(water_line_time))$p.value)
+subdat <- data.frame("Outcome" = rep("Time to water line replacement", 21), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(water_line_time))$estimate, "SE" = summary(pool(water_line_time))$std.error, "Pval" = summary(pool(water_line_time))$p.value)
 
@@
 effect_estims <- rbind(effect_estims, subdat)
-
-#child_test <- with(imp_long_mids, glm(testpost2014_child ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + confidants2 + factor(blood_test_after_april_2014, ordered = FALSE) + offset(number_children), family = "quasipoisson"))
-
-#summary(pool(child_test))
-
-#subdat <- data.frame("Outcome" = rep("Got child tested", 23), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Network size", "Adult not tested (ref: Adult tested)", "Adult unsure if tested (ref: Adult tested)"), "Estimate" = summary(pool(child_test))$estimate[-1], "SE" = summary(pool(child_test))$std.error[-1], "Pval" = summary(pool(child_test))$p.value[-1])
-
-#effect_estims <- rbind(effect_estims, subdat)
-
-##This model not included because of stability issues:
-
-#child_bll <- with(imp_long_mids, glm(bllpost2014_child ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + confidants2 + as.numeric(elevated_lead_after_april_2014=="Yes") + offset(number_children), family = "quasipoisson"))
-
-#summary(pool(child_bll))
-
-#subdat <- data.frame("Outcome" = rep("Child had elevated BLLs", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Network size", "Adult has elevated BLLs (ref: Adult has normal/unsure BLLs)"), "Estimate" = summary(pool(child_bll))$estimate[-1], "SE" = summary(pool(child_bll))$std.error[-1], "Pval" = summary(pool(child_bll))$p.value[-1])
-
-#effect_estims <- rbind(effect_estims, subdat)
-
-#child_bottled <- with(imp_long_mids, glm(bottledwater_child ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + confidants2 + factor(current_water_source2, ordered = FALSE) + offset(number_children), family = "quasipoisson"))
-
-#summary(pool(child_bottled))
-
-#subdat <- data.frame("Outcome" = rep("Child uses bottled water", 23), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Network size", "Adult uses filtered tap water (ref: Adult uses unfiltered water)", "Adult uses bottled water (ref: Adult uses unfiltered water)"), "Estimate" = summary(pool(child_bottled))$estimate[-1], "SE" = summary(pool(child_bottled))$std.error[-1], "Pval" = summary(pool(child_bottled))$p.value[-1])
-
-#effect_estims <- rbind(effect_estims, subdat)
 ```
@@
 
+At reviewer request, we redo the above modeling using only the complete data, without multiple imputation:
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+mydata_complete$zip2 <- case_when(
+  mydata_complete$current_zip=="48502" | mydata_complete$current_zip=="48503" ~ "48502/48503",
+  mydata_complete$current_zip=="48504" ~ "48504",
+  mydata_complete$current_zip=="48505" ~ "48505",
+  mydata_complete$current_zip=="48506" ~ "48506",
+  mydata_complete$current_zip=="48507" | mydata_complete$current_zip=="48532" ~ "48507/48532"
+)
+
+mydata_complete$educ_level2 <- case_when(
+  mydata_complete$educ_level=="Less than a high school diploma" | mydata_complete$educ_level=="High school degree or equivalent (e.g. GED)" ~ "High school or less",
+  mydata_complete$educ_level=="Some college, no degree" ~ "Some college",
+  mydata_complete$educ_level=="Associate degree" | mydata_complete$educ_level=="Bachelor's degree" | mydata_complete$educ_level=="Master's, Doctoral or Professional degree" ~ "Associate's or more"
+)
+
+mydata_complete$public_benefits2 <- ifelse(mydata_complete$public_benefits=="Yes", "Yes", "No")
+mydata_complete$gender2 <- ifelse(mydata_complete$gender=="Transgender Woman", "Female", mydata_complete$gender)
+
+mydata_complete$marital_status2 <- case_when(
+  mydata_complete$marital_status=="Single (never married)" ~ "Single (never married)",
+  mydata_complete$marital_status=="Married" ~ "Married", 
+  mydata_complete$marital_status=="Separated" | mydata_complete$marital_status=="Divorced" | mydata_complete$marital_status=="Widowed" ~ "Separated"
+)
+
+mydata_complete$employ_status2 <- case_when(
+  mydata_complete$employ_status=="Jobs/sporadic" | mydata_complete$employ_status=="Other" ~ "Other",
+  mydata_complete$employ_status=="Retired" ~ "Retired",
+  mydata_complete$employ_status=="Employed" ~ "Employed",
+  mydata_complete$employ_status=="Unemployed" ~ "Unemployed",
+  is.na(mydata_complete$employ_status) ~ NA_character_)
+
+mydata_complete$reth2 <- case_when(
+  mydata_complete$reth=="Black" ~ "Black",
+  mydata_complete$reth=="White" ~ "White",
+  mydata_complete$reth=="Mixed Race" | mydata_complete$reth=="American Indian" | mydata_complete$reth=="Other race" | mydata_complete$reth=="Asian" | mydata_complete$reth=="Hispanic/Latinx" ~ "Other"
+)
+
+mydata_complete$current_housing2 <- case_when(
+  mydata_complete$current_housing=="You own a home" ~ "Owned home",
+  mydata_complete$current_housing=="You rent a home" ~ "Rented home",
+  mydata_complete$current_housing=="You are staying with family or a friend" | mydata_complete$current_housing=="You are at a shelter" | mydata_complete$current_housing=="You are crashing/couch-surfing somewhere" | mydata_complete$current_housing=="You are on the streets" ~ "Unstable housing",
+  mydata_complete$current_housing=="You are at a retirement facility" | mydata_complete$current_housing=="You are in an in-patient setting (e.g., rehab)" | mydata_complete$current_housing=="Other" ~ "Other housing"
+)
+
+mydata_complete$have_health_insurance2 <- ifelse(mydata_complete$have_health_insurance=="Unsure/Don't know", "No", mydata_complete$have_health_insurance)
+
+mydata_complete$water_source2 <- ifelse(mydata_complete$water_source=="Tap water through the City of Flint (Water Department etc.)", "Tap water through the City of Flint", "Other")
+
+mydata_complete$current_water_source2 <- case_when(
+  mydata_complete$current_water_source=="Bottled water" | mydata_complete$current_water_source=="I don't drink any water at home" ~ "Bottled water",
+  mydata_complete$current_water_source=="Tap water (with a filter)" | mydata_complete$current_water_source=="Water from a filtration system" ~ "Filtered tap water",
+  mydata_complete$current_water_source=="Tap water (without a filter)" ~ "Unfiltered tap water"
+)
+
+mydata_complete$zip2 <- factor(mydata_complete$zip2)
+mydata_complete$educ_level2 <- factor(mydata_complete$educ_level2, levels = c("High school or less", "Some college", "Associate's or more"))
+mydata_complete$public_benefits2 <- factor(mydata_complete$public_benefits2)
+mydata_complete$marital_status2 <- factor(mydata_complete$marital_status2)
+mydata_complete$employ_status2 <- factor(mydata_complete$employ_status2)
+mydata_complete$reth2 <- factor(mydata_complete$reth2)
+mydata_complete$current_housing2 <- factor(mydata_complete$current_housing2, levels = c("Owned home", "Rented home", "Unstable housing", "Other housing"))
+mydata_complete$have_health_insurance2 <- factor(mydata_complete$have_health_insurance2)
+mydata_complete$water_source2 <- factor(mydata_complete$water_source2, levels = c("Tap water through the City of Flint", "Other"))
+mydata_complete$current_water_source2 <- factor(mydata_complete$current_water_source2, levels = c("Unfiltered tap water", "Filtered tap water", "Bottled water"), ordered = TRUE)
 ```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+effect_estims <- data.frame("Outcome" = NA, "Predictor" = NA, "Estimate" = NA, "SE" = NA, "Pval" = NA)
+
+time_to_notice <- lm(log(num_time_notice) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + water_source2 + access_vehicle + number_children + confidants2, data = mydata_complete)
+
+summary(time_to_notice)
+
+subdat <- data.frame("Outcome" = rep("Time to notice", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(time_to_notice)$coefficients[-1, 1], "SE" = summary(time_to_notice)$coefficients[-1, 2], "Pval" = summary(time_to_notice)$coefficients[-1, 4])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+number_water_tests <- glm(watertestnum ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, data = mydata_complete, family = "poisson")
+
+summary(number_water_tests)
+
+subdat <- data.frame("Outcome" = rep("Number of water tests", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(number_water_tests)$coefficients[-1,1], "SE" = summary(number_water_tests)$coefficients[-1,2], "Pval" = summary(number_water_tests)$coefficients[-1,4])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+last_water_test_time <- coxph(Surv(water_test_surv, as.numeric(water_test_event_ind)-1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, data = mydata_complete)
+
+summary(last_water_test_time)
+
+subdat <- data.frame("Outcome" = rep("Time to last water test", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(last_water_test_time)$coefficients[,1], "SE" = summary(last_water_test_time)$coefficients[,3], "Pval" = summary(last_water_test_time)$coefficients[,5])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+last_test_result <- glm(as.numeric(collapse_last_test=="Acceptable levels of lead") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial", data = mydata_complete)
+
+summary(last_test_result)
+
+subdat <- data.frame("Outcome" = rep("Last water test result", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(last_test_result)$coefficients[-1,1], "SE" = summary(last_test_result)$coefficients[-1,2], "Pval" = summary(last_test_result)$coefficients[-1,4])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+blood_test <- glm(as.numeric(blood_test_after_april_2014=="Yes") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial", data = mydata_complete)
+
+summary(blood_test)
+
+subdat <- data.frame("Outcome" = rep("Blood test", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(blood_test)$coefficients[-1, 1], "SE" = summary(blood_test)$coefficients[-1, 2], "Pval" = summary(blood_test)$coefficients[-1, 4])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+currentwatersource <- polr(current_water_source2 ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, Hess = TRUE, data = mydata_complete)
+
+summary(currentwatersource)
+
+subdat <- data.frame("Outcome" = rep("Current drinking water source", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(currentwatersource)$coefficients[1:22,1], "SE" = summary(currentwatersource)$coefficients[1:22,2], "Pval" = NA)
+
+effect_estims <- rbind(effect_estims, subdat)
+
+water_pod_past <- glm(used_water_pod ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial", data = mydata_complete)
+
+summary(water_pod_past)
+
+subdat <- data.frame("Outcome" = rep("Used water pod in the past", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(water_pod_past)$coefficients[-1, 1], "SE" = summary(water_pod_past)$coefficients[-1, 2], "Pval" = summary(water_pod_past)$coefficients[-1, 4])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+water_pod_now <- glm(get_free_bottled_water ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial", data = mydata_complete)
+
+summary(water_pod_now)
+
+subdat <- data.frame("Outcome" = rep("Use water pod now", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(water_pod_now)$coefficients[-1, 1], "SE" = summary(water_pod_now)$coefficients[-1, 2], "Pval" = summary(water_pod_now)$coefficients[-1, 4])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+waterlinestatus <- glm(as.numeric(water_line_status_after_april2014=="A mailing or official said that my lead/water line did not need to be replaced" | water_line_status_after_april2014=="I was offered a lead/water line replacement but I refused it" | water_line_status_after_april2014=="My lead/water lines were replaced") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + number_children + confidants2, family = "binomial", data = filter(mydata_complete, water_source2=="Tap water through the City of Flint"))
+
+summary(waterlinestatus)
+
+subdat <- data.frame("Outcome" = rep("Water line status", 21), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(waterlinestatus)$coefficients[-1, 1], "SE" = summary(waterlinestatus)$coefficients[-1, 2], "Pval" = summary(waterlinestatus)$coefficients[-1, 4])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+water_line_time <- coxph(Surv(water_line_surv, as.numeric(waterline_replaced_eventind)-1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + number_children + confidants2, data = filter(mydata_complete, water_source2=="Tap water through the City of Flint"))
+
+summary(water_line_time)
+
+subdat <- data.frame("Outcome" = rep("Time to water line replacement", 21), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(water_line_time)$coefficients[,1], "SE" = summary(water_line_time)$coefficients[,3], "Pval" = summary(water_line_time)$coefficients[,5])
+
+effect_estims <- rbind(effect_estims, subdat)
+
+drinktap <- polr(drink_tap_in_three_years ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, Hess = TRUE, data = mydata_complete)
+
+summary(drinktap)
+
+subdat <- data.frame("Outcome" = rep("Likely to drink tap in three years?", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(drinktap)$coefficients[1:22,1], "SE" = summary(drinktap)$coefficients[1:22,2], "Pval" = NA)
+
+effect_estims <- rbind(effect_estims, subdat)
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, eval = TRUE}
+effect_estims <- effect_estims[-1,]
+effect_estims$Pval[is.na(effect_estims$Pval)] <- 2*pnorm(abs(effect_estims$Estimate[is.na(effect_estims$Pval)]/effect_estims$SE[is.na(effect_estims$Pval)]), lower.tail = FALSE)
+effect_estims$Lower <- effect_estims$Estimate - 1.96*effect_estims$SE
+effect_estims$Upper <- effect_estims$Estimate + 1.96*effect_estims$SE
+
+pretty_effects <- data.frame("Outcome" = effect_estims$Outcome, "Predictor" = effect_estims$Predictor, "Estimate" = exp(effect_estims$Estimate), "Lower" = exp(effect_estims$Lower), "Upper" = exp(effect_estims$Upper), "BHpvalue" = round(p.adjust(effect_estims$Pval, method="BH"), digits = 2))
+
+pretty_effects$Label <- paste0(round(pretty_effects$Estimate, digits = 1), " (", round(pretty_effects$Lower, digits = 1), ", ", round(pretty_effects$Upper, digits = 1), ")")
+
+pretty_effects2 <- dplyr::select(pretty_effects, Outcome, Predictor, Label, BHpvalue)
+
+pretty_effects2[pretty_effects2$BHpvalue <= 0.05,]
+```

### 2022-08-25 paperone_adult_health.Rmd
Updates in response to reviewer comments + tidying up

@@
 ggsave(filename = "~/Desktop/Research/Jerel Flint/Publications/Paper 1 - Adult Health/mymap.pdf", plot = popmap, width = 8, height = 8)
-
-#table_predictors <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), strata = "collapserace", data=mydata, includeNA = TRUE, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE))
-
-#table_outcomes <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), strata = "collapserace", data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA = TRUE)
-
-#kable(print(table_predictors, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:16, 18:20)) %>% kable_styling(position="center")
-
-#kable(print(table_outcomes, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:7, 9:12, 14:17, 19:22, 24:27, 29:32, 36:38)) %>% kable_styling(position="center")
-
-#table_predictors_notstrat <- CreateTableOne(vars=c("age", "gender", "collapseeduc", "public_benefits", "collapsemarital", "number_children", "years_cityflint", "confidants2"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)
-
-#table_outcomes_notstrat <- CreateTableOne(vars=c("num_time_notice", "blood_test_after_april_2014", "elevated_lead_after_april_2014", "rashes_after_april_2014", "hairloss_after_april_2014", "nausea_after_april_2014", "irritable_after_april_2014", "overall_collapse", "ptsd_bin", "phq_bin"), data=mydata, argsNormal = list(NULL), argsNonNormal = list(var.equal = TRUE), includeNA=TRUE)
-
-#kable(print(table_predictors_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:6, 8:12, 14:16, 18:20)) %>% kable_styling(position="center")
-
-#kable(print(table_outcomes_notstrat, contDigits=1, varLabel = T, printToggle=FALSE), booktabs=T) %>% add_indent(c(4:7, 9:12, 14:17, 19:22, 24:27, 29:32, 36:38)) %>% kable_styling(position="center")
 ```
@@
 
-#bloodlead_dem <- with(imp_long_mids, logistf(elevated_collapse ~ age + collapsegender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2))
-
-#bloodlead_dem <- lapply(1:5, function(X) logistf(data = select(list_imps[[X]], elevated_collapse, age, collapsegender, collapserace, collapsepubben, number_children, years_cityflint, confidants2, zip2), elevated_collapse ~ age + collapsegender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2, pl = TRUE, dataout = TRUE))
-
 bloodlead_dem <- with(imp_long_mids, glm(elevated_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2, family = "binomial"))
 
-#test1 <- summary(bloodlead_dem)
-
-#test <- CLIP.confint(obj = bloodlead_dem)
 summary(pool(bloodlead_dem))
@@
 
-#rash_symp <- logistf(rash_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2 + hair_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + rash_collapse_before, data=mydata_complete)
-
-#test2 <- summary(rash_symp)
-
 rash_symp <- with(imp_long_mids, glm(rash_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2 + hair_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + rash_collapse_before, family = "binomial"))
@@
 effect_estims <- rbind(effect_estims, subdat)
-
-#hairloss_symp <- logistf(hair_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2 + rash_collapse + nausea_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + hair_collapse_before, data=mydata_complete)
-
-#test3 <- summary(hairloss_symp)
 
@@
 
-#nausea_symp <- logistf(nausea_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2 + rash_collapse + hair_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + nausea_collapse_before, data=mydata_complete)
-
-#test4 <- summary(nausea_symp)
-
 nausea_symp <- with(imp_long_mids, glm(nausea_collapse ~ age + collapsegender + collapserace + collapsepubben + collapseeduc2 + employ_collapse + number_children + years_cityflint + confidants2 + zip2 + rash_collapse + hair_collapse + irritable_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + nausea_collapse_before, family = "binomial"))
@@
 effect_estims <- rbind(effect_estims, subdat)
-
-#irritable_symp <- logistf(irritable_collapse ~ age + gender + collapserace + collapsepubben + number_children + years_cityflint + confidants2 + zip2 + rash_collapse + hair_collapse + nausea_collapse + elevated_collapse + bloodtest_collapse + num_time_notice + irritable_collapse_before, data=mydata_complete)
-
-#test5 <- summary(irritable_symp)
 
@@
 pretty_effects2 <- select(pretty_effects, Outcome, Predictor, Label, BHpvalue)
-#ptsd_plot <- ggplot(myresults[myresults$Outcome=="PTSD",], aes(fct_rev(Predictor_clean), Coefficient)) + geom_point() + geom_errorbar(aes(ymin=Lower, ymax=Upper, width=0.1)) + coord_flip(ylim=c(-2.35, 5.5)) + labs(y = "Odds Ratio and 95% CI", x = "", caption=TeX('Protective $\\leftarrow \\rightarrow$ Harmful' )) + geom_hline(yintercept=0, linetype="dashed", color = "black") + theme(panel.background = element_rect(fill="white"), panel.grid.major = element_blank(), panel.grid.minor=element_blank(), legend.position="bottom", text=element_text(size=14), plot.caption = element_text(size=14, hjust = 0.15)) + geom_rect(fill="white", ymin=4.7, ymax=Inf, xmin=-Inf, xmax=Inf) + annotate(geom = 'text', label = myresults$Label[myresults$Outcome=="PTSD"], x = myresults$Predictor_clean[myresults$Outcome=="PTSD"], y = 3.5, hjust = 0, vjust = 0.5) + scale_y_continuous(breaks=log(c(0.1, 0.25, 0.5, 1, 2, 4, 10)), labels=c("0.1","0.25", "0.5", "1.0", "2.0", "4.0", "10.0")) + ggtitle("Outcome: Trauma Symptoms")
-
-#ptsd_plot
-
-#phq_plot <- ggplot(myresults[myresults$Outcome=="PHQ",], aes(fct_rev(Predictor_clean), Coefficient)) + geom_point() + geom_errorbar(aes(ymin=Lower, ymax=Upper, width=0.1)) + coord_flip(ylim=c(-2.35, 5.5)) + labs(y = "Odds Ratio and 95% CI", x = "", caption=TeX('Protective $\\leftarrow \\rightarrow$ Harmful' )) + geom_hline(yintercept=0, linetype="dashed", color = "black") + theme(panel.background = element_rect(fill="white"), panel.grid.major = element_blank(), panel.grid.minor=element_blank(), legend.position="bottom", text=element_text(size=14), plot.caption = element_text(size=14, hjust = 0.15), axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank()) + geom_rect(fill="white", ymin=4.7, ymax=Inf, xmin=-Inf, xmax=Inf) + annotate(geom = 'text', label = myresults$Label[myresults$Outcome=="PHQ"], x = myresults$Predictor_clean[myresults$Outcome=="PHQ"], y = 3.5, hjust = 0, vjust = 0.5) + scale_y_continuous(breaks=log(c(0.1, 0.25, 0.5, 1, 2, 4, 10)), labels=c("0.1","0.25", "0.5", "1.0", "2.0", "4.0", "10.0")) + ggtitle("Outcome: Depression/Anxiety")
-
-#phq_plot
-
-#mental_plots <- grid.arrange(ptsd_plot, phq_plot, nrow=1, widths = c(6, 3))
-
 ```

### 2022-08-25 papertwo_child_health.Rmd
Updates in response to reviewer comments + tidying up

@@
 
-#child_adult <- filter(child_adult, age.x >= 5)
 child_adult <- filter(child_adult, age.x >= 0.5)
 samp2 <- nrow(child_adult)
-
-##child_adult <- filter(child_adult, relationship == "Your child" | relationship == "Your grandchild")
 
@@
 ```
-
-## Introductory Remarks
-
-Note: May 2021
-
-This report was an attempt to respond to two key reviewer concerns: 1) the presence of children under age 5 in our data--and thus not alive in April 2014, when the water switch happened, and 2) what to do with children who were described by a caregiver who wasn't their parent or grandparent.
-
-I tried a number of things to figure out what to do with children under age 5.
-Part of the problem here is that we were looking at excess mortality outcomes (i.e.
-"Did the child have this symptom after but not before April 2014?"), and for children under age 5, this wasn't defined, since the child wasn't alive before April 2014.
-I considered looking at 1) just the after outcome ("Did the child have this symptom after April 2014, regardless of whether they had it before 2014?") or 2) forcibly assuming that children under age 5 didn't have the symptom before April 2014.
-I was disturbed that these two outcome definitions resulted in  different results, with outcome definition (2) yielding many significant results, while outcome definition (1) yielded almost no significant results and different directions of association.
-That's bad news.
-Initially, I thought we would exclude all children under age 5.
-However, after more discussions with Jerel, we instead decided to restrict to children ages 6 months and up, and use outcome definition (1).
-
-I then looked a little more closely at the second inclusion criteria: children described by an aunt/uncle/babysitter/sibling, rather than a parent/grandparent.
-After investigating these children more closely, I concluded that we should keep them.
-They aren't significantly different from children described by a parent/grandparent, and including them in the sample doesn't affect the direction/magnitude of any associations, but it *does* increase our sample size enough to start seeing significant findings, because the larger sample size shrinks the standard errors.
-
-Therefore, I have concluded that our inclusion criteria will be children ages 6 months and up, considering outcomes based on just after April 2014 (and not before) described by any caregiver living in the City of Flint.
-
-Note: Oct. 2021
-
-This analysis was redone using Bayesian models, in order to meet a reviewer request for models that would not converge using REML.
-This allows us to address the issues with small sample size and separation in the data.
-
-Note: Dec. 2021
-
-This analysis was redone using GEE, in order to meet a reviewer request for a non-Bayesian analysis and to deal with the large number of small clusters in the data.
-
-\newpage
 
@@
 kable(pretty_effects)
-#kable(pretty_effects, col.names = c("Outcome", "Predictor", "Odds Ratio (95% CI)"))
 ```
